---
title: "SharedDAR"
author: "Renee Matthews"
date: "2025-06-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)
library(readxl)

```


#### Loading in dataframes  
```{r}
sig_3hr_shared <- readRDS("data/Final_four_data/re_analysis/AC_shared_3hour_DARs.RDS")
sig_24hr_shared <-  readRDS("data/Final_four_data/re_analysis/AC_shared_24hour_DARs.RDS")
toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))

peakAnnoList_DOX_DAR <- readRDS("data/Final_four_data/re_analysis/DOX_DAR_annotated_peaks_chipannno.RDS")

Assigned_genes_toPeak <- peakAnnoList_DOX_DAR$DOX_24 %>% as.data.frame() %>% 
  dplyr::select(mcols.genes,annotation, geneId, distanceToTSS) %>% 
  dplyr::rename("Peakid"=mcols.genes)

Top2b_peaks <- import(con="data/other_papers/ChIP3_TOP2B_CM_87-1.bed",format = "bed",genome="hg38")

RNA_results <-
toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  tidyr::unite("sample",time, id) %>% 
  pivot_wider(., id_cols = c(ENTREZID,SYMBOL),names_from = sample, values_from = logFC) %>% 
  rename_with(~ str_replace(., "hours", "RNA"))
```


```{r RNA DEG 3hr 24 hr}
RNA_all_expressed <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  dplyr::filter(time=="24_hours") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)  


RNA_24_DOX_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  dplyr::filter(time=="24_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_3_DOX_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  dplyr::filter(time=="3_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_24_EPI_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="EPI") %>% 
  dplyr::filter(time=="24_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_3_EPI_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="EPI") %>% 
  dplyr::filter(time=="3_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_24_DNR_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DNR") %>% 
  dplyr::filter(time=="24_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_3_DNR_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DNR") %>% 
  dplyr::filter(time=="3_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_24_MTX_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="MTX") %>% 
  dplyr::filter(time=="24_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

RNA_3_MTX_DEG <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="MTX") %>% 
  dplyr::filter(time=="3_hours"& adj.P.Val<0.05) %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)

Peak_gene_RNA_LFC <- Assigned_genes_toPeak %>% 
  left_join(., RNA_results, by =c("geneId"="ENTREZID"))


entrez_ids <- Assigned_genes_toPeak$geneId  


gene_info <- AnnotationDbi::select(
  org.Hs.eg.db,
  keys = entrez_ids,
  columns = c("SYMBOL"),
  keytype = "ENTREZID"
)
gene_info_collapsed <- gene_info %>%
  group_by(ENTREZID) %>%
  summarise(SYMBOL = paste(unique(SYMBOL), collapse = ","), .groups = "drop")

DOX_24_DAR <- all_results %>% 
  dplyr::filter(source =="DOX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)

DOX_3_DAR <- all_results %>% 
  dplyr::filter(source =="DOX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)


DOX_24_DAR_up <-   all_results %>%
  dplyr::filter(source =="DOX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
     dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)

DOX_3_DAR_up <- all_results %>% 
  dplyr::filter(source =="DOX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)

DOX_24_DAR_down <- all_results %>% 
  dplyr::filter(source =="DOX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)

DOX_3_DAR_down <- all_results %>% 
  dplyr::filter(source =="DOX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
```

TOP2B overlapping,  is 24 hour shared vs not shared enriched in TOP2b?
```{r Top2b}
Motif_list_gr <- readRDS( "data/Final_four_data/re_analysis/Motif_list_granges.RDS")
list2env(Motif_list_gr[10],envir = .GlobalEnv)
Allregion_ol <- join_overlap_intersect(all_regions,Top2b_peaks)%>% 
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE)


annotated_regions <-  Assigned_genes_toPeak %>%
  mutate(top_2b_ol=case_when(Peakid %in% Allregion_ol$Peakid~"TOP2b_peak",
         TRUE ~"not_TOP2b_peak")) %>% 
  mutate(top_2b_ol=factor(top_2b_ol,levels=c("TOP2b_peak","not_TOP2b_peak"))) %>% 
    mutate(ac_24_shared=case_when(Peakid %in%sig_24hr_shared~ "ac_shared",
                               TRUE ~ "not_ac_shared")) %>% 
   mutate(ac_3_shared=case_when(Peakid %in%sig_3hr_shared~ "ac_shared",
                               TRUE ~ "not_ac_shared")) %>% 
  mutate(RNA_expressed=case_when(geneId %in% RNA_all_expressed$ENTREZID ~"exp_RNA",
                                 TRUE ~ "not_exp_RNA"))
annotated_regions %>% 
  group_by(ac_3_shared,top_2b_ol) %>% 
  # tally() %>% 
  ggplot(., aes(x=ac_3_shared,fill=top_2b_ol))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle(" 3 hour AC_shared proportion of Top2B peaks")+
  ylab("proportion")


annotated_regions %>% 
  group_by(ac_24_shared,top_2b_ol) %>% 
  # tally() %>% 
  ggplot(., aes(x=ac_24_shared,fill=top_2b_ol))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle(" 24 hour AC_shared proportion of Top2B peaks")+
  ylab("proportion")

contingency_table_3hr_shared <- table(annotated_regions$ac_3_shared, annotated_regions$top_2b_ol)
contingency_table_3hr_shared

fisher.test(contingency_table_3hr_shared)  


contingency_table_24hr_shared <- table(annotated_regions$ac_24_shared, annotated_regions$top_2b_ol)
contingency_table_24hr_shared

fisher.test(contingency_table_24hr_shared)  

```


Using the CARs (Constitutively Active regions) shared between treatments at 3 hours and 24 hours,  Do we have enrichment in GO:BP terms.  What about Motifs?

Are CARs enriched in expressed genes?
  using 2kb of TSS and
  using 20kb of TSS
AT 3 hours:

```{r shared 3hour 2kb}
annotated_regions %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  ggplot(., aes(x=ac_3_shared,fill=RNA_expressed))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle("3 hour AC_shared peaks within 2kb of TSS")+
  ylab("proportion")

filt_annot_2kb <- annotated_regions %>%
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)
contingency_table_3hr_sharedRNA <- table(filt_annot_2kb$ac_3_shared, filt_annot_2kb$RNA_expressed)
contingency_table_3hr_sharedRNA

fisher.test(contingency_table_3hr_sharedRNA)  
```

```{r shared 3hour 20kb}
annotated_regions %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  ggplot(., aes(x=ac_3_shared,fill=RNA_expressed))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle("3 hour AC_shared peaks within 20kb of TSS")+
  ylab("proportion")

filt_annot_20kb <- annotated_regions %>%
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)
contingency_table_3hr_sharedRNA20 <- table(filt_annot_20kb$ac_3_shared, filt_annot_20kb$RNA_expressed)
contingency_table_3hr_sharedRNA20

fisher.test(contingency_table_3hr_sharedRNA20)  
```

AT 24 hours:

```{r shared 24hour 2kb}
annotated_regions %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  ggplot(., aes(x=ac_24_shared,fill=RNA_expressed))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle("24 hour AC_shared peaks within 2kb of TSS")+
  ylab("proportion")

filt_annot_2kb24 <- annotated_regions %>%
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)
contingency_table_24hr_sharedRNA <- table(filt_annot_2kb24$ac_24_shared, filt_annot_2kb24$RNA_expressed)
contingency_table_24hr_sharedRNA

fisher.test(contingency_table_24hr_sharedRNA)  
```

```{r shared 24hour 20kb}
annotated_regions %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  ggplot(., aes(x=ac_24_shared,fill=RNA_expressed))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle("24 hour AC_shared peaks within 20kb of TSS")+
  ylab("proportion")

filt_annot_2420kb <- annotated_regions %>%
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)
contingency_table_24hr_sharedRNA20 <- table(filt_annot_2420kb$ac_24_shared, filt_annot_2420kb$RNA_expressed)
contingency_table_24hr_sharedRNA20

fisher.test(contingency_table_24hr_sharedRNA20)  
```

```{r making DOX 2kb and 20kb bedfiles, eval=FALSE}
output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"
DOX_24_DAR_2kb <- annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)
  

DOX_24_notDAR_2kb <- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_24_DAR_20kb<- annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_24_notDAR_20kb<- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

# Now convert to GRanges
DOX_24_DAR_2kb_gr <- GRanges(
  seqnames = DOX_24_DAR_2kb$seqnames,
  ranges = IRanges(start = DOX_24_DAR_2kb$start, end = DOX_24_DAR_2kb$end),
  mcols = DOX_24_DAR_2kb %>% select(-seqnames, -start, -end)
)

DOX_24_notDAR_2kb_gr <- GRanges(
  seqnames = DOX_24_notDAR_2kb$seqnames,
  ranges = IRanges(start = DOX_24_notDAR_2kb$start, end = DOX_24_notDAR_2kb$end),
  mcols = DOX_24_notDAR_2kb %>% select(-seqnames, -start, -end)
)

DOX_24_DAR_20kb_gr <- GRanges(
  seqnames = DOX_24_DAR_20kb$seqnames,
  ranges = IRanges(start = DOX_24_DAR_20kb$start, end = DOX_24_DAR_20kb$end),
  mcols = DOX_24_DAR_20kb %>% select(-seqnames, -start, -end)
)

DOX_24_notDAR_20kb_gr <- GRanges(
  seqnames = DOX_24_notDAR_20kb$seqnames,
  ranges = IRanges(start = DOX_24_notDAR_20kb$start, end = DOX_24_notDAR_20kb$end),
  mcols = DOX_24_notDAR_20kb %>% select(-seqnames, -start, -end)
)


DOX_DAR_list_gr <- list("DOX_24_DAR_2kb"=DOX_24_DAR_2kb_gr,
                        "DOX_24_notDAR_2kb"=DOX_24_notDAR_2kb_gr,
                        "DOX_24_DAR_20kb"=DOX_24_DAR_20kb_gr,
                        "DOX_24_notDAR_20kb"=DOX_24_notDAR_20kb_gr)
for (name in names(DOX_DAR_list_gr)) {
  gr <- DOX_DAR_list_gr[[name]]

  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")

  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_centered.bed")), format = "BED")
}


```


##### making DOX bedfiles  


```{r making DOX 2kb and 20kb bedfiles, eval=FALSE}
output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"
DOX_24_DAR_2kb <- annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)
  

DOX_24_notDAR_2kb <- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_24_DAR_20kb<- annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_24_notDAR_20kb<- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

# Now convert to GRanges
DOX_24_DAR_2kb_gr <- GRanges(
  seqnames = DOX_24_DAR_2kb$seqnames,
  ranges = IRanges(start = DOX_24_DAR_2kb$start, end = DOX_24_DAR_2kb$end),
  mcols = DOX_24_DAR_2kb %>% select(-seqnames, -start, -end)
)

DOX_24_notDAR_2kb_gr <- GRanges(
  seqnames = DOX_24_notDAR_2kb$seqnames,
  ranges = IRanges(start = DOX_24_notDAR_2kb$start, end = DOX_24_notDAR_2kb$end),
  mcols = DOX_24_notDAR_2kb %>% select(-seqnames, -start, -end)
)

DOX_24_DAR_20kb_gr <- GRanges(
  seqnames = DOX_24_DAR_20kb$seqnames,
  ranges = IRanges(start = DOX_24_DAR_20kb$start, end = DOX_24_DAR_20kb$end),
  mcols = DOX_24_DAR_20kb %>% select(-seqnames, -start, -end)
)

DOX_24_notDAR_20kb_gr <- GRanges(
  seqnames = DOX_24_notDAR_20kb$seqnames,
  ranges = IRanges(start = DOX_24_notDAR_20kb$start, end = DOX_24_notDAR_20kb$end),
  mcols = DOX_24_notDAR_20kb %>% select(-seqnames, -start, -end)
)


DOX_DAR_list_gr <- list("DOX_24_DAR_2kb"=DOX_24_DAR_2kb_gr,
                        "DOX_24_notDAR_2kb"=DOX_24_notDAR_2kb_gr,
                        "DOX_24_DAR_20kb"=DOX_24_DAR_20kb_gr,
                        "DOX_24_notDAR_20kb"=DOX_24_notDAR_20kb_gr)
for (name in names(DOX_DAR_list_gr)) {
  gr <- DOX_DAR_list_gr[[name]]

  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")

  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_centered.bed")), format = "BED")
}


```

##### making EPI bedfiles

```{r EPI dataframes}
EPI_24_DAR <- all_results %>% 
  dplyr::filter(source =="EPI_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
EPI_3_DAR <- all_results %>% 
  dplyr::filter(source =="EPI_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)


EPI_24_DAR_up <- all_results %>% 
  dplyr::filter(source =="EPI_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
  dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
EPI_3_DAR_up <- all_results %>% 
  dplyr::filter(source =="EPI_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
   dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
EPI_24_DAR_down <- all_results %>% 
  dplyr::filter(source =="EPI_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
EPI_3_DAR_down <- all_results %>% 
  dplyr::filter(source =="EPI_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
```

```{r making EPI 2kb and 20kb bedfiles, eval=FALSE}
output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"
EPI_24_DAR_2kb <- annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)
  

EPI_24_notDAR_2kb <- annotated_regions %>% 
  dplyr::filter(!Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

EPI_24_DAR_20kb<- annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

EPI_24_notDAR_20kb<- annotated_regions %>% 
  dplyr::filter(!Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

# Now convert to GRanges
EPI_24_DAR_2kb_gr <- GRanges(
  seqnames = EPI_24_DAR_2kb$seqnames,
  ranges = IRanges(start = EPI_24_DAR_2kb$start, end = EPI_24_DAR_2kb$end),
  mcols = EPI_24_DAR_2kb %>% select(-seqnames, -start, -end)
)

EPI_24_notDAR_2kb_gr <- GRanges(
  seqnames = EPI_24_notDAR_2kb$seqnames,
  ranges = IRanges(start = EPI_24_notDAR_2kb$start, end = EPI_24_notDAR_2kb$end),
  mcols = EPI_24_notDAR_2kb %>% select(-seqnames, -start, -end)
)

EPI_24_DAR_20kb_gr <- GRanges(
  seqnames = EPI_24_DAR_20kb$seqnames,
  ranges = IRanges(start = EPI_24_DAR_20kb$start, end = EPI_24_DAR_20kb$end),
  mcols = EPI_24_DAR_20kb %>% select(-seqnames, -start, -end)
)

EPI_24_notDAR_20kb_gr <- GRanges(
  seqnames = EPI_24_notDAR_20kb$seqnames,
  ranges = IRanges(start = EPI_24_notDAR_20kb$start, end = EPI_24_notDAR_20kb$end),
  mcols = EPI_24_notDAR_20kb %>% select(-seqnames, -start, -end)
)


EPI_DAR_list_gr <- list("EPI_24_DAR_2kb"=EPI_24_DAR_2kb_gr,
                        "EPI_24_notDAR_2kb"=EPI_24_notDAR_2kb_gr,
                        "EPI_24_DAR_20kb"=EPI_24_DAR_20kb_gr,
                        "EPI_24_notDAR_20kb"=EPI_24_notDAR_20kb_gr)
for (name in names(EPI_DAR_list_gr)) {
  gr <- EPI_DAR_list_gr[[name]]

  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")

  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_centered.bed")), format = "BED")
}


```

##### making DNR bedfiles

```{r DNR dataframes}
DNR_24_DAR <- all_results %>% 
  dplyr::filter(source =="DNR_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
DNR_3_DAR <- all_results %>% 
  dplyr::filter(source =="DNR_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)

DNR_24_DAR_up <- all_results %>% 
  dplyr::filter(source =="DNR_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
  dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
DNR_3_DAR_up <- all_results %>% 
  dplyr::filter(source =="DNR_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
   dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
DNR_24_DAR_down <- all_results %>% 
  dplyr::filter(source =="DNR_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
DNR_3_DAR_down <- all_results %>% 
  dplyr::filter(source =="DNR_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
```

```{r making DNR 2kb and 20kb bedfiles, eval=FALSE}
output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"
DNR_24_DAR_2kb <- annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)
  

DNR_24_notDAR_2kb <- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DNR_24_DAR_20kb<- annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DNR_24_notDAR_20kb<- annotated_regions %>% 
  dplyr::filter(!Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

# Now convert to GRanges
DNR_24_DAR_2kb_gr <- GRanges(
  seqnames = DNR_24_DAR_2kb$seqnames,
  ranges = IRanges(start = DNR_24_DAR_2kb$start, end = DNR_24_DAR_2kb$end),
  mcols = DNR_24_DAR_2kb %>% select(-seqnames, -start, -end)
)

DNR_24_notDAR_2kb_gr <- GRanges(
  seqnames = DNR_24_notDAR_2kb$seqnames,
  ranges = IRanges(start = DNR_24_notDAR_2kb$start, end = DNR_24_notDAR_2kb$end),
  mcols = DNR_24_notDAR_2kb %>% select(-seqnames, -start, -end)
)

DNR_24_DAR_20kb_gr <- GRanges(
  seqnames = DNR_24_DAR_20kb$seqnames,
  ranges = IRanges(start = DNR_24_DAR_20kb$start, end = DNR_24_DAR_20kb$end),
  mcols = DNR_24_DAR_20kb %>% select(-seqnames, -start, -end)
)

DNR_24_notDAR_20kb_gr <- GRanges(
  seqnames = DNR_24_notDAR_20kb$seqnames,
  ranges = IRanges(start = DNR_24_notDAR_20kb$start, end = DNR_24_notDAR_20kb$end),
  mcols = DNR_24_notDAR_20kb %>% select(-seqnames, -start, -end)
)


DNR_DAR_list_gr <- list("DNR_24_DAR_2kb"=DNR_24_DAR_2kb_gr,
                        "DNR_24_notDAR_2kb"=DNR_24_notDAR_2kb_gr,
                        "DNR_24_DAR_20kb"=DNR_24_DAR_20kb_gr,
                        "DNR_24_notDAR_20kb"=DNR_24_notDAR_20kb_gr)
for (name in names(DNR_DAR_list_gr)) {
  gr <- DNR_DAR_list_gr[[name]]

  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")

  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_centered.bed")), format = "BED")
}


```

##### making MTX bedfiles

```{r MTX dataframes}
MTX_24_DAR <- all_results %>% 
  dplyr::filter(source =="MTX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
MTX_3_DAR <- all_results %>% 
  dplyr::filter(source =="MTX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)


MTX_24_DAR_up <- all_results %>% 
  dplyr::filter(source =="MTX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
  dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
MTX_3_DAR_up <- all_results %>% 
  dplyr::filter(source =="MTX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
   dplyr::filter(logFC>0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
MTX_24_DAR_down <- all_results %>% 
  dplyr::filter(source =="MTX_24") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
MTX_3_DAR_down <- all_results %>% 
  dplyr::filter(source =="MTX_3") %>% 
  dplyr::filter(adj.P.Val<0.05) %>%
   dplyr::filter(logFC<0) %>% 
  distinct(genes) %>% 
  dplyr::rename("Peakid"=genes)
```

```{r making MTX 2kb and 20kb bedfiles, eval=FALSE}
output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"
MTX_24_DAR_2kb <- annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)
  

MTX_24_notDAR_2kb <- annotated_regions %>% 
  dplyr::filter(!Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

MTX_24_DAR_20kb<- annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

MTX_24_notDAR_20kb<- annotated_regions %>% 
  dplyr::filter(!Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000)%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

# Now convert to GRanges
MTX_24_DAR_2kb_gr <- GRanges(
  seqnames = MTX_24_DAR_2kb$seqnames,
  ranges = IRanges(start = MTX_24_DAR_2kb$start, end = MTX_24_DAR_2kb$end),
  mcols = MTX_24_DAR_2kb %>% select(-seqnames, -start, -end)
)

MTX_24_notDAR_2kb_gr <- GRanges(
  seqnames = MTX_24_notDAR_2kb$seqnames,
  ranges = IRanges(start = MTX_24_notDAR_2kb$start, end = MTX_24_notDAR_2kb$end),
  mcols = MTX_24_notDAR_2kb %>% select(-seqnames, -start, -end)
)

MTX_24_DAR_20kb_gr <- GRanges(
  seqnames = MTX_24_DAR_20kb$seqnames,
  ranges = IRanges(start = MTX_24_DAR_20kb$start, end = MTX_24_DAR_20kb$end),
  mcols = MTX_24_DAR_20kb %>% select(-seqnames, -start, -end)
)

MTX_24_notDAR_20kb_gr <- GRanges(
  seqnames = MTX_24_notDAR_20kb$seqnames,
  ranges = IRanges(start = MTX_24_notDAR_20kb$start, end = MTX_24_notDAR_20kb$end),
  mcols = MTX_24_notDAR_20kb %>% select(-seqnames, -start, -end)
)


MTX_DAR_list_gr <- list("MTX_24_DAR_2kb"=MTX_24_DAR_2kb_gr,
                        "MTX_24_notDAR_2kb"=MTX_24_notDAR_2kb_gr,
                        "MTX_24_DAR_20kb"=MTX_24_DAR_20kb_gr,
                        "MTX_24_notDAR_20kb"=MTX_24_notDAR_20kb_gr)
for (name in names(MTX_DAR_list_gr)) {
  gr <- MTX_DAR_list_gr[[name]]

  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")

  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_centered.bed")), format = "BED")
}


```

### Extracting top DAR-DEG BED files
```{r DOX-DEG}
DOX_3_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DOX_3_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


DOX_3_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DOX_3_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r EPI_deg}
EPI_3_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

EPI_3_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


EPI_3_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

EPI_3_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r DNR-DEG}
DNR_3_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DNR_3_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


DNR_3_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DNR_3_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r MTX-DEG}
MTX_3_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

MTX_3_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


MTX_3_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

MTX_3_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r collect DAR-DEG data frames}
df_names_DAR_DEGS <- ls(pattern = ".*_DAR_DEG_.*kb$")

df_names_DAR_nonDEGS <- ls(pattern = ".*_DAR_nonDEG_.*kb$")


df_list_DAR_DEGS <- mget(df_names_DAR_DEGS)

df_list_DAR_nonDEGS <- mget(df_names_DAR_nonDEGS)


# Step 3: Convert each dataframe to GRanges

gr_list_DAR_DEGS <- lapply(df_list_DAR_DEGS, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

gr_list_DAR_nonDEGS <- lapply(df_list_DAR_nonDEGS, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

# Optional: Name the GRanges list same as original data frames

names(gr_list_DAR_DEGS) <- df_names_DAR_DEGS
names(gr_list_DAR_nonDEGS) <- df_names_DAR_nonDEGS
```


```{r exporting bed files, eval=FALSE}
# Folder with input BED files

output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"

# Create output folder if needed
dir.create(output_dir, showWarnings = FALSE)

# Loop through each BED file
for (name in names(gr_list_DAR_DEGS)) {
  gr <- gr_list_DAR_DEGS[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "DAR_DEG_centered.bed")), format = "BED")
}


### not significant DAR regions for xstreme

for (name in names(gr_list_DAR_nonDEGS)) {
  gr <- gr_list_DAR_nonDEGS[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "DAR_nonDEG_centered.bed")), format = "BED")
}

```



#### 24hour 2kb 20kb DAR_DEG bed files

```{r DOX-DEG_24}
DOX_24_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DOX_24_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


DOX_24_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DOX_24_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r EPI_deg_24}
EPI_24_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

EPI_24_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


EPI_24_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

EPI_24_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r DNR-DEG_24}
DNR_24_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DNR_24_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


DNR_24_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

DNR_24_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r MTX-DEG_24}
MTX_24_DAR_DEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

MTX_24_DAR_nonDEG_2kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS<2000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")


MTX_24_DAR_DEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA")

MTX_24_DAR_nonDEG_20kb <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS<20000) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA")
```

```{r collect DAR-DEG data frames}
df_names_DAR_DEGS <- ls(pattern = ".*_DAR_DEG_.*kb$")

df_names_DAR_nonDEGS <- ls(pattern = ".*_DAR_nonDEG_.*kb$")


df_list_DAR_DEGS <- mget(df_names_DAR_DEGS)

df_list_DAR_nonDEGS <- mget(df_names_DAR_nonDEGS)


# Step 3: Convert each dataframe to GRanges

gr_list_DAR_DEGS <- lapply(df_list_DAR_DEGS, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

gr_list_DAR_nonDEGS <- lapply(df_list_DAR_nonDEGS, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

# Optional: Name the GRanges list same as original data frames

names(gr_list_DAR_DEGS) <- df_names_DAR_DEGS
names(gr_list_DAR_nonDEGS) <- df_names_DAR_nonDEGS
```


```{r exporting bed files, eval=FALSE}
# Folder with input BED files

output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"

# Create output folder if needed
dir.create(output_dir, showWarnings = FALSE)

# Loop through each BED file
for (name in names(gr_list_DAR_DEGS)) {
  gr <- gr_list_DAR_DEGS[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "DAR_DEG_centered.bed")), format = "BED")
}


### not significant DAR regions for xstreme

for (name in names(gr_list_DAR_nonDEGS)) {
  gr <- gr_list_DAR_nonDEGS[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "DAR_nonDEG_centered.bed")), format = "BED")
}

```

#### up down DAR DEG  ( just DAR_DEG DAR_nonDEG up and down)
```{r DOX_DAR_DEG 3 and 24 only}
DOX_24_up_DAR_DEG <-
  annotated_regions %>%
  dplyr::filter(Peakid %in%DOX_24_DAR_up$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(geneId %in% RNA_24_DOX_DEG$ENTREZID)


DOX_24_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
   dplyr::filter(!geneId %in% RNA_24_DOX_DEG$ENTREZID)

DOX_3_up_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_DOX_DEG$ENTREZID)

DOX_3_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_DOX_DEG$ENTREZID)

DOX_24_down_DAR_DEG <-  annotated_regions %>%
  dplyr::filter(Peakid %in%DOX_24_DAR_down$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_24_DOX_DEG$ENTREZID)

DOX_24_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_24_DOX_DEG$ENTREZID)

DOX_3_down_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_DOX_DEG$ENTREZID)

DOX_3_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_DOX_DEG$ENTREZID)



```

```{r EPI_DAR_DEG 3 and 24 only}
EPI_24_up_DAR_DEG <-
  annotated_regions %>%
  dplyr::filter(Peakid %in% EPI_24_DAR_up$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(geneId %in% RNA_24_EPI_DEG$ENTREZID)


EPI_24_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in% EPI_24_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
   dplyr::filter(!geneId %in% RNA_24_EPI_DEG$ENTREZID)

EPI_3_up_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_EPI_DEG$ENTREZID)

EPI_3_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_EPI_DEG$ENTREZID)

EPI_24_down_DAR_DEG <-  annotated_regions %>%
  dplyr::filter(Peakid %in%EPI_24_DAR_down$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_24_EPI_DEG$ENTREZID)

EPI_24_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_24_EPI_DEG$ENTREZID)

EPI_3_down_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_EPI_DEG$ENTREZID)

EPI_3_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_EPI_DEG$ENTREZID)



```


```{r DNR_DAR_DEG 3 and 24 only}
DNR_24_up_DAR_DEG <-
  annotated_regions %>%
  dplyr::filter(Peakid %in%DNR_24_DAR_up$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(geneId %in% RNA_24_DNR_DEG$ENTREZID)


DNR_24_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
   dplyr::filter(!geneId %in% RNA_24_DNR_DEG$ENTREZID)

DNR_3_up_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_DNR_DEG$ENTREZID)

DNR_3_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_DNR_DEG$ENTREZID)

DNR_24_down_DAR_DEG <-  annotated_regions %>%
  dplyr::filter(Peakid %in%DNR_24_DAR_down$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_24_DNR_DEG$ENTREZID)

DNR_24_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_24_DNR_DEG$ENTREZID)

DNR_3_down_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_DNR_DEG$ENTREZID)

DNR_3_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_DNR_DEG$ENTREZID)



```


```{r MTX_DAR_DEG 3 and 24 only}
MTX_24_up_DAR_DEG <-
  annotated_regions %>%
  dplyr::filter(Peakid %in%MTX_24_DAR_up$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(geneId %in% RNA_24_MTX_DEG$ENTREZID)


MTX_24_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
   dplyr::filter(!geneId %in% RNA_24_MTX_DEG$ENTREZID)

MTX_3_up_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_MTX_DEG$ENTREZID)

MTX_3_up_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR_up$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_MTX_DEG$ENTREZID)

MTX_24_down_DAR_DEG <-  annotated_regions %>%
  dplyr::filter(Peakid %in%MTX_24_DAR_down$Peakid )%>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_24_MTX_DEG$ENTREZID)

MTX_24_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_24_MTX_DEG$ENTREZID)

MTX_3_down_DAR_DEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="exp_RNA") %>% 
  dplyr::filter(geneId %in% RNA_3_MTX_DEG$ENTREZID)

MTX_3_down_DAR_nonDEG <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR_down$Peakid ) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) %>% 
  dplyr::filter(RNA_expressed=="not_exp_RNA") %>% 
  dplyr::filter(!geneId %in% RNA_3_MTX_DEG$ENTREZID)



```



```{r}

df_names_DAR_DEGs <- ls(pattern = ".*_DAR_DEG")

df_names_DAR_nonDEGs <- ls(pattern = ".*_DAR_nonDEG")


df_list_DAR_DEGs<- mget(df_names_DAR_DEGs)

df_list_DAR_nonDEGs <- mget(df_names_DAR_nonDEGs)


# Step 3: Convert each dataframe to GRanges

gr_list_DAR_DEG <- lapply(df_list_DAR_DEGs, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

gr_list_DAR_nonDEG <- lapply(df_list_DAR_nonDEGs, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

# Optional: Name the GRanges list same as original data frames

names(gr_list_DAR_DEG) <- df_names_DAR_DEGs
names(gr_list_DAR_nonDEG) <- df_names_DAR_nonDEGs
```

```{r exporting bed files, eval=FALSE}
# Folder with input BED files

output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"

# Create output folder if needed
dir.create(output_dir, showWarnings = FALSE)

# Loop through each BED file
for (name in names(gr_list_DAR_DEG)) {
  gr <- gr_list_DAR_DEG[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_DEGcentered.bed")), format = "BED")
}


### not significant DAR regions for xstreme

for (name in names(gr_list_DAR_nonDEG)) {
  gr <- gr_list_DAR_nonDEG[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_DEGcentered.bed")), format = "BED")
}

```

##### REAL DAR DEG by time/trt  

```{r DOX-DEG_24}
DOX_24_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_24_DOX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) 

DOX_24_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_24_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_24_DOX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_3_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_3_DOX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DOX_3_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DOX_3_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_3_DOX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

```


```{r EPI-DEG_24}
EPI_24_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_24_EPI_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) 

EPI_24_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_24_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_24_EPI_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

EPI_3_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_3_EPI_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

EPI_3_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%EPI_3_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_3_EPI_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

```


```{r DNR-DEG_24}
DNR_24_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_24_DNR_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) 

DNR_24_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_24_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_24_DNR_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DNR_3_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_3_DNR_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

DNR_3_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%DNR_3_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_3_DNR_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

```


```{r MTX-DEG_24}
MTX_24_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_24_MTX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE) 

MTX_24_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_24_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_24_MTX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

MTX_3_DD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(geneId %in% RNA_3_MTX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

MTX_3_nDD <-
  annotated_regions %>% 
  dplyr::filter(Peakid %in%MTX_3_DAR$Peakid ) %>% 
  dplyr::filter(!geneId %in% RNA_3_MTX_DEG$ENTREZID) %>% 
  separate(Peakid, into = c("seqnames", "start", "end"), sep = "\\.", convert = TRUE, remove=FALSE)

```  


```{r}

df_names_DD <- ls(pattern = ".*_DD")

df_names_nDD <- ls(pattern = ".*_nDD")


df_list_DD<- mget(df_names_DD)

df_list_nDD <- mget(df_names_nDD)


# Step 3: Convert each dataframe to GRanges

gr_list_DD <- lapply(df_list_DD, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

gr_list_nDD <- lapply(df_list_nDD, function(df) {
  GRanges(
    seqnames = df$seqnames,
    ranges = IRanges(start = df$start, end = df$end),
    mcols = df %>% select(-seqnames, -start, -end)
  )
})

# Optional: Name the GRanges list same as original data frames

names(gr_list_DD) <- df_names_DD
names(gr_list_nDD) <- df_names_nDD
```  


```{r exporting bed files DD, eval=FALSE}
# Folder with input BED files

output_dir <- "data/Final_four_data/re_analysis/motif_beds_centered"

# Create output folder if needed
dir.create(output_dir, showWarnings = FALSE)

# Loop through each BED file
for (name in names(gr_list_DD)) {
  gr <- gr_list_DD[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_realcentered.bed")), format = "BED")
}


### not significant DAR regions for xstreme

for (name in names(gr_list_nDD)) {
  gr <- gr_list_nDD[[name]]
  
  # Recenter each region to 200 bp around its midpoint
  gr_centered <- resize(gr, width = 200, fix = "center")
  
  # Export to BED (auto converts to 0-based)
  export(gr_centered, con = file.path(output_dir, paste0(name, "_realcentered.bed")), format = "BED")
}

```
