---
title: "AF_HF_SNPs"
author: "Renee Matthews"
date: "2025-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(ggfortify)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(ggVennDiagram)
library(BiocParallel)
library(ggpubr)
library(edgeR)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(ComplexHeatmap)
library(cowplot)
library(smplot2)
library(readxl)
library(devtools)
library(vargen)
library(liftOver)

```


Loading Atrial Fibrillation and Heart Failure SNPs and I
```{r data loading}
gwas_HF <- readRDS("data/other_papers/HF_gwas_association_downloaded_2025_01_23_EFO_0003144_withChildTraits.RDS")

gwas_ARR <- readRDS("data/other_papers/AF_gwas_association_downloaded_2025_01_23_EFO_0000275.RDS")

gwas_IHD   <- readRDS("data/other_papers/IHD_IHD_gwas_association_downloaded_2025_06_26_EFO_1001375_withChildTraits")
gwas_CAD <- readRDS( "data/CAD_gwas_dataframe.RDS")
gwas_ACresp <- readRDS("data/gwas_3_dataframe.RDS")
Short_gwas_gr <-
  gwas_ARR %>% 
          distinct(SNPS,.keep_all = TRUE) %>%
          dplyr::select(CHR_ID, CHR_POS,SNPS) %>% 
          mutate(gwas="AF") %>% 
   rbind(gwas_HF %>% 
          distinct(SNPS,.keep_all = TRUE) %>%
          dplyr::select(CHR_ID, CHR_POS,SNPS) %>% 
          mutate(gwas="HF")) %>% 
  rbind(gwas_IHD %>% 
          distinct(SNPS,.keep_all = TRUE) %>%
          dplyr::select(CHR_ID, CHR_POS,SNPS) %>% 
          mutate(gwas="IHD")) %>% 
  rbind(gwas_CAD %>% 
          distinct(SNPS,.keep_all = TRUE) %>%
          dplyr::select(CHR_ID, CHR_POS,SNPS) %>% 
          mutate(gwas="CAD")) %>% 
  
  na.omit() %>% 
 mutate(seqnames=paste0("chr",CHR_ID), CHR_POS=as.numeric(CHR_POS)) %>% 
  na.omit() %>%
   mutate(start=CHR_POS, end=CHR_POS, width=1) %>% 
  GRanges()
# gwas_CAD %>% 
#   distinct(SNPS)


```

Loading ATAC-seq regions

```{r}
toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

DOX_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DOX_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

EPI_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="EPI_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

EPI_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="EPI_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DNR_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DNR_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DNR_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DNR_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

MTX_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="MTX_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

MTX_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="MTX_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

all_regions_gr <- all_results %>%
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_3") %>% 
  distinct(Peakid) %>% 
  separate_wider_delim(., cols="Peakid",names = c("seqnames","start","end"), delim= ".", cols_remove = FALSE) %>% 
  makeGRangesFromDataFrame(.,keep.extra.columns=TRUE) 

all_regions_peak <- all_results %>%
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_3") %>% 
  distinct(Peakid) 


```


Overlapping ATAC regions and SNPs

```{r overlapping regions and SNPs af}

AF_ol_peaks <-   join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() %>% 
  dplyr::filter(gwas =="AF") %>% 
  distinct(Peakid)

HF_ol_peaks <-   join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() %>% 
  dplyr::filter(gwas =="HF") %>% 
  distinct(Peakid)

IHD_ol_peaks <-   join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() %>% 
  dplyr::filter(gwas =="IHD") %>% 
  distinct(Peakid)

CAD_ol_peaks <-   join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() %>% 
  dplyr::filter(gwas =="CAD") %>% 
  distinct(Peakid)
HF_AF_ol <- join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() %>% 
  dplyr::filter(gwas =="AF"|gwas=="HF")

SNP_overlaps <- join_overlap_inner(all_regions_gr, Short_gwas_gr) %>%
  as.data.frame() #%>% saveRDS(., 
                  # "data/Final_four_data/re_analysis/GWAS_overlaps_dataframe.RDS")
```


```{r overlapping regions and SNPs}

gwas_annote_df <-all_regions_peak %>%
  mutate(AF_status=case_when(Peakid %in% AF_ol_peaks$Peakid ~"AF_peak",
                              TRUE~ "not_AF_peak"),
         HF_status=case_when(Peakid %in% HF_ol_peaks$Peakid ~"HF_peak",
                              TRUE~ "not_HF_peak"),
          CAD_status=case_when(Peakid %in% CAD_ol_peaks$Peakid ~"CAD_peak",
                              TRUE~ "not_CAD_peak"),
         IHD_status=case_when(Peakid %in% IHD_ol_peaks$Peakid ~"IHD_peak",
                              TRUE~ "not_IHD_peak")) %>% 
  mutate(DOX_3=case_when(Peakid %in% DOX_3_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(DOX_24=case_when(Peakid %in% DOX_24_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(EPI_3=case_when(Peakid %in% EPI_3_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(EPI_24=case_when(Peakid %in% EPI_24_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(DNR_3=case_when(Peakid %in% DNR_3_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(DNR_24=case_when(Peakid %in% DNR_24_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(MTX_3=case_when(Peakid %in% MTX_3_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) %>% 
  mutate(MTX_24=case_when(Peakid %in% MTX_24_sig$Peakid ~"sig_peak",
                              TRUE~ "not_sig_peak")) 
 
# saveRDS(gwas_annote_df,"data/Final_four_data/re_analysis/GWAS_SNP_annotations.RDS")
 
```
Testing for enrichment:
### DOX enrichment tests

```{r AF DOX_DAR 3 enrichment}
 gwas_annote_df %>% 
  group_by(DOX_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  print() %>% 
  column_to_rownames("DOX_3") %>% 
  chisq.test(.)
DOX_darsnp_3_AF <- gwas_annote_df %>%
  group_by(DOX_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)


```

```{r AF DOX_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(DOX_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DOX_24)) %>% 
  print() %>% 
  column_to_rownames("DOX_24") %>% 
  chisq.test(.)

DOX_darsnp_24_AF <-  gwas_annote_df %>% 
  group_by(DOX_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DOX_24)) %>% 
  column_to_rownames("DOX_24") %>% 
  fisher.test(.)
```


```{r HF DOX_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(DOX_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  print() %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)

DOX_darsnp_3_HF <- gwas_annote_df %>% 
  group_by(DOX_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)

```


```{r HF DOX_DAR 24 enrichment}
gwas_annote_df %>%
  group_by(DOX_24,HF_status) %>%
  tally() %>%
  pivot_wider(., DOX_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(DOX_24)) %>%
  print() %>%
  column_to_rownames("DOX_24") %>%
  chisq.test(.)

DOX_darsnp_24_HF <- gwas_annote_df %>%
  group_by(DOX_24,HF_status) %>%
  tally() %>%
  pivot_wider(., DOX_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(DOX_24)) %>%
  column_to_rownames("DOX_24") %>%
  fisher.test(.)


```


```{r IHD DOX_DAR 3 enrichment}
gwas_annote_df %>% 
  group_by(DOX_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DOX_3))%>% 
  print() %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)

DOX_darsnp_3_IHD <- gwas_annote_df %>% 
  group_by(DOX_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DOX_3))%>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)
```


```{r IHD DOX_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(DOX_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DOX_24)) %>% 
  print() %>% 
  column_to_rownames("DOX_24") %>% 
  fisher.test(.)

DOX_darsnp_24_IHD <- gwas_annote_df %>% 
  group_by(DOX_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DOX_24)) %>% 
  column_to_rownames("DOX_24") %>% 
  fisher.test(.)
```

```{r CAD DOX_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(DOX_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  print() %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)

DOX_darsnp_3_CAD <- gwas_annote_df %>% 
  group_by(DOX_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DOX_3)) %>% 
  column_to_rownames("DOX_3") %>% 
  fisher.test(.)

```

```{r CAD DOX_DAR 24enrichment}
gwas_annote_df %>% 
  group_by(DOX_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DOX_24)) %>% 
  print() %>% 
  column_to_rownames("DOX_24") %>% 
  chisq.test(.)

DOX_darsnp_24_CAD <- gwas_annote_df %>% 
  group_by(DOX_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DOX_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DOX_24)) %>% 
  column_to_rownames("DOX_24") %>% 
  fisher.test(.)

```


### EPI enrichment tests

```{r AF EPI_DAR 3 enrichment}
 gwas_annote_df %>% 
  group_by(EPI_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  print() %>% 
  column_to_rownames("EPI_3") %>% 
  chisq.test(.)
EPI_darsnp_3_AF <- gwas_annote_df %>%
  group_by(EPI_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)
```

```{r AF EPI_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(EPI_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(EPI_24)) %>% 
  print() %>% 
  column_to_rownames("EPI_24") %>% 
 chisq.test(.)

EPI_darsnp_24_AF <-  gwas_annote_df %>% 
  group_by(EPI_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(EPI_24)) %>% 
  column_to_rownames("EPI_24") %>% 
  fisher.test(.)
```


```{r HF EPI_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(EPI_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  print() %>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)

EPI_darsnp_3_HF <- gwas_annote_df %>% 
  group_by(EPI_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)

```


```{r HF EPI_DAR 24 enrichment}
gwas_annote_df %>%
  group_by(EPI_24,HF_status) %>%
  tally() %>%
  pivot_wider(., EPI_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(EPI_24)) %>%
  print() %>%
  column_to_rownames("EPI_24") %>%
  chisq.test(.)

EPI_darsnp_24_HF <- gwas_annote_df %>%
  group_by(EPI_24,HF_status) %>%
  tally() %>%
  pivot_wider(., EPI_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(EPI_24)) %>%
  column_to_rownames("EPI_24") %>%
  fisher.test(.)


```


```{r IHD EPI_DAR 3 enrichment}
gwas_annote_df %>% 
  group_by(EPI_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(EPI_3))%>% 
  print() %>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)

EPI_darsnp_3_IHD <- gwas_annote_df %>% 
  group_by(EPI_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(EPI_3))%>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)
```


```{r IHD EPI_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(EPI_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(EPI_24)) %>% 
  print() %>% 
  column_to_rownames("EPI_24") %>% 
  fisher.test(.)

EPI_darsnp_24_IHD <- gwas_annote_df %>% 
  group_by(EPI_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(EPI_24)) %>% 
  column_to_rownames("EPI_24") %>% 
  fisher.test(.)
```

```{r CAD EPI_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(EPI_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  print() %>% 
  column_to_rownames("EPI_3") %>% 
  chisq.test(.)

EPI_darsnp_3_CAD <- gwas_annote_df %>% 
  group_by(EPI_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(EPI_3)) %>% 
  column_to_rownames("EPI_3") %>% 
  fisher.test(.)

```

```{r CAD EPI_DAR 24enrichment}
gwas_annote_df %>% 
  group_by(EPI_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(EPI_24)) %>% 
  print() %>% 
  column_to_rownames("EPI_24") %>% 
 chisq.test(.)

EPI_darsnp_24_CAD <- gwas_annote_df %>% 
  group_by(EPI_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., EPI_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(EPI_24)) %>% 
  column_to_rownames("EPI_24") %>% 
  fisher.test(.)

```



### DNR enrichment tests

```{r AF DNR_DAR 3 enrichment}
 gwas_annote_df %>% 
  group_by(DNR_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  print() %>% 
  column_to_rownames("DNR_3") %>% 
  chisq.test(.)
DNR_darsnp_3_AF <- gwas_annote_df %>%
  group_by(DNR_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)
```

```{r AF DNR_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(DNR_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DNR_24)) %>% 
  print() %>% 
  column_to_rownames("DNR_24") %>% 
  chisq.test(.)

DNR_darsnp_24_AF <-  gwas_annote_df %>% 
  group_by(DNR_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(DNR_24)) %>% 
  column_to_rownames("DNR_24") %>% 
  fisher.test(.)
```


```{r HF DNR_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(DNR_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  print() %>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)

DNR_darsnp_3_HF <- gwas_annote_df %>% 
  group_by(DNR_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)

```


```{r HF DNR_DAR 24 enrichment}
gwas_annote_df %>%
  group_by(DNR_24,HF_status) %>%
  tally() %>%
  pivot_wider(., DNR_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(DNR_24)) %>%
  print() %>%
  column_to_rownames("DNR_24") %>%
  fisher.test(.)

DNR_darsnp_24_HF <- gwas_annote_df %>%
  group_by(DNR_24,HF_status) %>%
  tally() %>%
  pivot_wider(., DNR_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(DNR_24)) %>%
  column_to_rownames("DNR_24") %>%
  fisher.test(.)


```


```{r IHD DNR_DAR 3 enrichment}
gwas_annote_df %>% 
  group_by(DNR_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DNR_3))%>% 
  print() %>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)

DNR_darsnp_3_IHD <- gwas_annote_df %>% 
  group_by(DNR_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DNR_3))%>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)
```


```{r IHD DNR_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(DNR_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DNR_24)) %>% 
  print() %>% 
  column_to_rownames("DNR_24") %>% 
  fisher.test(.)

DNR_darsnp_24_IHD <- gwas_annote_df %>% 
  group_by(DNR_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(DNR_24)) %>% 
  column_to_rownames("DNR_24") %>% 
  fisher.test(.)
```
```{r CAD DNR_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(DNR_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  print() %>% 
  column_to_rownames("DNR_3") %>% 
  chisq.test(.)

DNR_darsnp_3_CAD <- gwas_annote_df %>% 
  group_by(DNR_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_3, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DNR_3)) %>% 
  column_to_rownames("DNR_3") %>% 
  fisher.test(.)

```

```{r CAD DNR_DAR 24enrichment}
gwas_annote_df %>% 
  group_by(DNR_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DNR_24)) %>% 
  print() %>% 
  column_to_rownames("DNR_24") %>% 
  chisq.test(.)

DNR_darsnp_24_CAD <- gwas_annote_df %>% 
  group_by(DNR_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., DNR_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(DNR_24)) %>% 
  column_to_rownames("DNR_24") %>% 
  fisher.test(.)

```


### MTX enrichment tests

```{r AF MTX_DAR 3 enrichment}
 gwas_annote_df %>% 
  group_by(MTX_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = AF_status, values_from = n,values_fill = 0) %>% 
  arrange(desc(MTX_3)) %>% 
  print() %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)
MTX_darsnp_3_AF <- gwas_annote_df %>%
  group_by(MTX_3,AF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = AF_status, values_from = n,values_fill = 0) %>% 
  arrange(desc(MTX_3)) %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)
```

```{r AF MTX_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(MTX_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(MTX_24)) %>% 
  print() %>% 
  column_to_rownames("MTX_24") %>% 
  chisq.test(.)

MTX_darsnp_24_AF <-  gwas_annote_df %>% 
  group_by(MTX_24,AF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = AF_status, values_from = n) %>% 
  arrange(desc(MTX_24)) %>% 
  column_to_rownames("MTX_24") %>% 
  fisher.test(.)
```


```{r HF MTX_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(MTX_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(MTX_3)) %>% 
  print() %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)

MTX_darsnp_3_HF <- gwas_annote_df %>% 
  group_by(MTX_3,HF_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = HF_status, values_from = n) %>% 
  arrange(desc(MTX_3)) %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)

```


```{r HF MTX_DAR 24 enrichment}
gwas_annote_df %>%
  group_by(MTX_24,HF_status) %>%
  tally() %>%
  pivot_wider(., MTX_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(MTX_24)) %>%
  print() %>%
  column_to_rownames("MTX_24") %>%
  fisher.test(.)

MTX_darsnp_24_HF <- gwas_annote_df %>%
  group_by(MTX_24,HF_status) %>%
  tally() %>%
  pivot_wider(., MTX_24, names_from = HF_status, values_from = n) %>%
  arrange(desc(MTX_24)) %>%
  column_to_rownames("MTX_24") %>%
  fisher.test(.)


```


```{r IHD MTX_DAR 3 enrichment}
gwas_annote_df %>% 
  group_by(MTX_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_3))%>% 
  print() %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)

MTX_darsnp_3_IHD <- gwas_annote_df %>% 
  group_by(MTX_3,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_3))%>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)
```


```{r IHD MTX_DAR 24 enrichment}
gwas_annote_df %>% 
  group_by(MTX_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_24)) %>% 
  print() %>% 
  column_to_rownames("MTX_24") %>% 
  fisher.test(.)

MTX_darsnp_24_IHD <- gwas_annote_df %>% 
  group_by(MTX_24,IHD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = IHD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_24)) %>% 
  column_to_rownames("MTX_24") %>% 
  fisher.test(.)
```

```{r CAD MTX_DAR 3enrichment}
gwas_annote_df %>% 
  group_by(MTX_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = CAD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_3)) %>% 
  print() %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)

MTX_darsnp_3_CAD <- gwas_annote_df %>% 
  group_by(MTX_3,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_3, names_from = CAD_status, values_from = n, values_fill = 0) %>% 
  arrange(desc(MTX_3)) %>% 
  column_to_rownames("MTX_3") %>% 
  fisher.test(.)

```

```{r CAD MTX_DAR 24enrichment}
gwas_annote_df %>% 
  group_by(MTX_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(MTX_24)) %>% 
  print() %>% 
  column_to_rownames("MTX_24") %>% 
  chisq.test(.)

MTX_darsnp_24_CAD <- gwas_annote_df %>% 
  group_by(MTX_24,CAD_status) %>% 
  tally() %>% 
  pivot_wider(., MTX_24, names_from = CAD_status, values_from = n) %>% 
  arrange(desc(MTX_24)) %>% 
  column_to_rownames("MTX_24") %>% 
  fisher.test(.)

```

Collecting all data to display:

```{r}
All_24_results <- mget(ls(pattern = "*_darsnp_24*"))
All_3_results <- mget(ls(pattern = "*_darsnp_3*"))
# All_dar_results <- mget(ls(pattern = "*_darsnp_*"))


# convert to data frames with metadata
combined_df_24 <- bind_rows(
  lapply(names(All_24_results), function(name) {
    res <- All_24_results[[name]]
    parts <- strsplit(name, "_")[[1]]
    
    # convert htest to data.frame
    data.frame(
      
      p.value = res$p.value,
      estimate = if (!is.null(res$estimate)) unname(res$estimate) else NA,
      conf.low = if (!is.null(res$conf.int)) res$conf.int[1] else NA,
      conf.high = if (!is.null(res$conf.int)) res$conf.int[2] else NA,
      drug = parts[1],
      time = parts[3],
      population = parts[4],
      stringsAsFactors = FALSE
    )
  })
)

combined_df_3 <- bind_rows(
  lapply(names(All_3_results), function(name) {
    res <- All_3_results[[name]]
    parts <- strsplit(name, "_")[[1]]
    
    # convert htest to data.frame
    data.frame(
      p.value = res$p.value,
      estimate = if (!is.null(res$estimate)) unname(res$estimate) else NA,
      conf.low = if (!is.null(res$conf.int)) res$conf.int[1] else NA,
      conf.high = if (!is.null(res$conf.int)) res$conf.int[2] else NA,
      drug = parts[1],
      time = parts[3],
      population = parts[4],
      stringsAsFactors = FALSE
    )
  })
)
```


```{r}

drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
combined_df_3 %>% 
  mutate(drug=factor(drug, levels = c("DOX","EPI","DNR","MTX")),
         time=factor(time, levels = c("3","24")),
         population=factor(population,levels = c("AF","HF","IHD","CAD"))) %>% 
  mutate(log10_pvalue=-log10(p.value)) %>% 
  ggplot(., aes(x=drug, y=log10_pvalue))+
  geom_col(aes(fill=drug))+
  geom_hline(yintercept= -log10(0.05), linetype = "dashed",color="black")+
  theme_classic()+
  facet_wrap(~time+population,nrow=2)+
  xlab("treatment")+
  ylab("log10 pvalue of fisher exact test")+
  scale_fill_manual(values = drug_pal)


  
  
```
```{r corrected for multiple testing}

combined_df_3 %>% 
  dplyr::filter(population!= "IHD" & population != "CAD") %>%
  mutate(drug=factor(drug, levels = c("DOX","EPI","DNR","MTX")),
         time=factor(time, levels = c("3","24")),
         population=factor(population,levels = c("AF","HF","IHD", "CAD"))) %>%
    group_by(time,drug) %>% 
  mutate(rank_val=rank(p.value, ties.method = "first")) %>%
  mutate(BH_correction= p.adjust(p.value,method= "BH")) %>% 
  mutate(log10_pvalue=-log10(BH_correction)) %>% 
  ggplot(., aes(x=drug, y=log10_pvalue))+
  geom_col(aes(fill=drug))+
  geom_hline(yintercept= -log10(0.05), linetype = "dashed",color="black")+
  theme_classic()+
  facet_wrap(~time+population,nrow=2)+
  xlab("treatment")+
  ylab("log10 pvalue of fisher exact test")+
  scale_fill_manual(values = drug_pal)

  
```

### OR of results

```{r OR_plot, fig.height=7, fig.width=6}
combined_df_3 %>% 
  mutate(group=paste0(drug,"_",time)) %>% 
  # separate_wider_delim(.,cols="group", names = c("trt","time"), delim = "_",cols_remove = FALSE) %>% 
    mutate(time= factor(time, levels =c("3","24")),
         drug=factor(drug, levels= c("DOX", "EPI", "DNR", "MTX"))) %>%
  mutate(population=factor(population, levels= c("AF","HF","IHD","CAD"))) %>% 
  mutate(
    significant = case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""
    )
  ) %>% 
ggplot(., aes(x = drug, y = estimate)) +
   geom_point(aes(color = drug), size=4)+
   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  geom_text(
  aes(y = conf.high + 0.1 * estimate, label = significant),
  hjust = 0,  # aligns text to the left of the y point
  size = 4,
  color = "black"
)+
  labs(
    title = "Odds Ratio of SNP enrichment by type",
    y = "Odds Ratio (95% confidence interval)",
    x = "treatment"
  ) +
  # coord_flip()+
  theme_bw() +
  facet_grid(rows = vars(population), cols = vars(time), scales = "free_y")+
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5)
  )
```


### MCF7 enrichment tests
```{r}
library(regioneR)
AF_gr <- Short_gwas_gr %>% 
  dplyr::filter(gwas == "AF")
HF_gr <- Short_gwas_gr %>% 
  dplyr::filter(gwas == "HF")
IHD_gr <- Short_gwas_gr %>% 
  dplyr::filter(gwas == "IHD")
CAD_gr <- Short_gwas_gr %>% 
  dplyr::filter(gwas == "CAD")


# AF_MCF7_ol_peaks <-   join_overlap_inner(MCF7_DAR_all, Short_gwas_gr) %>%
#   dplyr::filter(mcols(gwas =="AF")) %>% 
#   as.data.frame() %>% 
#   dplyr::filter(gwas =="AF") %>% 
#   distinct(names)
# 
# HF_MCF7_ol_peaks <-   join_overlap_inner(MCF7_DAR_all, Short_gwas_gr) %>%
#   as.data.frame() %>% 
#   dplyr::filter(gwas =="HF") %>% 
#   distinct(names)
# 
# IHD_MCF7_ol_peaks <-   join_overlap_inner(MCF7_DAR_all, Short_gwas_gr) %>%
#   as.data.frame() %>% 
#   dplyr::filter(gwas =="IHD") %>% 
#   distinct(names)

# saveRDS(AF,"data/Final_four_data/re_analysis/MCF7_DAR_AF_permtest.RDS")

IHD <-readRDS("data/Final_four_data/re_analysis/MCF7_DAR_IHD_permtest.RDS")

HF <- readRDS("data/Final_four_data/re_analysis/MCF7_DAR_HF_permtest.RDS")
AF <- readRDS("data/Final_four_data/re_analysis/MCF7_DAR_AF_permtest.RDS")
CAD <- readRDS("data/Final_four_data/re_analysis/MCF7_DAR_CAD_permtest.RDS")
# param <- SnowParam(workers = 8)
# AF<- permTest(A= MCF7_DAR_all,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)
AF
plot(AF)
HF
plot(HF)
IHD
plot(IHD)
CAD
plot(CAD)

```

### PT DOX 24hr check

```{r DOX perm}
# DOX_24_gr <- DOX_24_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
#   GRanges() 
# 
# DOX_3_gr <- DOX_3_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
#   GRanges() 
# param <- SnowParam(workers = 1)

DOX_AF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_AF_24h.RDS")
DOX_HF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_HF_24h.RDS")
DOX_IHD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_IHD_24h.RDS")
DOX_CAD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_CAD_24h.RDS")

DOX_AF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_AF_3h.RDS")
DOX_HF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_HF_3h.RDS")
DOX_IHD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_IHD_3h.RDS")
DOX_CAD_3 <-  readRDS("data/Final_four_data/re_analysis/perm_test_1000/DOX_CAD_3h.RDS")
# DOX_CAD<- permTest(A= DOX_24_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)

# DOX_AF<- permTest(A= DOX_24_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# DOX_HF<- permTest(A= DOX_24_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)

# DOX_IHD<- permTest(A= DOX_24_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)
DOX_AF
plot(DOX_AF)
DOX_HF
plot(DOX_HF)
DOX_IHD
plot(DOX_IHD)
DOX_CAD
plot(DOX_CAD)

# DOX_CAD_3<- permTest(A= DOX_3_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)

# DOX_AF_3<- permTest(A= DOX_3_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)

# DOX_HF_3<- permTest(A= DOX_3_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)

# DOX_IHD_3<- permTest(A= DOX_3_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         # universe = union_accessible_regions,
#                           verbose = TRUE,
#                           BPPARAM = param)
DOX_AF_3
plot(DOX_AF_3)
DOX_HF_3
plot(DOX_HF_3)
DOX_IHD_3
plot(DOX_IHD_3)
DOX_CAD_3
plot(DOX_CAD_3)

# saveRDS(DOX_AF,"data/Final_four_data/re_analysis/perm_test_100/DOX_AF_24h.RDS")
# saveRDS(DOX_HF,"data/Final_four_data/re_analysis/perm_test_100/DOX_HF_24h.RDS")
# saveRDS(DOX_IHD,"data/Final_four_data/re_analysis/perm_test_100/DOX_IHD_24h.RDS")
# saveRDS(DOX_CAD,"data/Final_four_data/re_analysis/perm_test_100/DOX_CAD_24h.RDS")

# saveRDS(DOX_AF_3,"data/Final_four_data/re_analysis/perm_test_100/DOX_AF_3h.RDS")
# saveRDS(DOX_HF_3,"data/Final_four_data/re_analysis/perm_test_100/DOX_HF_3h.RDS")
# saveRDS(DOX_IHD_3,"data/Final_four_data/re_analysis/perm_test_100/DOX_IHD_3h.RDS")
# saveRDS(DOX_CAD_3,"data/Final_four_data/re_analysis/perm_test_100/DOX_CAD_3h.RDS")

# saveRDS(DOX_AF,"data/Final_four_data/re_analysis/perm_test_1000/DOX_AF_24h.RDS")
# saveRDS(DOX_HF,"data/Final_four_data/re_analysis/perm_test_1000/DOX_HF_24h.RDS")
# saveRDS(DOX_IHD,"data/Final_four_data/re_analysis/perm_test_1000/DOX_IHD_24h.RDS")
# saveRDS(DOX_CAD,"data/Final_four_data/re_analysis/perm_test_1000/DOX_CAD_24h.RDS")

# saveRDS(DOX_AF_3,"data/Final_four_data/re_analysis/perm_test_1000/DOX_AF_3h.RDS")
# saveRDS(DOX_HF_3,"data/Final_four_data/re_analysis/perm_test_1000/DOX_HF_3h.RDS")
# saveRDS(DOX_IHD_3,"data/Final_four_data/re_analysis/perm_test_1000/DOX_IHD_3h.RDS")
# saveRDS(DOX_CAD_3,"data/Final_four_data/re_analysis/perm_test_1000/DOX_CAD_3h.RDS")
```

### PT EPI 24hr check
```{r EPI perm}
EPI_24_gr <- EPI_24_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

EPI_3_gr <- EPI_3_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

EPI_AF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_AF_24h.RDS")
EPI_HF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_HF_24h.RDS")
EPI_IHD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_IHD_24h.RDS")
EPI_CAD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_CAD_24h.RDS")

EPI_AF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_AF_3h.RDS")
EPI_HF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_HF_3h.RDS")
EPI_IHD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_IHD_3h.RDS")
EPI_CAD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/EPI_CAD_3h.RDS")



# EPI_AF_3<- permTest(A= EPI_3_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         #
#                           verbose = TRUE,
#                           BPPARAM = param)
# EPI_HF_3<- permTest(A= EPI_3_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# EPI_IHD_3<- permTest(A= EPI_3_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# EPI_CAD_3<- permTest(A= EPI_3_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)






EPI_AF_3
plot(EPI_AF_3)
EPI_HF_3
plot(EPI_HF_3)
EPI_IHD_3
plot(EPI_IHD_3)
EPI_CAD_3
plot(EPI_CAD_3)

# EPI_AF<- permTest(A= EPI_24_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# EPI_HF<- permTest(A= EPI_24_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# EPI_IHD<- permTest(A= EPI_24_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# EPI_CAD <- permTest(A= EPI_24_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)


EPI_AF
plot(EPI_AF)
EPI_HF
plot(EPI_HF)
EPI_IHD
plot(EPI_IHD)
EPI_CAD
plot(EPI_CAD)

# saveRDS(EPI_AF,"data/Final_four_data/re_analysis/perm_test_100/EPI_AF_24h.RDS")
# saveRDS(EPI_HF,"data/Final_four_data/re_analysis/perm_test_100/EPI_HF_24h.RDS")
# saveRDS(EPI_IHD,"data/Final_four_data/re_analysis/perm_test_100/EPI_IHD_24h.RDS")
# saveRDS(EPI_CAD,"data/Final_four_data/re_analysis/perm_test_100/EPI_CAD_24h.RDS")
# 
# saveRDS(EPI_AF_3,"data/Final_four_data/re_analysis/perm_test_100/EPI_AF_3h.RDS")
# saveRDS(EPI_HF_3,"data/Final_four_data/re_analysis/perm_test_100/EPI_HF_3h.RDS")
# saveRDS(EPI_IHD_3,"data/Final_four_data/re_analysis/perm_test_100/EPI_IHD_3h.RDS")
# saveRDS(EPI_CAD_3,"data/Final_four_data/re_analysis/perm_test_100/EPI_CAD_3h.RDS")

# saveRDS(EPI_AF,"data/Final_four_data/re_analysis/perm_test_1000/EPI_AF_24h.RDS")
# saveRDS(EPI_HF,"data/Final_four_data/re_analysis/perm_test_1000/EPI_HF_24h.RDS")
# saveRDS(EPI_IHD,"data/Final_four_data/re_analysis/perm_test_1000/EPI_IHD_24h.RDS")
# saveRDS(EPI_CAD,"data/Final_four_data/re_analysis/perm_test_1000/EPI_CAD_24h.RDS")
# 
# saveRDS(EPI_AF_3,"data/Final_four_data/re_analysis/perm_test_1000/EPI_AF_3h.RDS")
# saveRDS(EPI_HF_3,"data/Final_four_data/re_analysis/perm_test_1000/EPI_HF_3h.RDS")
# saveRDS(EPI_IHD_3,"data/Final_four_data/re_analysis/perm_test_1000/EPI_IHD_3h.RDS")
# saveRDS(EPI_CAD_3,"data/Final_four_data/re_analysis/perm_test_1000/EPI_CAD_3h.RDS")


```
### PT DNR 24hr check
```{r DNR perm}
DNR_24_gr <- DNR_24_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

DNR_3_gr <- DNR_3_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

DNR_AF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_AF_24h.RDS")
DNR_HF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_HF_24h.RDS")
DNR_IHD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_IHD_24h.RDS")
DNR_CAD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_CAD_24h.RDS")

DNR_AF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_AF_3h.RDS")
DNR_HF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_HF_3h.RDS")
DNR_IHD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_IHD_3h.RDS")
DNR_CAD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/DNR_CAD_3h.RDS")

# DNR_AF_3<- permTest(A= DNR_3_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         #
#                           verbose = TRUE,
#                           BPPARAM = param)
# DNR_HF_3<- permTest(A= DNR_3_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# DNR_IHD_3<- permTest(A= DNR_3_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# DNR_CAD_3<- permTest(A= DNR_3_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)






DNR_AF_3
plot(DNR_AF_3)
DNR_HF_3
plot(DNR_HF_3)
DNR_IHD_3
plot(DNR_IHD_3)
DNR_CAD_3
plot(DNR_CAD_3)

# DNR_AF<- permTest(A= DNR_24_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# DNR_HF<- permTest(A= DNR_24_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# DNR_IHD<- permTest(A= DNR_24_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# DNR_CAD <- permTest(A= DNR_24_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 

DNR_AF
plot(DNR_AF)
DNR_HF
plot(DNR_HF)
DNR_IHD
plot(DNR_IHD)
DNR_CAD
plot(DNR_CAD)

# saveRDS(DNR_AF,"data/Final_four_data/re_analysis/perm_test_100/DNR_AF_24h.RDS")
# saveRDS(DNR_HF,"data/Final_four_data/re_analysis/perm_test_100/DNR_HF_24h.RDS")
# saveRDS(DNR_IHD,"data/Final_four_data/re_analysis/perm_test_100/DNR_IHD_24h.RDS")
# saveRDS(DNR_CAD,"data/Final_four_data/re_analysis/perm_test_100/DNR_CAD_24h.RDS")
# 
# saveRDS(DNR_AF_3,"data/Final_four_data/re_analysis/perm_test_100/DNR_AF_3h.RDS")
# saveRDS(DNR_HF_3,"data/Final_four_data/re_analysis/perm_test_100/DNR_HF_3h.RDS")
# saveRDS(DNR_IHD_3,"data/Final_four_data/re_analysis/perm_test_100/DNR_IHD_3h.RDS")
# saveRDS(DNR_CAD_3,"data/Final_four_data/re_analysis/perm_test_100/DNR_CAD_3h.RDS")

# saveRDS(DNR_AF,"data/Final_four_data/re_analysis/perm_test_1000/DNR_AF_24h.RDS")
# saveRDS(DNR_HF,"data/Final_four_data/re_analysis/perm_test_1000/DNR_HF_24h.RDS")
# saveRDS(DNR_IHD,"data/Final_four_data/re_analysis/perm_test_1000/DNR_IHD_24h.RDS")
# saveRDS(DNR_CAD,"data/Final_four_data/re_analysis/perm_test_1000/DNR_CAD_24h.RDS")
# 
# saveRDS(DNR_AF_3,"data/Final_four_data/re_analysis/perm_test_1000/DNR_AF_3h.RDS")
# saveRDS(DNR_HF_3,"data/Final_four_data/re_analysis/perm_test_1000/DNR_HF_3h.RDS")
# saveRDS(DNR_IHD_3,"data/Final_four_data/re_analysis/perm_test_1000/DNR_IHD_3h.RDS")
# saveRDS(DNR_CAD_3,"data/Final_four_data/re_analysis/perm_test_1000/DNR_CAD_3h.RDS")


```
### PT MTX 24hr check
```{r MTX perm}
MTX_24_gr <- MTX_24_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

MTX_3_gr <- MTX_3_sig %>% separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges() 

MTX_AF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_AF_24h.RDS")
MTX_HF <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_HF_24h.RDS")
MTX_IHD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_IHD_24h.RDS")
MTX_CAD <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_CAD_24h.RDS")

MTX_AF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_AF_3h.RDS")
MTX_HF_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_HF_3h.RDS")
MTX_IHD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_IHD_3h.RDS")
MTX_CAD_3 <- readRDS("data/Final_four_data/re_analysis/perm_test_1000/MTX_CAD_3h.RDS")

# MTX_AF_3<- permTest(A= MTX_3_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                         #
#                           verbose = TRUE,
#                           BPPARAM = param)
# MTX_HF_3<- permTest(A= MTX_3_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# MTX_IHD_3<- permTest(A= MTX_3_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# MTX_CAD_3<- permTest(A= MTX_3_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# 
#                           verbose = TRUE,
#                           BPPARAM = param)






MTX_AF_3
plot(MTX_AF_3)
MTX_HF_3
plot(MTX_HF_3)
MTX_IHD_3
plot(MTX_IHD_3)
MTX_CAD_3
plot(MTX_CAD_3)

# MTX_AF<- permTest(A= MTX_24_gr,
#                           B= AF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# MTX_HF<- permTest(A= MTX_24_gr,
#                           B= HF_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# 
# MTX_IHD<- permTest(A= MTX_24_gr,
#                           B= IHD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)
# 
# MTX_CAD <- permTest(A= MTX_24_gr,
#                           B= CAD_gr,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
#                           verbose = TRUE,
#                           BPPARAM = param)


MTX_AF
plot(MTX_AF)
MTX_HF
plot(MTX_HF)
MTX_IHD
plot(MTX_IHD)
MTX_CAD
plot(MTX_CAD)

# saveRDS(MTX_AF,"data/Final_four_data/re_analysis/perm_test_100/MTX_AF_24h.RDS")
# saveRDS(MTX_HF,"data/Final_four_data/re_analysis/perm_test_100/MTX_HF_24h.RDS")
# saveRDS(MTX_IHD,"data/Final_four_data/re_analysis/perm_test_100/MTX_IHD_24h.RDS")
# saveRDS(MTX_CAD,"data/Final_four_data/re_analysis/perm_test_100/MTX_CAD_24h.RDS")
# 
# saveRDS(MTX_AF_3,"data/Final_four_data/re_analysis/perm_test_100/MTX_AF_3h.RDS")
# saveRDS(MTX_HF_3,"data/Final_four_data/re_analysis/perm_test_100/MTX_HF_3h.RDS")
# saveRDS(MTX_IHD_3,"data/Final_four_data/re_analysis/perm_test_100/MTX_IHD_3h.RDS")
# saveRDS(MTX_CAD_3,"data/Final_four_data/re_analysis/perm_test_100/MTX_CAD_3h.RDS")

# saveRDS(MTX_AF,"data/Final_four_data/re_analysis/perm_test_1000/MTX_AF_24h.RDS")
# saveRDS(MTX_HF,"data/Final_four_data/re_analysis/perm_test_1000/MTX_HF_24h.RDS")
# saveRDS(MTX_IHD,"data/Final_four_data/re_analysis/perm_test_1000/MTX_IHD_24h.RDS")
# saveRDS(MTX_CAD,"data/Final_four_data/re_analysis/perm_test_1000/MTX_CAD_24h.RDS")
# 
# saveRDS(MTX_AF_3,"data/Final_four_data/re_analysis/perm_test_1000/MTX_AF_3h.RDS")
# saveRDS(MTX_HF_3,"data/Final_four_data/re_analysis/perm_test_1000/MTX_HF_3h.RDS")
# saveRDS(MTX_IHD_3,"data/Final_four_data/re_analysis/perm_test_1000/MTX_IHD_3h.RDS")
# saveRDS(MTX_CAD_3,"data/Final_four_data/re_analysis/perm_test_1000/MTX_CAD_3h.RDS")


```


### Creating heatmaps

```{r}

all_results_LFC <- all_results %>%  dplyr::select(source,genes,logFC) %>%
    pivot_wider(id_cols=genes, values_from = logFC, names_from = source) %>% 
  dplyr::rename("Peakid"=genes)


ATAC_all_adj.pvals <- readRDS("data/Final_four_data/re_analysis/ATAC_all_adj_pvals.RDS")

AF_heatmap_df <- SNP_overlaps %>% 
  as.data.frame() %>% 
  dplyr::filter(gwas=="AF") %>% 
  group_by(Peakid) %>%
  summarise(SNPS=paste(unique(SNPS),collapse = ";"))

HF_heatmap_df <- SNP_overlaps %>% 
  as.data.frame() %>% 
  dplyr::filter(gwas=="HF") %>% 
  group_by(Peakid) %>%
  summarise(SNPS=paste(unique(SNPS),collapse = ";"))
```

```{r AF heatmap, fig.height=13, fig.width=8}

AF_mat <- AF_heatmap_df %>% 
  left_join(., all_results_LFC, by=c("Peakid"="Peakid")) %>% 
  tidyr::unite(., name,Peakid,SNPS) %>% 
  column_to_rownames("name") %>% 
  as.matrix()

AF_sig_mat <- AF_heatmap_df %>% 
  left_join(., ATAC_all_adj.pvals, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,SNPS) %>% 
  column_to_rownames("name") %>% 
  as.matrix()


simply_AF_lfc <- ComplexHeatmap::Heatmap(AF_mat,
                                         
                        show_row_names = TRUE,
                       row_names_max_width=
ComplexHeatmap::max_text_width(rownames(AF_mat),                                                        gp=gpar(fontsize=14)),
                        heatmap_legend_param = list(direction = "horizontal"),
column_title = "AF_SNPS",
                       
                        show_column_names = TRUE,
                        cluster_rows = FALSE,
                        cluster_columns = FALSE,
                        cell_fun = function(j, i, x, y, width, height, fill) {
                          if (!is.na(AF_sig_mat[i, j]) && AF_sig_mat[i, j] <0.05) {
                              grid.text("*", x, y, gp = gpar(fontsize = 20))  # Add star if significant
                            } })

ComplexHeatmap::draw(simply_AF_lfc, 
     merge_legend = TRUE, 
     heatmap_legend_side = "left", 
    annotation_legend_side = "left")
```

```{r HF heatmap, fig.height=10, fig.width=8}

HF_mat <- HF_heatmap_df %>% 
  left_join(., all_results_LFC, by=c("Peakid"="Peakid")) %>% 
  tidyr::unite(., name,Peakid,SNPS) %>% 
  column_to_rownames("name") %>% 
  as.matrix()

HF_sig_mat <- HF_heatmap_df %>% 
  left_join(., ATAC_all_adj.pvals, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,SNPS) %>% 
  column_to_rownames("name") %>% 
  as.matrix()


simply_HF_lfc <- ComplexHeatmap::Heatmap(HF_mat,
                                         
                        show_row_names = TRUE,
                       row_names_max_width=
ComplexHeatmap::max_text_width(rownames(HF_mat),                                                        gp=gpar(fontsize=14)),
                        heatmap_legend_param = list(direction = "horizontal"),
column_title = "HF_SNPS",
                       
                        show_column_names = TRUE,
                        cluster_rows = FALSE,
                        cluster_columns = FALSE,
                        cell_fun = function(j, i, x, y, width, height, fill) {
                          if (!is.na(HF_sig_mat[i, j]) && HF_sig_mat[i, j] <0.05) {
                              grid.text("*", x, y, gp = gpar(fontsize = 20))  # Add star if significant
                            } })

ComplexHeatmap::draw(simply_HF_lfc, 
     merge_legend = TRUE, 
     heatmap_legend_side = "left", 
    annotation_legend_side = "left")
```
