---
title: "CorMotif_data"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
# library(ggsignif)
# library(cowplot)
# library(ggpubr)
# library(scales)
# library(sjmisc)
library(kableExtra)
# library(broom)
# library(biomaRt)
library(RColorBrewer)
# library(gprofiler2)
# library(qvalue)
# library(ChIPseeker)
# library("TxDb.Hsapiens.UCSC.hg38.knownGene")
# library("org.Hs.eg.db")
# library(ATACseqQC)
# library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)

library(scales)
# library(ggVennDiagram)
library(Cormotif)
library(BiocParallel)
library(ggpubr)
```

```{r echo=TRUE, file='code/corMotifcustom.R'}

```
## Data import and set up

The first time I ran this data, I used all of the high confidence peaks.   
```{r setting up data}
high_conf_peak_counts <- read.csv("data/high_conf_peak_counts.csv", row.names = 1)


high_conf_peak_counts <- high_conf_peak_counts %>% 
  column_to_rownames("Geneid") %>% 
  dplyr::select(Ind1_75DA24h:Ind6_71V3h)
groupmat_names <- data.frame(timeset = colnames(high_conf_peak_counts))

df_names <-groupmat_names %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>%
  mutate(timeset=gsub("87","2_",timeset)) %>%
  mutate(timeset=gsub("77","3_",timeset)) %>%
  mutate(timeset=gsub("79","4_",timeset)) %>%
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>%
  mutate(timeset = gsub("24h","_24h",timeset),
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) 
  
 
group <- c( rep(c(1,2,3,4,5,6,7,8,9,10,11,12),6))
group <- factor(group, levels =c("1","2","3","4","5","6","7","8","9","10","11","12"))                        
indv <- df_names$indv
# indv <- factor(indv, levels = c(1,2,3,4,5,6))
time <- df_names$time
# time <- factor(time, levels =c("3h","24"))
trt <- df_names$trt
label <- paste0(indv,"_",trt,"_",time)
group_fac <- group
groupid <- as.numeric(group_fac)

compid <- data.frame(c1= c(2,4,6,8,10,1,3,5,7,9), c2 = c( 12,12,12,12,12,11,11,11,11,11))

y_TMM_cpm <- cpm(high_conf_peak_counts, log = TRUE)
 

rownames(y_TMM_cpm) <- rownames(high_conf_peak_counts)
colnames(y_TMM_cpm) <- label
# y_TMM_cpm
set.seed(31415)
# cormotif_initial <- cormotiffit(exprs = y_TMM_cpm,
#                                 groupid = groupid,
#                                 compid = compid,
#                                 K=1:6, max.iter = 500, runtype="logCPM")
# saveRDS(cormotif_initial,"data/cormotif_full_6_run.RDS")

cormotif_initial <- readRDS("data/cormotif_full_6_run.RDS")
gene_prob_tran <- cormotif_initial$bestmotif$p.post

rownames(gene_prob_tran) <- rownames(y_TMM_cpm)
motif_prob <- cormotif_initial$bestmotif$clustlike
rownames(motif_prob) <- rownames(y_TMM_cpm)
# write.csv(motif_prob,"data/cormotif_probability_all_6_list.csv")

Cormotif::plotIC(cormotif_initial)
Cormotif::plotMotif(cormotif_initial)

myColors <-  rev(c("#FFFFFF", "#E6E6E6" ,"#CCCCCC", "#B3B3B3", "#999999", "#808080", "#666666","#4C4C4C", "#333333", "#191919","#000000"))
plot.new()
legend('bottomleft',fill=myColors, legend =rev(c("0", "0.1", "0.2", "0.3", "0.4",  "0.5", "0.6", "0.7", "0.8","0.9", "1")), box.col="white",title = "Probability\nlegend", horiz=FALSE,title.cex=.8)


```

total number of peaks = `r length(high_conf_peak_counts[[1]])`.

Study breakdown: 1 = DNR_3, 2 = DOX_3, 3 = EPI_3, 4 = MTX_3, 5 = TRZ_3  
                6 = DNR_24, 7 = DOX_24, 8 = EPI_24, 9 = MTX_24, 10 = TRZ_24

I realized  I may need to run the cormotif with JUST the highly expressed set of highconf (hc) peaks and
therefore reran cormotif on the set with log2cpm rowmeans > 0.

```{r hc high expressed motif}

high_conf_peak_counts <- read.csv("data/high_conf_peak_counts.csv", row.names = 1)
my_hc_counts <- high_conf_peak_counts %>% 
  dplyr::select(Geneid,Ind1_75DA24h:Ind6_71V3h) %>% 
  column_to_rownames("Geneid")

lcpm <- cpm(my_hc_counts, log=TRUE)  ### for determining the basic cutoffs

row_means <- rowMeans(lcpm)
my_hc_filtered_counts <- my_hc_counts[row_means > 0,]



groupmat_names_he <- data.frame(timeset = colnames(my_hc_filtered_counts))

df_names_he <-groupmat_names_he %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>%
  mutate(timeset=gsub("87","2_",timeset)) %>%
  mutate(timeset=gsub("77","3_",timeset)) %>%
  mutate(timeset=gsub("79","4_",timeset)) %>%
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>%
  mutate(timeset = gsub("24h","_24h",timeset),
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) 
  
 
label <- paste0(indv,"_",trt,"_",time)
group_fac <- group
groupid <- as.numeric(group_fac)

compid <- data.frame(c1= c(2,4,6,8,10,1,3,5,7,9), c2 = c( 12,12,12,12,12,11,11,11,11,11))

y_TMM_cpm_he <- cpm(my_hc_filtered_counts, log = TRUE)
 

rownames(y_TMM_cpm_he) <- rownames(my_hc_filtered_counts)
colnames(y_TMM_cpm_he) <- label
set.seed(31415)
# cormotif_initial_he <- cormotiffit(exprs = y_TMM_cpm_he,
                                # groupid = groupid,
                                # compid = compid,
                                # K=1:6, max.iter = 500, runtype="logCPM")
# saveRDS(cormotif_initial_he,"data/cormotif_full_6_run_he.RDS")

cormotif_initial_he<- readRDS("data/cormotif_full_6_run_he.RDS")
gene_prob_tran_he <- cormotif_initial_he$bestmotif$p.post

rownames(gene_prob_tran_he) <- rownames(y_TMM_cpm_he)
motif_prob_he <- cormotif_initial_he$bestmotif$clustlike
rownames(motif_prob_he) <- rownames(y_TMM_cpm_he)
write.csv(motif_prob_he,"data/cormotif_probability_all_6_list_he.csv")

Cormotif::plotIC(cormotif_initial_he)
Cormotif::plotMotif(cormotif_initial_he)

myColors <-  rev(c("#FFFFFF", "#E6E6E6" ,"#CCCCCC", "#B3B3B3", "#999999", "#808080", "#666666","#4C4C4C", "#333333", "#191919","#000000"))
plot.new()
legend('bottomleft',fill=myColors, legend =rev(c("0", "0.1", "0.2", "0.3", "0.4",  "0.5", "0.6", "0.7", "0.8","0.9", "1")), box.col="white",title = "Probability\nlegend", horiz=FALSE,title.cex=.8)









```
This filtering left me with `r length(my_hc_filtered_counts[[1]])` peaks.





```{r pulling out the groups}

motif_prob <- read.csv("data/cormotif_probability_all_6_list.csv")
motif_prob <- motif_prob %>% 
  column_to_rownames('X')
clust1 <- motif_prob %>%
  as.data.frame() %>%
  filter(V1>0.5) %>% 
  rownames
clust2 <- motif_prob %>%
  as.data.frame() %>%
  filter(V2>0.5) %>% 
  rownames
clust3 <- motif_prob %>%
  as.data.frame() %>%
  filter(V3>0.5) %>% 
  rownames
clust4 <- motif_prob %>%
  as.data.frame() %>%
  filter(V4>0.5) %>% 
  rownames


```



