---
title: "DOX_DAR_heatmaps"
author: "Renee Matthews"
date: "2025-06-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)
library(readxl)
library(ComplexHeatmap)

```


Loading counts matrix and making filtered matrix
```{r countmatrix loading}
raw_counts <- read_delim("data/Final_four_data/re_analysis/Raw_unfiltered_counts.tsv",delim="\t") %>% 
  column_to_rownames("Peakid") %>% 
  as.matrix()

lcpm <- cpm(raw_counts, log= TRUE)
  ### for determining the basic cutoffs
filt_raw_counts <- raw_counts[rowMeans(lcpm)> 0,]

filt_raw_counts_noY <- filt_raw_counts[!grepl("chrY",rownames(filt_raw_counts)),]

```

Subsetting count matrix and adding log2cpm
```{r creating dataframes with all regions}
# annotation_mat <- data.frame(timeset=colnames(filt_raw_counts_noY)) %>%
#   mutate(sample = timeset) %>% 
#   separate(timeset, into = c("indv","trt","time"), sep= "_") %>% 
#   mutate(time = factor(time, levels = c("3h", "24h"))) %>% 
#   mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>% 
#   mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
#   mutate(trt_time=paste0(trt,"_",time))

DOX_VEH_3hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select(contains("VEH")& ends_with("3h")| contains("DOX")& ends_with("3h")) %>% 
  # dplyr::select(where(~ grepl("VEH|DOX", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


DOX_VEH_24hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select((contains("VEH")& ends_with("24h"))| (contains("DOX")& ends_with("24h"))) %>% 
  # dplyr::select(where(~ grepl("VEH|DOX", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)

EPI_VEH_3hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select(contains("VEH")& ends_with("3h")| contains("EPI")& ends_with("3h")) %>% 
  # dplyr::select(where(~ grepl("VEH|EPI", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


EPI_VEH_24hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select((contains("VEH")& ends_with("24h"))| (contains("EPI")& ends_with("24h"))) %>% 
  # dplyr::select(where(~ grepl("VEH|EPI", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)

DNR_VEH_3hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select(contains("VEH")& ends_with("3h")| contains("DNR")& ends_with("3h")) %>% 
  # dplyr::select(where(~ grepl("VEH|DNR", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


DNR_VEH_24hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select((contains("VEH")& ends_with("24h"))| (contains("DNR")& ends_with("24h"))) %>% 
  # dplyr::select(where(~ grepl("VEH|DNR", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)

MTX_VEH_3hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select(contains("VEH")& ends_with("3h")| contains("MTX")& ends_with("3h")) %>% 
  # dplyr::select(where(~ grepl("VEH|MTX", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


MTX_VEH_24hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select((contains("VEH")& ends_with("24h"))| (contains("MTX")& ends_with("24h"))) %>% 
  # dplyr::select(where(~ grepl("VEH|MTX", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)

TRZ_VEH_3hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select(contains("VEH")& ends_with("3h")| contains("TRZ")& ends_with("3h")) %>% 
  # dplyr::select(where(~ grepl("VEH|TRZ", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


TRZ_VEH_24hr <- filt_raw_counts_noY %>% 
  as.data.frame() %>% 
  dplyr::select((contains("VEH")& ends_with("24h"))| (contains("TRZ")& ends_with("24h"))) %>% 
  # dplyr::select(where(~ grepl("VEH|TRZ", .col) & grepl("3h$", .col))) %>% ### this also works
  cpm(., log=TRUE)


```

loading DOX DARs for 3 hours and 24 hours
```{r}
toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

DOX_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DOX_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

EPI_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="EPI_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

EPI_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="EPI_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DNR_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DNR_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

DNR_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DNR_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

MTX_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="MTX_3") %>% 
   dplyr::filter(adj.P.Val<0.05) 

MTX_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="MTX_24") %>% 
   dplyr::filter(adj.P.Val<0.05) 

TRZ_3_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="TRZ_3") 

TRZ_24_sig <-all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="TRZ_24") 

```

### DOX 3 hour filtering matrix  


```{r DOX 3hr heatmap, fig.height=8, fig.width=5}
DOX_VEH_3hr_mat <-  DOX_VEH_3hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%DOX_3_sig$Peakid) %>% 
  as.matrix()

DOX3_annot_mat <- tibble(timeset=colnames(DOX_VEH_3hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(DOX3_annot_mat$indv))
col_ha_3hr <- HeatmapAnnotation(df=DOX3_annot_mat,
                                col=list(
                                  trt = c(DOX="#8B006D",VEH="#41B333"),
                                  indv = indv_color)) 
wss <- sapply(1:15, function(k) {
  kmeans(DOX_VEH_3hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K") 

                              

Heatmap(DOX_VEH_3hr_mat, 
        top_annotation = col_ha_3hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "3 Hour Log2cpm of 3 hr DOX DARs")
  
```


### DOX 24 hour filtering matrix

```{r DOX 24hr heatmap, fig.height=8, fig.width=5}
DOX_VEH_24hr_mat <-  DOX_VEH_24hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%DOX_24_sig$Peakid) %>% 
  as.matrix()

DOX24_annot_mat <- tibble(timeset=colnames(DOX_VEH_24hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_24color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(DOX24_annot_mat$indv))
col_ha_24hr <- HeatmapAnnotation(df=DOX24_annot_mat,
                                col=list(
                                  trt = c(DOX="#8B006D",VEH="#41B333"),
                                  indv = indv_24color)) 
 set.seed(123)
wss <- sapply(1:15, function(k) {
  kmeans(DOX_VEH_24hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K") 



Heatmap(DOX_VEH_24hr_mat, 
        top_annotation = col_ha_24hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 3,
        column_title = "24 Hour Log2cpm of 24 hr DARs")
  
```

### EPI 3 hour filtering matrix  


```{r EPI 3hr heatmap, fig.height=8, fig.width=5}


EPI_VEH_3hr_mat <-  EPI_VEH_3hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%EPI_3_sig$Peakid) %>% 
  as.matrix()

EPI3_annot_mat <- tibble(timeset=colnames(EPI_VEH_3hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(EPI3_annot_mat$indv))
col_ha_3hr <- HeatmapAnnotation(df=EPI3_annot_mat,
                                col=list(
                                  trt = c(EPI="#DF707E",VEH="#41B333"),
                                  indv = indv_color)) 
wss <- sapply(1:15, function(k) {
  kmeans(EPI_VEH_3hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K") 

                              

Heatmap(EPI_VEH_3hr_mat, 
        top_annotation = col_ha_3hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "3 Hour Log2cpm of 3 hr DARs")
  
```


### EPI 24 hour filtering matrix

```{r EPI 24hr heatmap, fig.height=8, fig.width=5}
EPI_VEH_24hr_mat <-  EPI_VEH_24hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%EPI_24_sig$Peakid) %>% 
  as.matrix()

EPI24_annot_mat <- tibble(timeset=colnames(EPI_VEH_24hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_24color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(EPI24_annot_mat$indv))
col_ha_24hr <- HeatmapAnnotation(df=EPI24_annot_mat,
                                col=list(
                                  trt = c(EPI="#DF707E",VEH="#41B333"),
                                  indv = indv_24color)) 
 wss <- sapply(1:15, function(k) {
  kmeans(EPI_VEH_24hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                              

Heatmap(EPI_VEH_24hr_mat, 
        top_annotation = col_ha_24hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "24 Hour Log2cpm of 24 hr DARs")
  
```

### DNR 3 hour filtering matrix  


```{r DNR 3hr heatmap, fig.height=8, fig.width=5}
DNR_VEH_3hr_mat <-  DNR_VEH_3hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%DNR_3_sig$Peakid) %>% 
  as.matrix()

DNR3_annot_mat <- tibble(timeset=colnames(DNR_VEH_3hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(DNR3_annot_mat$indv))
col_ha_3hr <- HeatmapAnnotation(df=DNR3_annot_mat,
                                col=list(
                                  trt = c(DNR="#F1B72B",VEH="#41B333"),
                                  indv = indv_color)) 
wss <- sapply(1:15, function(k) {
  kmeans(DNR_VEH_3hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                               

Heatmap(DNR_VEH_3hr_mat, 
        top_annotation = col_ha_3hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "3 Hour Log2cpm of 3 hr DARs")
  
```


### DNR 24 hour filtering matrix

```{r DNR 24hr heatmap, fig.height=8, fig.width=5}
DNR_VEH_24hr_mat <-  DNR_VEH_24hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%DNR_24_sig$Peakid) %>% 
  as.matrix()

DNR24_annot_mat <- tibble(timeset=colnames(DNR_VEH_24hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_24color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(DNR24_annot_mat$indv))
col_ha_24hr <- HeatmapAnnotation(df=DNR24_annot_mat,
                                col=list(
                                  trt = c(DNR="#F1B72B",VEH="#41B333"),
                                  indv = indv_24color)) 
wss <- sapply(1:15, function(k) {
  kmeans(DNR_VEH_24hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                               

Heatmap(DNR_VEH_24hr_mat, 
        top_annotation = col_ha_24hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "24 Hour Log2cpm of 24 hr DARs")
  
```


### MTX 3 hour filtering matrix  


```{r MTX 3hr heatmap, fig.height=8, fig.width=5}
MTX_VEH_3hr_mat <-  MTX_VEH_3hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%MTX_3_sig$Peakid) %>% 
  as.matrix()

MTX3_annot_mat <- tibble(timeset=colnames(MTX_VEH_3hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(MTX3_annot_mat$indv))
col_ha_3hr <- HeatmapAnnotation(df=MTX3_annot_mat,
                                col=list(
                                  trt = c(MTX="#3386DD",VEH="#41B333"),
                                  indv = indv_color)) 
wss <- sapply(1:15, function(k) {
  kmeans(MTX_VEH_3hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                               

Heatmap(MTX_VEH_3hr_mat, 
        top_annotation = col_ha_3hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 7,
        column_title = "3 Hour Log2cpm of 3 hr DARs")
  
```


### MTX 24 hour filtering matrix

```{r MTX 24hr heatmap, fig.height=8, fig.width=5}
MTX_VEH_24hr_mat <-  MTX_VEH_24hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%MTX_24_sig$Peakid) %>% 
  as.matrix()

MTX24_annot_mat <- tibble(timeset=colnames(MTX_VEH_24hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_24color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(MTX24_annot_mat$indv))
col_ha_24hr <- HeatmapAnnotation(df=MTX24_annot_mat,
                                col=list(
                                  trt = c(MTX="#3386DD",VEH="#41B333"),
                                  indv = indv_24color)) 
wss <- sapply(1:15, function(k) {
  kmeans(MTX_VEH_24hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                               

Heatmap(MTX_VEH_24hr_mat, 
        top_annotation = col_ha_24hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "24 Hour Log2cpm of 24 hr DARs")
  
```

### TRZ 3 hour filtering matrix  


```{r TRZ 3hr heatmap, fig.height=8, fig.width=5}
TRZ_VEH_3hr_mat <-  TRZ_VEH_3hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%TRZ_3_sig$Peakid) %>% 
  as.matrix()

TRZ3_annot_mat <- tibble(timeset=colnames(TRZ_VEH_3hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(TRZ3_annot_mat$indv))
col_ha_3hr <- HeatmapAnnotation(df=TRZ3_annot_mat,
                                col=list(
                                  trt = c(TRZ="#707031",VEH="#41B333"),
                                  indv = indv_color)) 
wss <- sapply(1:15, function(k) {
  kmeans(TRZ_VEH_3hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")
```


```{r TRZ 3hr heatmap map, fig.height=8, fig.width=5}
Heatmap(TRZ_VEH_3hr_mat, 
        top_annotation = col_ha_3hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 4,
        column_title = "3 Hour Log2cpm of 3 hr all regions")
  
```


### TRZ 24 hour filtering matrix

```{r TRZ 24hr heatmap, fig.height=8, fig.width=5}
TRZ_VEH_24hr_mat <-  TRZ_VEH_24hr %>% 
  as.data.frame() %>% 
  dplyr::filter(rownames(.) %in%TRZ_24_sig$Peakid) %>% 
  as.matrix()

TRZ24_annot_mat <- tibble(timeset=colnames(TRZ_VEH_24hr)) %>%
  mutate(sample = timeset) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>%
  # mutate(time = factor(time, levels = c("3h", "24h"))) %>%
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>%
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  column_to_rownames("sample")
  # mutate(trt_time=paste0(trt,"_",time))
# drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
indv_24color <- setNames(brewer.pal(n = 4, name = "Dark2"), unique(TRZ24_annot_mat$indv))
col_ha_24hr <- HeatmapAnnotation(df=TRZ24_annot_mat,
                                col=list(
                                  trt = c(TRZ="#707031",VEH="#41B333"),
                                  indv = indv_24color))
wss <- sapply(1:15, function(k) {
  kmeans(TRZ_VEH_24hr_mat, centers = k, nstart = 10)$tot.withinss
})

plot(1:15, wss, type = "b", pch = 19,
     xlab = "Number of Clusters (K)",
     ylab = "Total Within-Cluster Sum of Squares",
     main = "Elbow Method for Choosing K")                                   
```


```{r TRZ 24hr heatmap map, fig.height=8, fig.width=5}
Heatmap(TRZ_VEH_24hr_mat, 
        top_annotation = col_ha_24hr,
        show_column_names = TRUE,
        show_row_names = FALSE,
        cluster_columns = TRUE,
        cluster_rows = FALSE,
        use_raster=TRUE,
        raster_device="png",
        raster_quality = 2,
        row_km = 5,
        column_title = "24 Hour Log2cpm of 24 hr DARs")
  
```

