---
title: "ATAC_fastqc"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
# library(ggsignif)
# library(cowplot)
# library(ggpubr)
# library(scales)
# library(sjmisc)
library(kableExtra)
# library(broom)
# library(biomaRt)
library(RColorBrewer)
# library(gprofiler2)
# library(qvalue)
```
## Total Sequences
This code takes the multiqc fastqc output file and:
splits by rows to trimmed and non trimmed, then separates the trimmed file names into catagories I want, then adds back in the non trimmed data rows (while also splitting file name like the trimmed file name).
after rbind, I split treatmenttime by position, fix the names of the time column, remove numbers from trt column, add a new column called "trimmed" where I add in a vector that lets me group by trimmed file verses non trimmed file, the select only those columns containing the columns I want to keep. 
```{r data loading}
multiqc_fastqc2 <- read_csv("data/multiqc_fastqc_run2.txt")
multiqc_general_stats2 <- read_csv("data/multiqc_genestat_run2.txt")


fastqc_full <- multiqc_fastqc2 %>% 
  slice_tail(n=144) %>% 
  separate(Filename, into = c(NA,"ind","treatmenttime",NA,"read")) %>% 
  rbind(., (multiqc_fastqc2 %>% slice_head(n=144) %>% separate(Filename, into = c("ind","treatmenttime",NA,"read")))) %>% 
  separate_wider_position(., col =treatmenttime,c(2,trt=2,time=3),too_few = "align_start") %>% 
  mutate(time=case_match(trt,"E2"~"24h","E3"~"3h","M2"~"24h", "M3"~"3h","T2"~"24h","T3"~"3h","V2"~"24h","V3"~"3h",.default = time)) %>% 
  mutate(trt=gsub("[[:digit:]]", "", trt) ) %>% 
  mutate(trimmed = if_else(grepl(pattern ="^trim", x = Sample)==TRUE, "yes","no")) %>% 
  select(Sample:read, trimmed,`Total Sequences`:avg_sequence_length) %>% 
  full_join(., multiqc_general_stats2, join_by(Sample)) %>% 
   rename("percent_gc"="FastQC_mqc-generalstats-fastqc-percent_gc",
         "avg_seq_len"= "FastQC_mqc-generalstats-fastqc-avg_sequence_length",
         "percent_dup"= "FastQC_mqc-generalstats-fastqc-percent_duplicates",
         "percent_fails"= "FastQC_mqc-generalstats-fastqc-percent_fails",
         "total_sequences"= "FastQC_mqc-generalstats-fastqc-total_sequences") %>% 
  mutate(ind = factor(ind, levels = c("Ind1", "Ind2", "Ind3", "Ind4", "Ind5", "Ind6"))) %>%
  mutate(time = factor(time, levels = c("3h", "24h"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels = c("DX","E", "DA","M", "T", "V"), labels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) 

```
(in this case, Sample, ind, trt, time read, trimmed, Total sequences, Flagged poor  quality, sequence length, %GC,total deduplicated %,and avg sequence length)
I also then addin the gen_stats file and rename the columns to normal things.
```{r ggplot Total sequences}
fastqc_full
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
fastqc_full %>% 
  filter(trimmed=="no") %>%
  ggplot(., aes(x=trt, y= `Total Sequences`))+
  geom_col(aes(fill= trt))+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
  ggtitle("Total Sequences, untrimmed")+
      # ylab(ylab)+
      xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))

fastqc_full %>% 
  filter(trimmed=="yes") %>% 
  ggplot(., aes(x=trt, y= `Total Sequences`))+
  geom_col(aes(fill= trt))+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
  ggtitle("Total Sequences, trimmed")+
      # ylab(ylab)+
      xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))

totseq <- fastqc_full %>% 
  dplyr::filter(read =='R1') %>% 
  # group_by(ind,trt,time) %>% 
 select(Sample, ind, trt, time, trimmed, `Total Sequences`) %>% 
  pivot_wider(id_cols = c(ind,trt,time), names_from = trimmed, values_from = `Total Sequences`) %>% 
  mutate(perc_removed=(no-yes)/no*100) #%>% 
 kable(list(totseq[1:36,], totseq[37:72,]),caption= "Summary of Total sequences before and after trimming, with percentage of removed sequences") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) #%>%
   # scroll_box(width = "100%", height = "400px")
  
  totseq %>% 
    ggplot(.,aes(x=trt,y=perc_removed) )+
    geom_col(aes(fill= trt))+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
  ggtitle("Total Sequences, percent removed")+
      # ylab(ylab)+
      xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))
```
##Average sequence length  


```{r avg seq length}
fastqc_full %>% 
  
  filter(trimmed=="no") %>%
  mutate(avg_sequence_length=as.numeric(avg_sequence_length)) %>% 
  ggplot(., aes(x=read, y= avg_seq_len))+
  geom_boxplot(aes(fill= trt))+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
  # ylim(0,55)+
  ggtitle("Average sequence length, untrimmed")+
      # ylab(ylab)+
      # xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          # axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))

fastqc_full %>% 
  filter(trimmed=="yes") %>% 
   mutate(avg_sequence_length=as.numeric(avg_sequence_length)) %>% 
  ggplot(., aes(x=read, y= avg_seq_len))+
  geom_boxplot(aes(col= trt))+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  scale_color_manual(values = drug_pal)+
  theme_bw()+
  ggtitle("Average sequence length, trimmed")+
      # ylab(ylab)+
      # xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          # axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))
  


```


```{r percentdup, fig.width=12}
fastqc_full %>% 
  
  filter(trimmed=="no") %>%
  group_by(trt) %>% 
  # mutate(avg_sequence_length=as.numeric(avg_sequence_length)) %>% 
  ggplot(., aes(x=read, y= percent_dup))+
  geom_col(position= "dodge",aes(fill= trt))+
  geom_text(aes(group=trt,label = sprintf("%.1f",percent_dup)),
            position=position_dodge(width =.95),angle= 90,vjust=.02, hjust=.7 )+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
  # ylim(0,55)+
  ggtitle("Percent duplicated, untrimmed")+
      # ylab(ylab)+
      # xlab("")+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          # axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))

fastqc_full %>% 
  filter(trimmed=="yes") %>% 
   group_by(trt) %>% 
  # mutate(avg_sequence_length=as.numeric(avg_sequence_length)) %>% 
  ggplot(., aes(x=read, y= percent_dup))+
  geom_col(position= "dodge",aes(fill= trt))+
  geom_text(aes(group=trt,label = sprintf("%.1f",percent_dup)),
            position=position_dodge(width =.95),angle= 90,vjust=.02, hjust=.7 )+
  facet_wrap(ind~time)+
  scale_fill_manual(values=drug_pal)+
  theme_bw()+
      theme(strip.background = element_rect(fill = "white",linetype=1, linewidth = 0.5),
          plot.title = element_text(size=14,hjust = 0.5,face="bold"),
          axis.title = element_text(size = 10, color = "black"),
          axis.ticks = element_line(linewidth = 0.5),
          axis.line = element_line(linewidth = 0.5),
          # axis.text.x = element_blank(),
          strip.text.x = element_text(margin = margin(2,0,2,0, "pt"),face = "bold"))
  


```
