---
title: "GO_analysis_DARs"
author: "Renee Matthews"
date: "2025-06-16"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)
library(readxl)
library(gprofiler2)

```
### Loading DATA 

```{r adding dataframes}
## significant DAR regions associated to TSS

toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))
peakAnnoList_DOX_DAR <- readRDS("data/Final_four_data/re_analysis/DOX_DAR_annotated_peaks_chipannno.RDS")
Assigned_genes_toPeak <- peakAnnoList_DOX_DAR$DOX_24 %>% as.data.frame() %>% 
  dplyr::select(mcols.genes,annotation, geneId, distanceToTSS) %>% 
  dplyr::rename("Peakid"=mcols.genes)

DOX3_DAR <- peakAnnoList_DOX_DAR$DOX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DOX24_DAR <- peakAnnoList_DOX_DAR$DOX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

DOX3_DAR_up <- peakAnnoList_DOX_DAR$DOX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DOX24_DAR_up <- peakAnnoList_DOX_DAR$DOX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)


DOX3_DAR_down <- peakAnnoList_DOX_DAR$DOX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DOX24_DAR_down <- peakAnnoList_DOX_DAR$DOX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

EPI3_DAR <- peakAnnoList_DOX_DAR$EPI_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
EPI24_DAR <- peakAnnoList_DOX_DAR$EPI_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

EPI3_DAR_up <- peakAnnoList_DOX_DAR$EPI_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
EPI24_DAR_up <- peakAnnoList_DOX_DAR$EPI_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)


EPI3_DAR_down <- peakAnnoList_DOX_DAR$EPI_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
EPI24_DAR_down <- peakAnnoList_DOX_DAR$EPI_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

DNR3_DAR <- peakAnnoList_DOX_DAR$DNR_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DNR24_DAR <- peakAnnoList_DOX_DAR$DNR_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

DNR3_DAR_up <- peakAnnoList_DOX_DAR$DNR_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DNR24_DAR_up <- peakAnnoList_DOX_DAR$DNR_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)


DNR3_DAR_down <- peakAnnoList_DOX_DAR$DNR_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
DNR24_DAR_down <- peakAnnoList_DOX_DAR$DNR_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

MTX3_DAR <- peakAnnoList_DOX_DAR$MTX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
MTX24_DAR <- peakAnnoList_DOX_DAR$MTX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

MTX3_DAR_up <- peakAnnoList_DOX_DAR$MTX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
MTX24_DAR_up <- peakAnnoList_DOX_DAR$MTX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC>0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)


MTX3_DAR_down <- peakAnnoList_DOX_DAR$MTX_3 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>%
dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)
MTX24_DAR_down <- peakAnnoList_DOX_DAR$MTX_24 %>% 
  as.data.frame() %>% 
  dplyr::filter(mcols.adj.P.Val <0.05) %>% 
  dplyr::filter(mcols.logFC<0) %>% 
   dplyr::rename("Peakid"=mcols.genes) %>% 
  distinct(Peakid)

RNA_results <-
toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  tidyr::unite("sample",time, id) %>% 
  pivot_wider(., id_cols = c(ENTREZID,SYMBOL),names_from = sample, values_from = logFC) %>% 
  rename_with(~ str_replace(., "hours", "RNA"))


DOX24_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="24_hours_DOX")

DOX3_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="3_hours_DOX")


MTX24_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="MTX") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="24_hours_MTX")

MTX3_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="MTX") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="3_hours_MTX")

EPI24_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="EPI") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="24_hours_EPI")

EPI3_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="EPI") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="3_hours_EPI")

DNR24_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DNR") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="24_hours_DNR")

DNR3_degs <- toplistall_RNA %>%
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DNR") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(sample:SYMBOL,adj.P.Val,logFC) %>% 
  dplyr::filter(adj.P.Val<0.05) %>% 
  dplyr::filter(sample=="3_hours_DNR")

RNA_all_expressed <-toplistall_RNA %>% 
  dplyr::select(time:logFC,adj.P.Val) %>% 
  dplyr::filter(id=="DOX") %>% 
  dplyr::filter(time=="24_hours") %>% 
  tidyr::unite("sample",time, id) %>% 
  dplyr::select(ENTREZID, SYMBOL)  

Peak_gene_RNA_LFC <- Assigned_genes_toPeak %>% 
  left_join(., RNA_results, by =c("geneId"="ENTREZID"))


entrez_ids <- Assigned_genes_toPeak$geneId  


gene_info <- AnnotationDbi::select(
  org.Hs.eg.db,
  keys = entrez_ids,
  columns = c("SYMBOL"),
  keytype = "ENTREZID"
)
gene_info_collapsed <- gene_info %>%
  group_by(ENTREZID) %>%
  summarise(SYMBOL = paste(unique(SYMBOL), collapse = ","), .groups = "drop")
```


### DOX
### DOX DAR_DEGs 3 and 24 hour @ 20kb
```{r}

DOX_DAR_DEG_3hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX3_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% DOX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DOX_DAR_DEG_24hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX24_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% DOX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

length(DOX_DAR_DEG_3hour_20kb$geneId)
length(DOX_DAR_DEG_24hour_20kb$geneId)
DOX_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/DOX_DAR_DEG_24hour_20kb_res.RDS")

####Sample of gost code run
# DOX_DAR_DEG_24hour_20kb_res <- gost(query = DOX_DAR_DEG_24hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(DOX_DAR_DEG_24hour_20kb_res,"data/Final_four_data/re_analysis/DOX_DAR_DEG_24hour_20kb_res.RDS")
```
the length of DOX_3 hour 20kb DAR_DEGS is `r length(DOX_DAR_DEG_3hour_20kb$geneId)` so no enrichment could take place.
### DOX 24hr 20kb
```{r, fig.height=5}

DOX_DD_2420kb_nomtable <-  DOX_DAR_DEG_24hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DOX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in DOX_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DOX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour DOX_DAR pairs (within 20kb of TSS) GO:BP enriched terms top 10")

```
### DOX 24hr 20kb KEGG

```{r, fig.height=3}

DOX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in DOX_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DOX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour DOX_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
```


### DOX 3 hour up/down 20kb

There was not enough DAR-DEG pairs at 20kb to do enrichment analysis up or down
```{r}

DOX_DAR_DEG_3hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX3_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% DOX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DOX_DAR_DEG_24hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX24_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% DOX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

DOX_DAR_DEG_3hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX3_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% DOX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DOX_DAR_DEG_24hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DOX24_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% DOX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)
length(DOX_DAR_DEG_3hour_20kb_down$geneId)
length(DOX_DAR_DEG_24hour_20kb_down$geneId)

DOX_DAR_DEG_24hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/DOX_DAR_DEG_24hour_20kb_up_res.RDS")
DOX_DAR_DEG_24hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/DOX_DAR_DEG_24hour_20kb_down_res.RDS")

# DOX_DAR_DEG_24hour_20kb_up_res <- gost(query = DOX_DAR_DEG_24hour_20kb_up$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(DOX_DAR_DEG_24hour_20kb_up_res,"data/Final_four_data/re_analysis/DOX_DAR_DEG_24hour_20kb_up_res.RDS")
```
### DOX 24 hour up 20kb
```{r DOX_DAR up GO 20kb, fig.height=5}
# DOX_DAR_DEG_24hour_20kb_up_res$result

DOX_DD_24_up_nomtable <-  DOX_DAR_DEG_24hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DOX_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up DOX_DAR_DEG_pairs 24 hours up") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DOX_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up DOX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10")


```


```{r DOX_DAR up KEGG 20kb}
DOX_DD_24_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up DOX_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### DOX 24 hour down 20kb
```{r DOX_DAR down GO 20kb, fig.height=5}

DOX_DAR_DEG_24hour_20kb_down_res$result

DOX_DD_24_down_nomtable <-  DOX_DAR_DEG_24hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DOX_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down DOX_DAR_DEG_pairs 24 hours") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DOX_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down DOX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10")

```

```{r DOX_DAR down KEGG 20kb}
DOX_DD_24_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down DOX_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```


### EPI


```{r}

EPI_DAR_DEG_3hour_2kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI3_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% EPI3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS <2000) %>% 
  distinct(geneId)

EPI_DAR_DEG_24hour_2kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI24_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% EPI24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-2000 & distanceToTSS <2000) %>%
  distinct(geneId)

length(EPI_DAR_DEG_3hour_2kb$geneId)
length(EPI_DAR_DEG_24hour_2kb$geneId)
EPI_DAR_DEG_3hour_2kb_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_2kb_res.RDS")

# EPI_DAR_DEG_3hour_2kb_res <- gost(query = EPI_DAR_DEG_3hour_2kb$geneId,
#                     organism = "hsapiens",
#                     significant = FALSE,
#                     ordered_query = FALSE,
#                     domain_scope = "custom",
#                     measure_underrepresentation = FALSE,
#                     evcodes = FALSE,
#                     user_threshold = 0.05,
#                     correction_method = c("fdr"),
#                     custom_bg = RNA_all_expressed$ENTREZID,
#                     sources=c("GO:BP","KEGG","GO:MF"))
# 
# saveRDS(EPI_DAR_DEG_3hour_2kb_res,"data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_2kb_res.RDS")
EPI_DAR_DEG_24hour_2kb_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_2kb_res.RDS")

# EPI_DAR_DEG_24hour_2kb_res <- gost(query = EPI_DAR_DEG_24hour_2kb$geneId,
#                     organism = "hsapiens",
#                     significant = FALSE,
#                     ordered_query = FALSE,
#                     domain_scope = "custom",
#                     measure_underrepresentation = FALSE,
#                     evcodes = FALSE,
#                     user_threshold = 0.05,
#                     correction_method = c("fdr"),
#                     custom_bg = RNA_all_expressed$ENTREZID,
#                     sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(EPI_DAR_DEG_24hour_2kb_res,"data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_2kb_res.RDS")
```
 


### EPI 3 hour 20kb DAR DEGS
```{r}

EPI_DAR_DEG_3hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI3_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% EPI3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

EPI_DAR_DEG_24hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI24_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% EPI24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

length(EPI_DAR_DEG_3hour_20kb$geneId)
length(EPI_DAR_DEG_24hour_20kb$geneId)
EPI_DAR_DEG_3hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_20kb_res.RDS")

# EPI_DAR_DEG_3hour_20kb_res <- gost(query = EPI_DAR_DEG_3hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(EPI_DAR_DEG_3hour_20kb_res,"data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_20kb_res.RDS")
```


```{r 3hr 20kb ePI, fig.height=10}

EPI_DD_320kb_nomtable <-  EPI_DAR_DEG_3hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in EPI_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour EPI_DAR_DEG pairs (within 2kb of TSS) GO:BP enriched terms top 60 20kb")
```
### EPI 3 hour 20kb DAR DEGS KEGG

```{r}

EPI_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in EPI_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour EPI_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
```


### EPI 24hr DAR DEG 20kb
```{r EPI  24 hour 20kb}
EPI_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_20kb_res.RDS")

# EPI_DAR_DEG_24hour_20kb_res <- gost(query = EPI_DAR_DEG_24hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(EPI_DAR_DEG_24hour_20kb_res,"data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_20kb_res.RDS")
```

```{r, fig.height=5}



EPI_DD_2420kb_nomtable <-  EPI_DAR_DEG_24hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in EPI_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour EPI_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10 ")

```

### EPI 24hr DAR DEG KEGG
```{r EPI  24 hour 20kb KEGG}

EPI_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in EPI_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour EPI_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
```



After running gprofiler2, i saved the results as .RDS files to save time in the future. Now I just extract the information and graph.
up


### EPI up and down 20kb
```{r}

EPI_DAR_DEG_3hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI3_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% EPI3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

EPI_DAR_DEG_24hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI24_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% EPI24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

EPI_DAR_DEG_3hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI3_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% EPI3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

EPI_DAR_DEG_24hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%EPI24_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% EPI24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)
length(EPI_DAR_DEG_3hour_20kb_down$geneId)
length(EPI_DAR_DEG_24hour_20kb_down$geneId)

EPI_DAR_DEG_3hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_20kb_up_res.RDS")
EPI_DAR_DEG_3hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_20kb_down_res.RDS")
EPI_DAR_DEG_24hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_20kb_up_res.RDS")
EPI_DAR_DEG_24hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/EPI_DAR_DEG_24hour_20kb_down_res.RDS")

# EPI_DAR_DEG_24hour_20kb_down_res <- gost(query = EPI_DAR_DEG_24hour_20kb_down$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(EPI_DAR_DEG_3hour_20kb_up_res,"data/Final_four_data/re_analysis/EPI_DAR_DEG_3hour_20kb_up_res.RDS")
```
### EPI 3 hour 20kb up
```{r EPI_DAR 20 3 up GO, fig.height=10}
# EPI_DAR_DEG_24hour_20kb_up_res$result

EPI_DD_3_up_nomtable <-  EPI_DAR_DEG_3hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up EPI_DAR_DEG_pairs 3hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour up EPI_DAR pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

EPI 3 hour 20kb up KEGG
```{r EPI_DAR 3hr up KEGG 20kb}


EPI_DD_24_up_nomtable <-  EPI_DAR_DEG_24hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_24_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up EPI_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### EPI 3 hour 20kb down
```{r EPI_DAR 3 hour  down GO 20kb, fig.height=10}

# EPI_DAR_DEG_3hour_20kb_down_res$result

EPI_DD_3_down_nomtable <-  EPI_DAR_DEG_3hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down EPI_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down EPI_DAR pairs (within 20kb of TSS) GO:BP enriched terms top 45")

```

EPI 3 hour 20kb down KEGG
```{r EPI_DAR down 3h KEGG 20kb}
EPI_DD_3_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down EPI_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 45")
### parsing similar terms:  
```

### EPI 24 hour 20kb up
```{r EPI_DAR 20 24 up GO, fig.height=10}
# EPI_DAR_DEG_24hour_20kb_up_res$result

EPI_DD_24_up_nomtable <-  EPI_DAR_DEG_24hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in up EPI_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up EPI_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")

```

EPI 24 hour 20kb up KEGG
```{r EPI_DAR up KEGG 24 hr20kb}
EPI_DD_24_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up EPI_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### EPI 24 hour 20kb down
```{r EPI_DAR down GO 20kb, fig.height=5}

# EPI_DAR_DEG_24hour_20kb_down_res$result

EPI_DD_24_down_nomtable <-  EPI_DAR_DEG_24hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

EPI_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down EPI_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


EPI_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down EPI_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10")

```
EPI 24 hour 20kb down KEGG

```{r EPI_DAR down KEGG 20kb}
EPI_DD_24_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down EPI_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```




### DNR

```{r}

DNR_DAR_DEG_3hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR3_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% DNR3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DNR_DAR_DEG_24hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR24_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% DNR24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

length(DNR_DAR_DEG_3hour_20kb$geneId)
length(DNR_DAR_DEG_24hour_20kb$geneId)
DNR_DAR_DEG_3hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_3hour_20kb_res.RDS")
DNR_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_res.RDS")


# DNR_DAR_DEG_24hour_20kb_res <- gost(query = DNR_DAR_DEG_24hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(DNR_DAR_DEG_24hour_20kb_res,"data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_res.RDS")
```
### DNR 3hr 20kb DAR DEGS

```{r 3hr 20kb DNR, fig.height=10}



DNR_DD_320kb_nomtable <-  DNR_DAR_DEG_3hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in DNR_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour DNR_DAR_DEG pairs (within 2kb of TSS) GO:BP enriched terms top 60 20kb")
```
### DNR 3hr 20kb DAR DEGS KEGG

```{r}

DNR_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in DNR_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour DNR_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
```


### DNR 24 hr 20kb DAR DEGS 
```{r DNR  24 hour 20kb}
DNR_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_res.RDS")

# DNR_DAR_DEG_24hour_20kb_res <- gost(query = DNR_DAR_DEG_24hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(DNR_DAR_DEG_24hour_20kb_res,"data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_res.RDS")
```
```{r, fig.height=5}

DNR_DD_2420kb_nomtable <-  DNR_DAR_DEG_24hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in DNR_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour DNR_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10 20kb")


```
### DNR 24 hr 20kb DAR DEGS KEGG

```{r DNR  24 hour 20kb KEGG}

DNR_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in DNR_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour DNR_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
```



### DNR up and down 20kb
```{r}

DNR_DAR_DEG_3hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR3_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% DNR3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DNR_DAR_DEG_24hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR24_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% DNR24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

DNR_DAR_DEG_3hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR3_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% DNR3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

DNR_DAR_DEG_24hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%DNR24_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% DNR24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)
length(DNR_DAR_DEG_3hour_20kb_down$geneId)
length(DNR_DAR_DEG_24hour_20kb_down$geneId)

DNR_DAR_DEG_3hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_3hour_20kb_up_res.RDS")
DNR_DAR_DEG_3hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_3hour_20kb_down_res.RDS")
DNR_DAR_DEG_24hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_up_res.RDS")
DNR_DAR_DEG_24hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_down_res.RDS")

# DNR_DAR_DEG_24hour_20kb_up_res <- gost(query = DNR_DAR_DEG_24hour_20kb_up$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(DNR_DAR_DEG_24hour_20kb_up_res,"data/Final_four_data/re_analysis/DNR_DAR_DEG_24hour_20kb_up_res.RDS")
```
### DNR 3 hours 20 kb up
```{r DNR_DAR 20 3 up GO, fig.height=10}
# DNR_DAR_DEG_24hour_20kb_up_res$result

DNR_DD_3_up_nomtable <-  DNR_DAR_DEG_3hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up DNR_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour up DNR_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


# DNR_DD_3_up_nomtable %>%
#   dplyr::filter(source=="GO:MF") %>% 
#   dplyr::filter(p_value < 0.05) %>% 
#   mutate(log10_p=(-log(p_value, base=10))) %>% 
#   slice_max(log10_p, n=60) %>% 
#   ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
#     geom_col()+
#   geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
#   theme_bw()+
#   ylab("")+
#   xlab(paste0("-log10 p-value"))+
#   guides(fill="none")+
#   theme(axis.text.y = element_text(color="black"))+
#   ggtitle("24 hour up DNR_DAR_DEG pairs (within 20kb of TSS) GO:MF enriched terms top 60")
```

DNR 3 hours 20 kb up KEGG
```{r DNR_DAR up 3 hour KEGG 20kb}
DNR_DD_3_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour up DNR_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### DNR 3 hours 20 kb down
```{r DNR_DAR down 3hr GO 20kb, fig.height=10}

DNR_DAR_DEG_3hour_20kb_down_res$result

DNR_DD_3_down_nomtable <-  DNR_DAR_DEG_3hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down DNR_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down DNR DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

DNR 3 hours 20 kb down KEGG
```{r DNR_DAR down 3hr KEGG 20kb}
DNR_DD_3_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down DNR_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```


### DNR 24 hours 20 kb up
```{r DNR_DAR 20 24 up GO, fig.height=10}
# DNR_DAR_DEG_24hour_20kb_up_res$result

DNR_DD_24_up_nomtable <-  DNR_DAR_DEG_24hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up DNR_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up DNR_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

DNR 24 hours 20 kb up KEGG
```{r DNR_DAR up 24 hour KEGG 20kb}
DNR_DD_24_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up DNR_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### DNR 24 hour 20kb down
```{r DNR_DAR down 24d GO 20kb, fig.height=10}

# DNR_DAR_DEG_24hour_20kb_down_res$result

DNR_DD_24_down_nomtable <-  DNR_DAR_DEG_24hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

DNR_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down DNR_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


DNR_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down DNR_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

DNR 24 hour 20kb down KEGG
```{r DNR_DAR down 24hr KEGG 20kb}
DNR_DD_24_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down DNR_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```



### MTX

###  MTX 3hr 20kb DAR DEGS
```{r}

MTX_DAR_DEG_3hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX3_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% MTX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

MTX_DAR_DEG_24hour_20kb <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX24_DAR$Peakid) %>% 
  dplyr::filter(geneId %in% MTX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

length(MTX_DAR_DEG_3hour_20kb$geneId)
length(MTX_DAR_DEG_24hour_20kb$geneId)
MTX_DAR_DEG_3hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_3hour_20kb_res.RDS")
MTX_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_res.RDS")


# MTX_DAR_DEG_3hour_20kb_res <- gost(query = MTX_DAR_DEG_3hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(MTX_DAR_DEG_3hour_20kb_res,"data/Final_four_data/re_analysis/MTX_DAR_DEG_3hour_20kb_res.RDS")
```

```{r 3hr 20kb MTX, fig.height=10}

MTX_DD_320kb_nomtable <-  MTX_DAR_DEG_3hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in MTX_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_320kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour MTX_DAR_DEG pairs (within 2kb of TSS) GO:BP enriched terms top 60 20kb")
```
###  MTX 3hr 20kb DAR DEGS KEGG

```{r}

MTX_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in MTX_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_320kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour MTX_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
```


### MTX 24hr 20kb DAR DEGS
```{r MTX  24 hour 20kb}
MTX_DAR_DEG_24hour_20kb_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_res.RDS")

# MTX_DAR_DEG_24hour_20kb_res <- gost(query = MTX_DAR_DEG_24hour_20kb$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(MTX_DAR_DEG_24hour_20kb_res,"data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_res.RDS")
```

```{r, fig.height=5}

MTX_DD_2420kb_nomtable <-  MTX_DAR_DEG_24hour_20kb_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in MTX_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=10) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour MTX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 10 20kb")


```
### MTX 24hr 20kb DAR DEGS KEGG

```{r MTX  24 hour 20kb KEGG}

MTX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  # dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "KEGG terms found in MTX_DAR_DEG_pairs 24hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_2420kb_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour MTX_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
```


### MTX up and down 20kb
```{r}

MTX_DAR_DEG_3hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX3_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% MTX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

MTX_DAR_DEG_24hour_20kb_up <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX24_DAR_up$Peakid) %>% 
  dplyr::filter(geneId %in% MTX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)

MTX_DAR_DEG_3hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX3_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% MTX3_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>% 
  distinct(geneId)

MTX_DAR_DEG_24hour_20kb_down <- Assigned_genes_toPeak %>% 
  dplyr::filter(Peakid %in%MTX24_DAR_down$Peakid) %>% 
  dplyr::filter(geneId %in% MTX24_degs$ENTREZID) %>% 
  dplyr::filter(distanceToTSS >-20000 & distanceToTSS <20000) %>%
  distinct(geneId)
length(MTX_DAR_DEG_3hour_20kb_down$geneId)
length(MTX_DAR_DEG_24hour_20kb_down$geneId)

MTX_DAR_DEG_3hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_3hour_20kb_up_res.RDS")
MTX_DAR_DEG_3hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_3hour_20kb_down_res.RDS")
MTX_DAR_DEG_24hour_20kb_up_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_up_res.RDS")
MTX_DAR_DEG_24hour_20kb_down_res <- readRDS("data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_down_res.RDS")

# MTX_DAR_DEG_24hour_20kb_down_res <- gost(query = MTX_DAR_DEG_24hour_20kb_down$geneId,
# organism = "hsapiens",
# significant = FALSE,
# ordered_query = FALSE,
# domain_scope = "custom",
# measure_underrepresentation = FALSE,
# evcodes = FALSE,
# user_threshold = 0.05,
# correction_method = c("fdr"),
# custom_bg = RNA_all_expressed$ENTREZID,
# sources=c("GO:BP","KEGG","GO:MF"))
# saveRDS(MTX_DAR_DEG_24hour_20kb_down_res,"data/Final_four_data/re_analysis/MTX_DAR_DEG_24hour_20kb_down_res.RDS")
```
### MTX 3 hours 20kb up
```{r MTX_DAR 20 3 up GO}
# MTX_DAR_DEG_24hour_20kb_up_res$result

MTX_DD_3_up_nomtable <-  MTX_DAR_DEG_3hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up MTX_DAR_DEG_pairs 3 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_3_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour up MTX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

MTX 3 hours 20kb up KEGG
```{r MTX_DAR up 3 hour KEGG 20kb}
MTX_DD_3_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour up MTX_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### MTX 3 hours 20kb down
no results
```{r MTX_DAR down 3hr GO 20kb, fig.height=10, eval= FALSE}

# MTX_DAR_DEG_3hour_20kb_down_res$result

MTX_DD_3_down_nomtable <-  MTX_DAR_DEG_3hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down MTX_DAR_DEG_pairs 3hours") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down MTX_DARDEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


MTX_DD_3_down_nomtable %>%
  dplyr::filter(source=="GO:MF") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down MTX_DAR_DEG pairs (within 20kb of TSS) GO:MF enriched terms top 60")
### parsing similar terms:  
```

```{r MTX_DAR down 3down null KEGG 20kb, eval=FALSE}
MTX_DD_3_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("3 hour down MTX_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```

### MTX 24 hours 20kb up
```{r MTX_DAR 20 24 up GO, fig.height=10}
# MTX_DAR_DEG_24hour_20kb_up_res$result

MTX_DD_24_up_nomtable <-  MTX_DAR_DEG_24hour_20kb_up_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  up MTX_DAR_DEG_pairs 24 hours 20kb") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_24_up_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up MTX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

MTX 24 hours 20kb up KEGG
```{r MTX_DAR up 24 hour KEGG 20kb}
MTX_DD_24_up_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour up MTX_DAR pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```
### MTX 24 hours 20kb down  

```{r MTX_DAR down 24hour GO 20kb, fig.height=10}

# MTX_DAR_DEG_24hour_20kb_down_res$result

MTX_DD_24_down_nomtable <-  MTX_DAR_DEG_24hour_20kb_down_res$result %>%
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))

MTX_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = "Significant (p < 0.05 )terms found in  down MTX_DAR_DEG_pairs 24hours") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")


MTX_DD_24_down_nomtable %>%
  dplyr::filter(source=="GO:BP") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=45) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down MTX_DAR_DEG pairs (within 20kb of TSS) GO:BP enriched terms top 45")


```

MTX 24 hours 20kb down KEGG
```{r MTX_DAR down 24h KEGG 20kb}
MTX_DD_24_down_nomtable %>%
  dplyr::filter(source=="KEGG") %>% 
  dplyr::filter(p_value < 0.05) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  slice_max(log10_p, n=60) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col()+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle("24 hour down MTX_DAR_DEG pairs (within 20kb of TSS) KEGG enriched terms top 60")
### parsing similar terms:  
```


### KEGG heatmap of terms

```{r , fig.height=6}
filt_term_id <- bind_rows(DOX_DD_2420kb_nomtable %>%
  mutate(group="DOX_24") %>% 
  dplyr::filter(source =="KEGG",
                p_value < 0.05) %>% 
  dplyr::filter(term_id !="KEGG:00000") %>% 
  slice_head(n=5),(EPI_DD_2420kb_nomtable %>%
  mutate(group="EPI_24") %>% 
  dplyr::filter(source =="KEGG",
                p_value < 0.05) %>% 
  dplyr::filter(term_id !="KEGG:00000") %>% 
  slice_head(n=5))) %>% 
    bind_rows((DNR_DD_2420kb_nomtable %>%
  mutate(group="DNR_24") %>% 
  dplyr::filter(source =="KEGG",
                p_value < 0.05) %>% 
  dplyr::filter(term_id !="KEGG:00000") %>% 
  slice_head(n=5))) %>% 
    bind_rows((MTX_DD_2420kb_nomtable %>%
  mutate(group="MTX_24") %>% 
  dplyr::filter(source =="KEGG",
                p_value < 0.05) %>% 
  dplyr::filter(term_id !="KEGG:00000") %>% 
  slice_head(n=5))) %>% 
  distinct(term_id)

KEGGtable <-   bind_rows((DOX_DD_2420kb_nomtable %>% mutate(group="DOX_24")),(EPI_DD_2420kb_nomtable %>% mutate(group="EPI_24"))) %>%
  bind_rows(.,(DNR_DD_2420kb_nomtable %>% mutate(group="DNR_24"))) %>% 
  bind_rows(.,(MTX_DD_2420kb_nomtable %>% mutate(group="MTX_24"))) %>% 
  dplyr::filter(source =="KEGG") %>% 
  dplyr::filter(term_id %in% filt_term_id$term_id)

mat <- KEGGtable %>%
  unite(KEGG,term_id, term_name, sep="_") %>% 
  dplyr::select(group,KEGG,p_value) %>% 
  mutate(p_value=(log10(p_value)*-1)) %>% 
  pivot_wider(., id_cols = group, names_from = KEGG, values_from = p_value) %>% 
  column_to_rownames("group") %>% 
  as.matrix() 
  ComplexHeatmap::Heatmap(mat, 
                          name = "p-value", 
                          col = colorRamp2(c(0, 1, 4), c("blue", "white", "red")),
                          cluster_rows = FALSE, 
                          cluster_columns = FALSE,
                          column_names_rot = -45,  # Rotate to 45 degrees
                          column_names_gp = gpar(fontsize = 8),  # Smaller font size
                          show_row_names = TRUE, 
                          show_column_names = TRUE,
                           cell_fun = function(j, i, x, y, width, height, fill) {
    if (!is.na(mat[i, j]) && mat[i, j] > 1.30103) {
      grid.text("*", x = x, y = y, gp = gpar(fontsize = 20, col = "black"))
    }
  }
)

```

