---
title: "GO and KEGG pathway analysis"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(gprofiler2)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(ggVennDiagram)
library(BiocParallel)
library(ggpubr)
library(biomaRt)

```


```{r table function}
GO_KEGG_analysis <- function(df,type, setp_value=1){
# Extract the name of the dataframe
  a <- deparse(substitute(df)) %>% 
  gsub("_NG_2kresgenes","",.)

 # Prepare the table output
  df_nomtable <-  df$result %>% 
  dplyr::select(c(source, term_id,
                  term_name,intersection_size, 
                   term_size, p_value))
# Create a color palette for different dataframe names
  # You can customize this color palette as needed  
  
  mrc_palette <- c(
    "EAR_open" = "#F8766D",
    "EAR_close" = "#f6483c",
    "ESR_open" = "#7CAE00",
    "ESR_close" = "#587b00",
     "ESR_OC" = "#6a9500",
    "ESR_opcl" = "cornflowerblue",
    "ESR_clop"= "grey60",
     "LR_open" = "#00BFC4",
     "LR_close" = "#008d91",
     "NR" = "#C77CFF"
  )
   # Use the dataframe name as the fill color (fallback to black if name is not in the palette)
   fill_color <- mrc_palette[a] %||% "darkgrey"
   
table <- df_nomtable %>%
  dplyr::filter(source==type) %>% 
  dplyr::filter(p_value < setp_value) %>% 
  mutate_at(.vars = 6, .funs = scientific_format()) %>%
  kable(.,caption = paste0("Significant (p < ",setp_value," ) ",type," terms found in ",a," neargenes")) %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(
    full_width = FALSE,
    position = "left",
    bootstrap_options = c("striped", "hover")
  ) %>%
  scroll_box(width = "100%", height = "400px")

# plot the table as ggplot object
plot <- df_nomtable %>%
  filter(source==type) %>% 
  # slice_head(n=10) %>% 
    dplyr::filter(p_value < setp_value) %>% 
  mutate(log10_p=(-log(p_value, base=10))) %>% 
  ggplot(., aes(x=log10_p, y=reorder(term_name, log10_p)))+
    geom_col(fill=fill_color)+
  geom_vline(aes(xintercept=-log(0.05,base = 10)), col="red",linetype = 2)+
  theme_bw()+
  ylab("")+
  xlab(paste0("-log10 p-value"))+
  guides(fill="none")+
  theme(axis.text.y = element_text(color="black"))+
  ggtitle(paste0("(p < ",setp_value," ) ",type," terms found in\n ",a," neargenes"))


print(table)
print(plot)
}
```

##### data loading
```{r loading data}
col_ng_peak <- read.delim("data/Final_four_data/collapsed_new_peaks.txt")
TSS_NG_data <- read_delim("data/Final_four_data/TSS_assigned_NG.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

# scale_fill_mrc <-  function(...){
#   ggplot2:::manual_scale(
#     'fill',
#     values = setNames(c("#F8766D","#f6483c","#7CAE00","#587b00","#6a9500",  "#00BFC4","#008d91", "#C77CFF"), c("EAR_open","EAR_close","ESR_open","ESR_close","ESR_OC","LR_open","LR_close","NR")),
#     ...
#   )
# }
peak_list_all_mrc <- readRDS( "data/Final_four_data/Peak_list_all_mrc_NG.RDS")

background_NGs <- TSS_NG_data %>% distinct(ENTREZID,SYMBOL)



mrc_palette <- c(
    "EAR_open" = "#F8766D",
    "EAR_close" = "#f6483c",
    "ESR_open" = "#7CAE00",
    "ESR_close" = "#587b00",
     "ESR_OC" = "#6a9500",
    "ESR_opcl" = "cornflowerblue",
    "ESR_clop"= "grey60",
     "LR_open" = "#00BFC4",
     "LR_close" = "#008d91",
     "NR" = "#C77CFF"
  )
```


## Introduction

This is an updated page of GO/KEGG analysis based on previous analysis. To get this analysis, I took the  8 sets of peaks from my data and filtered each group by peaks that are within 2000 kb of a TSS of a near-gene.   I used the background of all expressed RNA genes (14,084) (the genes used to generate the  expressed near-gene list) to test for enrichment of GO:Biological Processes and KEGG Pathways.

This page is broken up into the following sections:  
1. Creation of NG lists
2. List of terms from GO:BP and KEGG by each MRC
3. Bargraphs of top KEGG/~~GO terms~~ 

### Making the lists
#### EAR_open to background list

```{r GO_making lists}

EAR_open_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="EAR_open") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)
EAR_close_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="EAR_close") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)
  
ESR_open_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="ESR_open") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)
ESR_close_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="ESR_close") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)
ESR_OC_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="ESR_OC") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)

LR_open_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="LR_open") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)
LR_close_NG_2k<-  peak_list_all_mrc %>% 
      dplyr::filter(mrc =="LR_close") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene:SYMBOL, delim= ",") %>% 
    distinct(NCBI_gene,SYMBOL)

NR_NG_2k <-   peak_list_all_mrc %>%
      dplyr::filter(mrc =="NR") %>% 
    dplyr::filter(dist_to_NG >-2000&dist_to_NG<2000) %>% 
    dplyr::select(Peakid, NCBI_gene:SYMBOL,dist_to_NG, mrc) %>% 
    separate_longer_delim(., cols=NCBI_gene, delim= ",") %>% 
     separate_longer_delim(., cols=,SYMBOL, delim= ",")  
 
# NR_NG_2kresgenes <- gost(query = NR_NG_2k$NCBI_gene,
#                     organism = "hsapiens",
#                     significant = FALSE,
#                     ordered_query = FALSE,
#                     domain_scope = "custom",
#                     measure_underrepresentation = FALSE,
#                     evcodes = FALSE,
#                     user_threshold = 0.05,
#                     correction_method = c("fdr"),
#                     custom_bg = background_NGs$ENTREZID,
#                     sources=c("GO:BP","KEGG"))



# saveRDS(NR_NG_2k,"data/Final_four_data/GO_analysis/NR_NG_2kresgenes.RDS")
# saveRDS(EAR_close_NG_2kresgenes,"data/Final_four_data/GO_analysis/EAR_close_NG_2kresgenes.RDS")
# saveRDS(ESR_close_NG_2kresgenes,"data/Final_four_data/GO_analysis/ESR_close_NG_2kresgenes.RDS")
# saveRDS(ESR_OC_NG_2kresgenes,"data/Final_four_data/GO_analysis/ESR_OC_NG_2kresgenes.RDS")
# saveRDS(LR_open_NG_2kresgenes,"data/Final_four_data/GO_analysis/LR_open_NG_2kresgenes.RDS")
# saveRDS(ESR_open_NG_2kresgenes,"data/Final_four_data/GO_analysis/ESR_open_NG_2kresgenes.RDS")
# saveRDS(EAR_open_NG_2kresgenes,"data/Final_four_data/GO_analysis/EAR_open_NG_2kresgenes.RDS")
NR_NG_2k <- readRDS("data/Final_four_data/GO_analysis/NR_NG_2kresgenes.RDS")
EAR_close_NG_2kresgenes <- readRDS("data/Final_four_data/GO_analysis/EAR_close_NG_2kresgenes.RDS")
ESR_close_NG_2kresgenes <- readRDS("data/Final_four_data/GO_analysis/ESR_close_NG_2kresgenes.RDS")
ESR_OC_NG_2kresgenes <- readRDS("data/Final_four_data/GO_analysis/ESR_OC_NG_2kresgenes.RDS")
LR_open_NG_2kresgenes <- readRDS("data/Final_four_data/GO_analysis/LR_open_NG_2kresgenes.RDS")
LR_close_NG_2kresgenes <- readRDS("data/Final_four_data/GO_analysis/LR_close_NG_2kresgenes.RDS")
ESR_open_NG_2kresgenes <-readRDS ("data/Final_four_data/GO_analysis/ESR_open_NG_2kresgenes.RDS")
EAR_open_NG_2kresgenes<-readRDS  ("data/Final_four_data/GO_analysis/EAR_open_NG_2kresgenes.RDS")


```

## experimental GO

```{r GOBP}
GO_KEGG_analysis(EAR_open_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(EAR_close_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(ESR_open_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(ESR_close_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(ESR_OC_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(LR_open_NG_2kresgenes,"GO:BP", 0.049)
GO_KEGG_analysis(LR_close_NG_2kresgenes,"GO:BP", 0.049)
# GO_KEGG_analysis(NR_NG_2k,"GO:BP", 0.049)

```
 
##### KEGG (not informative)
```{r KEGG analysis}
GO_KEGG_analysis(EAR_open_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(EAR_close_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(ESR_open_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(ESR_close_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(ESR_OC_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(LR_open_NG_2kresgenes,"KEGG", 0.05)
GO_KEGG_analysis(LR_close_NG_2kresgenes,"KEGG", 0.05)
# GO_KEGG_analysis(NR_NG_2k,"KEGG", 0.05)
```

