---
title: "H3K27ac_data_integration"
author: "Renee Matthews"
date: "2025-05-09"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library(rtracklayer)
library(edgeR)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(eulerr)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(ComplexHeatmap)
library(smplot2)
library(stringr)
library(cowplot)
```

###  Integrating ATAC seq and H3K27ac CUT&Tag-seq together
Loading data frames
```{r}

Collapsed_peaks <- read_delim("data/Final_four_data/collapsed_new_peaks.txt",
                              delim = "\t", 
                              escape_double = FALSE, 
                              trim_ws = TRUE)

Motif_list_gr <- readRDS("data/Final_four_data/re_analysis/Motif_list_granges.RDS")
##order specific
df_list <- plyr::llply(Motif_list_gr, as.data.frame)
### no change motif_list_gr names so they do not overwrite the dataframes
names(Motif_list_gr) <- paste0(names(Motif_list_gr), "_gr")
list2env(Motif_list_gr,envir= .GlobalEnv)

list2env(df_list,envir= .GlobalEnv)

final_peaks_gr <- Collapsed_peaks %>% 
  dplyr::filter(Peakid %in% mcols(all_regions_gr)$Peakid) %>% 
  GRanges()

final_peaks <- Collapsed_peaks %>% 
  dplyr::filter(Peakid %in% mcols(all_regions_gr)$Peakid) 

mrc_lookup <- bind_rows(
  (EAR_open  %>% dplyr::select(Peakid) %>% mutate(mrc = "EAR_open")),  
  (EAR_close %>%  dplyr::select(Peakid) %>%mutate(mrc = "EAR_close")),
  (ESR_open  %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_open")),
  (ESR_close %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_close")),
  (ESR_opcl   %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_opcl")),
  (ESR_clop   %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_clop")),
  (LR_open   %>%  dplyr::select(Peakid) %>%mutate(mrc = "LR_open")),
  (LR_close  %>%  dplyr::select(Peakid) %>%mutate(mrc = "LR_close")),
  (NR        %>%  dplyr::select(Peakid) %>%mutate(mrc = "NR"))
) %>%
  distinct(Peakid, mrc) 

RNA_exp_genes <- read.csv("data/other_papers/S13Table_Matthews2024.csv") %>% 
  dplyr::select(ENTREZID,SYMBOL)

# write_csv(median_3_lfc, "data/Final_four_data/re_analysis/median_3_lfc_H3K27ac_norm.csv")
# write_csv(median_24_lfc, "data/Final_four_data/re_analysis/median_24_lfc_H3K27ac_norm.csv")
# write_csv(median_3_lfc, "data/Final_four_data/re_analysis/median_3_lfc_norm.csv")
# write_csv(median_24_lfc, "data/Final_four_data/re_analysis/median_24_lfc_norm.csv")


H3K27ac_gr <- readRDS("data/Final_four_data/re_analysis/H3K27ac_granges_df.RDS")

```

### Overlapping data sets

When doing the overlapping, ATAC regions are labeled with Peakid, H3K27ac regions are labeled with Geneid
```{r}
ol_peaks <- join_overlap_intersect(final_peaks_gr, H3K27ac_gr)
ATAC_region_count <- ol_peaks %>% 
  as.data.frame() %>% 
  distinct(Peakid)
H3K27ac_region_count <- ol_peaks %>% 
  as.data.frame() %>% 
  distinct(Geneid)
Overlap_regions <- ol_peaks %>% 
  as.data.frame() %>% 
  distinct(Peakid,Geneid)
```

Number of ATAC regions: `r length(final_peaks_gr)`  
Number of ATAC regions overlapping H3K27ac regions:`r length(ATAC_region_count$Peakid)` 
`r sprintf("%.2f%%" , (length(ATAC_region_count$Peakid)/length(final_peaks_gr)*100))`  of ATAC peaks overlap an acetylated region.

Number of H3K27ac regions: `r length(H3K27ac_gr)`  
Number of ATAC regions overlapping H3K27ac regions:`r length(H3K27ac_region_count$Geneid)` 
`r sprintf("%.2f%%" , (length(H3K27ac_region_count$Geneid)/length(H3K27ac_gr)*100))`  of H3K27ac peaks overlap an acetylated region.


### Looking at correlation of LFC H3K27ac regions and LFC ATAC regions

```{r  Correlation setup}
H3K27ac_toplist_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results_H3K27ac_data.RDS")
H3K27ac_toptable_list <- bind_rows(H3K27ac_toplist_results, .id = "group")
ATAC_toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")
ATAC_toptable_list <- bind_rows(ATAC_toptable_results, .id = "group")

hr3_K27 <-  H3K27ac_toptable_list %>% 
    separate_wider_delim(., group, names=c("trt","time"), delim="_") %>% 
  dplyr::select(trt,time:logFC) %>% 
  dplyr::filter(time=="3") %>% 
  pivot_wider(., id_cols=c(genes), names_from = trt, values_from = logFC) %>% 
  dplyr::rename(DOX_3_K27=DOX, DNR_3_K27=DNR,EPI_3_K27=EPI,MTX_3_K27=MTX)


hr24_K27 <- H3K27ac_toptable_list %>% 
  separate_wider_delim(., group, names=c("trt","time"), delim="_") %>% 
  dplyr::select(trt,time:logFC) %>% 
  dplyr::filter(time=="24") %>% 
  pivot_wider(., id_cols=c(genes), names_from = trt, values_from = logFC) %>% 
  dplyr::rename(DOX_24_K27=DOX, DNR_24_K27=DNR,EPI_24_K27=EPI,MTX_24_K27=MTX)

K27_LFC_df <- hr3_K27 %>% 
  left_join(., hr24_K27, by=c("genes"="genes")) 


hr3_ATAC <- ATAC_toptable_list %>% 
  dplyr::select(group:logFC) %>% 
    separate_wider_delim(., group, names=c("trt","time"), delim="_") %>% 
  dplyr::filter(time=="3") %>% 
  pivot_wider(., id_cols=c(time, genes), names_from = trt, values_from = logFC) %>% 
  dplyr::select(!TRZ) %>% 
  dplyr::rename(DOX_3_ATAC=DOX, DNR_3_ATAC=DNR,EPI_3_ATAC=EPI,MTX_3_ATAC=MTX) %>% 
  dplyr::rename("peak"=genes)

hr24_ATAC <- ATAC_toptable_list %>% 
  dplyr::select(group:logFC) %>% 
    separate_wider_delim(., group, names=c("trt","time"), delim="_") %>% 
  dplyr::filter(time=="24") %>% 
  pivot_wider(., id_cols=c(time, genes), names_from = trt, values_from = logFC) %>% 
  dplyr::select(!TRZ) %>% 
  dplyr::rename(DOX_24_ATAC=DOX, DNR_24_ATAC=DNR,EPI_24_ATAC=EPI,MTX_24_ATAC=MTX) %>%
  dplyr::rename("peak"=genes)

ATAC_LFC_df <- hr3_ATAC %>% 
  left_join(., hr24_ATAC, by=c("peak"="peak")) %>%
   dplyr::select(!time.x) %>% 
  dplyr::select(!time.y)


```

```{r correlation heatmaps}

K27_ATAC_mat <- Overlap_regions %>%
  left_join(.,ATAC_LFC_df,by=c("Peakid"="peak")) %>% 
  left_join(.,K27_LFC_df, by=c("Geneid"="genes")) %>%
  distinct(Peakid,Geneid,.keep_all = TRUE) %>% 
  tidyr::unite(name,Peakid:Geneid, sep="_") %>% 
  column_to_rownames("name") %>% 
  as.matrix()  


pearson_cor_mat <- cor(K27_ATAC_mat,method = "pearson", use = "pairwise.complete.obs")

## do spearman correlation between matched observation of RNA and ATAC
spearman_cor_mat <- cor(K27_ATAC_mat,method = "spearman", use = "pairwise.complete.obs")
### make correlation heatmaps of both sets

ComplexHeatmap::Heatmap(pearson_cor_mat, 
                        column_title = "Pearson H3K27ac/ATAC LFC correlation")

ComplexHeatmap::Heatmap(spearman_cor_mat,
                        column_title = "Spearman H3K27ac/ATAC LFC correlation")

```
### Integration of RNA, ATAC, and H3K27ac data together

I associated the data together like this:
1)  Take the list of all ATAC regions that overlap H3K27ac regions
2) Join the overlap list of regions with the assigned RNA expressed genes and their distance. 
```{r Adding RNA toplist information}
toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))

hr3_RNA <- toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  dplyr::filter(time=="3_hours") %>% 
  pivot_wider(., id_cols=c(ENTREZID,SYMBOL), names_from = id, values_from = logFC) %>% 
   dplyr::select(!TRZ) %>% 
  dplyr::rename(DOX_3_RNA=DOX, DNR_3_RNA=DNR,EPI_3_RNA=EPI,MTX_3_RNA=MTX)
  

hr24_RNA <- toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  dplyr::filter(time=="24_hours") %>% 
  pivot_wider(., id_cols=c(ENTREZID,SYMBOL), names_from = id, values_from = logFC) %>% 
   dplyr::select(!TRZ) %>% 
  dplyr::rename(DOX_24_RNA=DOX, DNR_24_RNA=DNR,EPI_24_RNA=EPI,MTX_24_RNA=MTX)

RNA_LFC_df <- hr3_RNA %>% 
  left_join(., hr24_RNA, by=c("SYMBOL"="SYMBOL","ENTREZID"="ENTREZID")) 
```

```{r}
All_data_overlaps <- Overlap_regions %>% 
  left_join(., (final_peaks %>% 
              dplyr::select (Peakid,NCBI_gene:dist_to_NG)), 
            by=c("Peakid"= "Peakid")) %>% 
  # mutate(NCBI_gene = gsub("[:,]", ";", NCBI_gene),
  #        SYMBOL = gsub("[:,]", ";", SYMBOL)) %>%
  # separate_longer_delim(NCBI_gene, delim = ";") %>%
  # separate_longer_delim(SYMBOL, delim = ";") %>% 
  left_join(.,ATAC_LFC_df,by=c("Peakid"="peak")) %>% 
  left_join(.,K27_LFC_df, by=c("Geneid"="genes")) %>%
  left_join(., RNA_LFC_df, by = c("SYMBOL"="SYMBOL", "NCBI_gene"="ENTREZID"))

Only_2kb_ATAC_K27_RNA <- All_data_overlaps %>% 
  dplyr::filter(dist_to_NG > -2000 & dist_to_NG < 2000)


All_data_mat <- All_data_overlaps %>% 
  tidyr::unite(name, Peakid:dist_to_NG, sep="_") %>%
  column_to_rownames(., "name") %>%
  as.matrix()

All_data_2kb_mat <- Only_2kb_ATAC_K27_RNA %>% 
    tidyr::unite(name, Peakid:dist_to_NG, sep="_") %>%
  column_to_rownames(., "name") %>%
  as.matrix()

  

```
Looking at correlations of all overlaps, irrespective of distance of region from expressed gene
```{r}
pearson_cor_mat_all <- cor(All_data_mat,method = "pearson", use = "pairwise.complete.obs")

## do spearman correlation between matched observation of RNA and ATAC
spearman_cor_mat_all <- cor(All_data_mat,method = "spearman", use = "pairwise.complete.obs")
### make correlation heatmaps of both sets

ComplexHeatmap::Heatmap(pearson_cor_mat_all, 
                        column_title = "Pearson RNA/ATAC/H3K27ac LFC correlation")

ComplexHeatmap::Heatmap(spearman_cor_mat_all,
                        column_title = "Spearman RNA/ATAC/H3K27ac LFC correlation")

```

```{r just 2kb correlation}

pearson_cor_mat_2kb <- cor(All_data_2kb_mat,method = "pearson", use = "pairwise.complete.obs")

## do spearman correlation between matched observation of RNA and ATAC
spearman_cor_mat_2kb <- cor(All_data_2kb_mat,method = "spearman", use = "pairwise.complete.obs")
### make correlation heatmaps of both sets

ComplexHeatmap::Heatmap(pearson_cor_mat_2kb, 
                        column_title = "Pearson RNA/ATAC/H3K27ac LFC correlation using +/- 2 kb from TSS ")

ComplexHeatmap::Heatmap(spearman_cor_mat_2kb,
                        column_title = "Spearman RNA/ATAC/H3K27ac LFC correlation using +/- 2 kb from TSS ")

```

Looking at correlation of median LFC between H3K27ac and ATAC shared regions
```{r loading median dataframes}

H3K27_med_3 <- read_csv("data/Final_four_data/re_analysis/median_3_lfc_H3K27ac_norm.csv") %>% 
  dplyr::select(H3K27ac_peak,med_Kac_3h_lfc)
H3K27_med_24 <- read_csv("data/Final_four_data/re_analysis/median_24_lfc_H3K27ac_norm.csv")%>% 
  dplyr::select(H3K27ac_peak,med_Kac_24h_lfc)
ATAC_med_3 <- read_csv("data/Final_four_data/re_analysis/median_3_lfc_norm.csv")%>% 
  dplyr::select(peak,med_3h_lfc)
ATAC_med_24 <- read_csv("data/Final_four_data/re_analysis/median_24_lfc_norm.csv")%>% 
  dplyr::select(peak,med_24h_lfc)
RNA_median_3 <- readRDS("data/other_papers/RNA_median_3_lfc.RDS") %>% 
  dplyr::select(RNA_3h_lfc,ENTREZID)
RNA_median_24 <- readRDS("data/other_papers/RNA_median_24_lfc.RDS") %>% 
  dplyr::select(RNA_24h_lfc,ENTREZID)



```

```{r}
Median_df_2kb <- Only_2kb_ATAC_K27_RNA %>% 
  dplyr::select(Peakid, Geneid,NCBI_gene) %>% 
  mutate(NCBI_gene = gsub("[:,]", ";", NCBI_gene)) %>% 
  separate_longer_delim(NCBI_gene, delim = ";") %>% 
  distinct() %>% 
  left_join(H3K27_med_3,by = c("Geneid"="H3K27ac_peak")) %>% 
  left_join(H3K27_med_24,by = c("Geneid"="H3K27ac_peak")) %>% 
  left_join(ATAC_med_3,by = c("Peakid"="peak")) %>% 
  left_join(ATAC_med_24,by = c("Peakid"="peak")) %>%
  left_join(RNA_median_3, by = c("NCBI_gene"="ENTREZID")) %>% 
  left_join(RNA_median_24, by = c("NCBI_gene"="ENTREZID")) 
 
  
```

```{r ATAC, H3K27ac}

Median_df_2kb %>% 
  ggplot(., aes(y=med_Kac_3h_lfc, x=med_3h_lfc))+
  ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("Correlation of 2kb ATAC regions and H3K27ac regions 3 hours")+
  xlab("ATAC peak med LFC")+
   ylab("H3K27ac med LFC")

Median_df_2kb %>% 
  ggplot(., aes(y=med_Kac_24h_lfc, x=med_24h_lfc))+
   ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("Correlation of 2kb ATAC regions and H3K27ac regions 24 hours")+
  xlab("ATAC peak med LFC")+
   ylab("H3K27ac med LFC")


```
```{r  RNA ATAC correlation}
Median_df_2kb %>% 
  ggplot(., aes(y=RNA_3h_lfc, x=med_3h_lfc))+
   ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("Correlation of 2kb ATAC regions and RNA expressed genes 3 hours")+
  xlab("ATAC peak med LFC")+
   ylab("RNA med LFC")

Median_df_2kb %>% 
  ggplot(., aes(y=RNA_24h_lfc, x=med_24h_lfc))+
  ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("Correlation of 2kb ATAC regions and RNA expressed genes 24 hours")+
  xlab("ATAC peak med LFC")+
   ylab("RNA med LFC")
```

```{r}

no_H3K27ac_overlap <-   final_peaks %>%
  dplyr::filter(!Peakid %in% Overlap_regions$Peakid) %>% 
  dplyr::select (Peakid,NCBI_gene:dist_to_NG) %>% 
left_join(ATAC_med_3,by = c("Peakid"="peak")) %>% 
  left_join(ATAC_med_24,by = c("Peakid"="peak")) %>%
  left_join(RNA_median_3, by = c("NCBI_gene"="ENTREZID")) %>% 
  left_join(RNA_median_24, by = c("NCBI_gene"="ENTREZID")) %>% 
  dplyr::filter(dist_to_NG > -2000 & dist_to_NG < 2000)

no_H3K27ac_overlap %>% 
ggplot(., aes(y=RNA_3h_lfc, x=med_3h_lfc))+
  ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("3 hour 2kb ATAC & RNA expressed, no H3K27ac overlap")+
  xlab("ATAC peak med LFC")+
   ylab("RNA med LFC")


no_H3K27ac_overlap %>% 
ggplot(., aes(y=RNA_24h_lfc, x=med_24h_lfc))+
  ggrastr::geom_point_rast()+
   sm_statCorr(corr_method = 'pearson')+
   ggtitle("24 hour 2kb ATAC & RNA expressed, no H3K27ac overlap")+
  xlab("ATAC peak med LFC")+
   ylab("RNA med LFC")

```

```{r}

```

