---
title: "H3K27ac_cormotif"
author: "Renee Matthews"
date: "2025-05-09"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library(rtracklayer)
library(edgeR)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(eulerr)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(ComplexHeatmap)
library(smplot2)
library(stringr)
library(cowplot)
```

### Loading raw counts for 23 samples

Filtered out matrix from the [previous QC](https://mward-lab.github.io/Matthews_cardiotox_ATAC_2025/H3K27ac_initial_QC.html) page.
```{r}
final_23_mat <- readRDS("data/Final_four_data/re_analysis/H3K27ac_final_23_raw_counts_noM.RDS")
```

Filtering check
```{r filtering out low counts 23}
lcpm_f <- cpm(final_23_mat, log= TRUE)
  ### for determining the basic cutoffs
filt_final_raw_counts <- final_23_mat[rowMeans(lcpm_f)> 0,]
dim(filt_final_raw_counts)

```

#### Custom Cormotif script
```{r echo=TRUE, file='code/corMotifcustom.R'}

```
#### Making the dge cpm-TMM object and annotation matrix
```{r}

annotation_mat <- data.frame(timeset=colnames(filt_final_raw_counts)) %>%
  mutate(sample = timeset) %>% 
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>% 
  mutate(time = factor(time, levels = c("3", "24"))) %>% 
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) %>% 
  mutate(indv=factor(indv, levels = c("A","B","C","D"))) %>% 
  mutate(trt_time=paste0(trt,"_",time))

groupset <- colnames(filt_final_raw_counts)
split_parts <- strsplit(groupset, "_")
group <- sapply(split_parts, function(x) paste(x[2], x[3], sep = "_"))
indv <- sapply(split_parts, function(x) paste(x[1]))

group <- factor(group, levels=c("DNR_24","DNR_3","DOX_24","DOX_3","EPI_24","EPI_3","MTX_24","MTX_3","VEH_24","VEH_3"))

dge <-  DGEList.data.frame(counts = filt_final_raw_counts, group = group, genes = row.names(filt_final_raw_counts))
dge <- calcNormFactors(dge)
dge$samples

```
Checking that I have 23 columns and the normalization factors.


#### Setting up cormotif compid

```{r Initial cormotif data}
group_fac <- group
groupid <- as.numeric(group_fac)
### order of samples
# DNR_24 DNR_3  DOX_24 EPI_24 EPI_3  MTX_24 MTX_3  VEH_24 DNR_24 DNR_3  DOX_3  EPI_24 EPI_3  MTX_24
# VEH_3  DNR_24 DNR_3  DOX_24 DOX_3  MTX_24 MTX_3  VEH_24 VEH_3 
#   1  2  3  5  6  7  8  9  1  2  4  5  6  7 10  1  2  3  4  7  8  9 10

compid <- data.frame(c1= c(2,4,6,8,1,3,5,7), c2 = c( 10,10,10,10,9,9,9,9))
compid
y_TMM_cpm_ac <- cpm(dge, log = TRUE)

```
#### Running Cormotif
```{r Cormotif run, eval=FALSE}
set.seed(31415)
cormotif_initial_ac <- cormotiffit(exprs = y_TMM_cpm_ac, groupid = groupid, compid = compid, K=1:6, max.iter = 500, runtype = "logCPM")

saveRDS(cormotif_initial_ac, "data/Final_four_data/re_analysis/cormotif_23sample_initial_noM.RDS")

```

```{r}
cormotif_initial_ac <- readRDS("data/Final_four_data/re_analysis/cormotif_23sample_initial_noM.RDS")
plotIC(cormotif_initial_ac)
plotMotif(cormotif_initial_ac)

```

```{r Cluster assingments}
motif_prob <- cormotif_initial_ac$bestmotif$clustlike

row.names(motif_prob) <- row.names(y_TMM_cpm_ac)

group1 <- motif_prob %>% 
  as.data.frame() %>% 
  dplyr::filter(V1>0.5 & V2<0.5 & V3 <0.5& V4<0.5) %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::select(Peakid) %>% 
  separate(Peakid, into=c("chr","start","end"),remove = FALSE)
  
  
group2 <- motif_prob %>% 
  as.data.frame() %>% 
  dplyr::filter(V1<0.5 & V2>0.5 & V3 <0.5& V4<0.5) %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::select(Peakid) %>% 
  separate(Peakid, into=c("chr","start","end"),remove = FALSE)
  
  
  group3 <- motif_prob %>% 
  as.data.frame() %>% 
  dplyr::filter(V1<0.5 & V2<0.5 & V3 >0.5& V4<0.5) %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::select(Peakid) %>% 
  separate(Peakid, into=c("chr","start","end"),remove = FALSE)
  
  
  
  group4 <- motif_prob %>% 
  as.data.frame() %>% 
  dplyr::filter(V1<0.5 & V2<0.5 & V3 <0.5& V4>0.5) %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::select(Peakid) %>% 
  separate(Peakid, into=c("chr","start","end"),remove = FALSE)


```

Number of regions in group 1 (no-response)`r length(group1$Peakid)`

Number of regions in group 2 (early acute response)`r length(group2$Peakid)`

Number of regions in group 1 (late response)`r length(group3$Peakid)`

Number of regions in group 1 (early-sustained)`r length(group4$Peakid)`

```{r sampling}
set.seed(31415)

peaks1 <- group1 %>% 
  slice_sample(n=3) %>% 
  dplyr::select(Peakid)

peaks2 <- group2 %>% 
  slice_sample(n=3) %>% 
  dplyr::select(Peakid)

peaks3 <- group3 %>% 
  slice_sample(n=3) %>% 
  dplyr::select(Peakid)

peaks4 <- group4 %>% 
  slice_sample(n=3) %>% 
  dplyr::select(Peakid)


```

```{r}
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#41B333")


example_boxplots <- function(peaks_df){
  df_name <- deparse(substitute(peaks_df))
y_TMM_cpm_ac %>%
  as.data.frame() %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::filter(Peakid %in% peaks_df$Peakid) %>% 
  pivot_longer(cols=-Peakid, names_to="name", values_to = "log_cpm") %>% 
  separate_wider_delim(cols=name,delim="_",names=c("indv","trt","time")) %>% 
  mutate(trt=factor(trt,levels=c("DOX","EPI","DNR","MTX","VEH")),
         time=factor(time, levels=c("3","24"),labels=c("3 hours","24 hours"))) %>% 
  ggplot(., aes(x=time, y=log_cpm))+
  geom_boxplot(aes(fill=trt))+
   theme_bw()+
  facet_wrap(~Peakid,nrow = 3, ncol = 6 )+
 scale_fill_manual(values=drug_pal)+
  theme(strip.text = element_text(face = "bold",  hjust = 0, size = 8),
        strip.background = element_rect(fill = "white", linetype = "solid",
                                        color = "black", linewidth = 1),
        panel.spacing = unit(1, 'points'))+
  ggtitle(df_name)
}


```

```{r}
example_boxplots(peaks1)

example_boxplots(peaks2)

example_boxplots(peaks3)

example_boxplots(peaks4)
```

