---
title: "Peak_Calling"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
# library(ggsignif)
# library(cowplot)
# library(ggpubr)
# library(scales)
# library(sjmisc)
library(kableExtra)
# library(broom)
# library(biomaRt)
library(RColorBrewer)
# library(gprofiler2)
# library(qvalue)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(ATACseqQC)
library(rtracklayer)
```

```{r data_loading and other functions}
drug_pal_fact <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene

loadFile_peakCall <- function(){
 file <- choose.files()
 file <- readPeakFile(file, header = FALSE)
 return(file)
}

prepGRangeObj <- function(seek_object){
 seek_object$Peaks = seek_object$V4
 seek_object$level = seek_object$V5
 seek_object$V4 = seek_object$V5 = NULL
 return(seek_object)
}
TSS = getBioRegion(TxDb=txdb, upstream=3000, downstream=3000, by = "gene", 
                   type = "start_site")

# ind4_V24hpeaks <- readRDS("data/ind4_V24hpeaks.RDS")
# ind1_DA24hpeaks <- readRDS("data/ind1_DA24hpeaks.RDS")
# anno_ind4_V24h <- readRDS("data/anno_ind4_V24h.RDS")
# anno_ind1_DA24h <- readRDS("data/anno_ind1_DA24h.RDS")


Ind1_summary  <- read.csv("data/Ind1_summary.txt", row.names = 1) %>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind2_summary  <- read.csv("data/Ind2_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind3_summary  <- read.csv("data/Ind3_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind4_summary  <- read.csv("data/Ind4_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind5_summary  <- read.csv("data/Ind5_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind6_summary  <- read.csv("data/Ind6_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
```

This specific page so far contains the QC analysis after calling peaks using MACS2.

Primary scripts used for ATAC data preprocesing will be linked here in the future:

-    Currently the steps were are as follows:

    -   Basic Fastqc followed by adapter trimming and Fastqc analysis on the leftover fragments.

    -   Trimmed reads were aligned to the hg38 human genome.

    -   Mitochondrial reads (chrM) were removed

    -   samtools was used to removed non-paired, discordantly paired, and multi-mapped reads from the .bam.

    -   Markduplicates function from Picard was used to mark optical and PCR duplicates, with samtools used to remove these reads using the flag -F 1024.

    -   MACS2 was used to call peaks, with QC of the peak files below.
    
Initial read summary is found [at this LINK](https://reneeisnowhere.github.io/ATAC_learning/Fastqc_results.html)




```{r Readssummary1, eval=FALSE, include=FALSE}
#  library(readr) pulling in orginal files example code
#
# Ind1_summary <- read_delim("~/ATAC_downloads/Ind1/trimmed/Ind1_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind2_summary <- read_delim("~/ATAC_downloads/Ind2/trimmed/Ind2_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind3_summary <- read_delim("~/ATAC_downloads/Ind3/trimmed/Ind3_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind4_summary <- read_delim("~/ATAC_downloads/Ind4/trimmed/Ind4_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind5_summary <- read_delim("~/ATAC_downloads/Ind5/trimmed/Ind5_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind6_summary <- read_delim("~/ATAC_downloads/Ind6/trimmed/Ind6_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# write.csv(Ind6_summary, "data/Ind6_summary.txt")
Ind1_reads_summary <- Ind1_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind1_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 1") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

Ind1_reads_summary %>% 
  pivot_longer(cols = total_reads:dedup_read_pairs, names_to="type", values_to = "reads") %>% 
  dplyr::filter(type %in% list("total_reads","total_mapped_reads","nuclear_mapped_reads", "unique_mapped_reads","dedup_reads")) %>% 
  mutate(type=factor(type, levels=c("total_reads", "total_mapped_reads", "nuclear_mapped_reads","unique_mapped_reads","dedup_reads"))) %>% 
  mutate(trt=gsub("[[:digit:]]", "",sample)) %>% 
  # mutate(trt=substr(trt,-1,2))
  mutate(time = if_else(grepl("24h$", sample) ==TRUE, "24_hours","3_hours")) %>% 
   mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>% 
  mutate(trt = case_match(trt,"DAh"~"DNR","DXh"~"DOX","Eh"~"EPI", "Mh" ~ "MTX", "Th" ~ "TRZ", "Vh" ~"VEH",.default = trt)) %>% 
  ggplot(., aes (x=type, y=reads, group = time)) +
  geom_col(position="dodge",aes(fill=time))+
  facet_wrap(~trt)+
  theme(axis.text.x=element_text(angle=90))+
  ggtitle("Ind 1")
  
```

### Individual 1 fragment files:

```{r fragfiles1}

Ind1_frag_files <- read.csv("data/Ind1_fragment_files.txt", row.names = 1)
Ind1_firstfrag_files <- read.csv("data/Ind1_firstfragment_files.txt", row.names = 1)
Ind1_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)+
  coord_cartesian(ylim=c(0,300000))

Ind1_firstfrag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=(counts), x=(frag_size), group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)+
  coord_cartesian(xlim=c(0,1000))
# 

Ind1_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=(counts), x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)#+
  # coord_cartesian(ylim=c(0,300000))



Ind1_firstfrag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=(counts), x=(frag_size), group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)+
  coord_cartesian(xlim=c(0,1000))
# 
```

### Individual 2 fragment files:

```{r fragfiles2}

Ind2_frag_files <- read.csv("data/Ind2_fragment_files.txt", row.names = 1)
Ind2_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 2\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind2_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 2\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```

### Individual 3 fragment files:

```{r fragfiles3}

Ind3_frag_files <- read.csv("data/Ind3_fragment_files.txt", row.names = 1)
Ind3_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 3\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind3_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 3\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```


### Individual 4 fragment files:

```{r fragfiles visualize}

Ind4_frag_files <- read.csv("data/Ind4_fragment_files.txt", row.names = 1)
Ind4_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt ))+
  ggtitle("Individual 4\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind4_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt ))+
  ggtitle("Individual 4\n24 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)


```

### Individual 5 fragment files:

```{r fragfiles5}

Ind5_frag_files <- read.csv("data/Ind5_fragment_files.txt", row.names = 1)
Ind5_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 5\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind5_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 5\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```


### Individual 6 fragment files:

```{r fragfiles6}

Ind6_frag_files <- read.csv("data/Ind6_fragment_files.txt", row.names = 1)
Ind6_frag_files %>% 
  dplyr::filter(time =="3h") %>%
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 6\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind6_frag_files %>% 
  dplyr::filter(time =="24h") %>%
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 6\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```


### Peak data


```{r peak info}
##collecting summary files

# Ind1_peaksummary <- read_table("~/ATAC_downloads/Ind1/trimmed/macs_output/Ind1_peaksummary.txt",
#     col_names = FALSE) %>%
#   rename(X1 ="counts", X2= "sample")
# Ind2_peaksummary <- read_table("~/ATAC_downloads/Ind2/trimmed/macs_output/Ind2_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind3_peaksummary <- read_table("~/ATAC_downloads/Ind3/trimmed/macs_output/Ind3_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind4_peaksummary <- read_table("~/ATAC_downloads/Ind4/trimmed/macs_output/Ind4_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind5_peaksummary <- read_table("~/ATAC_downloads/Ind5/trimmed/macs_output/Ind5_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind6_peaksummary <- read_table("~/ATAC_downloads/Ind6/trimmed/macs_output/Ind6_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Peaksummary <- rbind(Ind1_peaksummary,Ind2_peaksummary,Ind3_peaksummary,Ind4_peaksummary,Ind5_peaksummary,Ind6_peaksummary)
# # 
# write.csv(Peaksummary, "data/first_Peaksummarycounts.csv")
Peaksummary <- read.csv("data/first_Peaksummarycounts.csv",row.names=1)
Peaksummary %>% 
  dplyr::filter(sample != "total") %>% 
   separate(sample, into=c(NA,"indv","sample",NA,NA,NA)) %>% 
  mutate(trt=gsub("[[:digit:]]", "",sample)) %>% 
  # mutate(trt=substr(trt,-1,2))
  mutate(time = if_else(grepl("24h$", sample) ==TRUE, "24_hours","3_hours")) %>% 
  mutate(trt = case_match(trt,"DAh"~"DNR","DXh"~"DOX","Eh"~"EPI", "Mh" ~ "MTX", "Th" ~ "TRZ", "Vh" ~"VEH",.default = trt)) %>% 
  mutate(indv = factor(indv, levels = c("Ind1", "Ind2", "Ind3", "Ind4", "Ind5", "Ind6"))) %>%
  mutate(time = factor(time, levels = c("3_hours", "24_hours"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels =  c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH")))%>% 
  ggplot(., aes(x =trt, y=counts,group=trt))+
  geom_boxplot(aes(fill= trt))+
  geom_point(aes(col=indv, size =3))+
  facet_wrap(~time)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("Peak counts by treatment")+
  theme_bw()



```


### Ind1 Peaks

```{r Ind1 inital TSS setup}

# plotAnnoBar(anno_ind4_V24h, main = "Genomic Feature Distribution")+ ggtitle("Ind4 VEH 24 hour")
# plotAnnoBar(anno_ind1_DA24h, main = "Genomic Feature Distribution")+ ggtitle("Ind1 DNR 24 hour")

# ind4_V24hpeaks_gr <- prepGRangeObj(ind4_V24hpeaks)
# ind1_DA24hpeaks_gr <- prepGRangeObj((ind1_DA24hpeaks))
# Epi_list <- GRangesList(ind1_DA24hpeaks_gr, ind4_V24hpeaks_gr)
# # ##plotting the TSS average window (making an overlap of each using Epi_list as list holder)
# Epi_list_tagMatrix = lapply(Epi_list, getTagMatrix, windows = TSS)
# plotAvgProf(Epi_list_tagMatrix, xlim=c(-3000, 3000), ylab = "Count Frequency")
#plotPeakProf(Epi_list_tagMatrix, facet = "none", conf = 0.95)

## What I did here:  I called all my narrowpeak files
# peakfiles1 <- choose.files()

##these were practice for getting file names and shortening for the for loop below
# testname <- basename(peakfiles1[1])
# str_split_i(testname, "_",3)

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind1_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles1[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind1_peaks[[banana_peel]] <- readPeakFile(peakfiles1[file])
# }
# saveRDS(Ind1_peaks, "data/Ind1_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)
# peakAnnoList_1 <- lapply(Ind1_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_1, "data/peakAnnoList_1.RDS")

peakAnnoList_1 <- readRDS("data/peakAnnoList_1.RDS")
plotAnnoBar(peakAnnoList_1, main = "Genomic Feature Distribution")


# saveRDS(Epi_list_tagMatrix, "data/Ind1_TSS_peaks.RDS")

Ind1_TSS_peaks_plot <- readRDS("data/Ind1_TSS_peaks.RDS")

# Epi_list_tagMatrix = lapply(Ind1_peaks, getTagMatrix, windows = TSS)

plotAvgProf(Ind1_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 1" )

plotAvgProf(Ind1_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 1" )

```


### Ind2 Peaks

```{r Ind2 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles2 <- choose.files()

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind2_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles2[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind2_peaks[[banana_peel]] <- readPeakFile(peakfiles2[file])
# }
# saveRDS(Ind2_peaks, "data/Ind2_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind2_peaks <- readRDS("data/Ind2_peaks_list.RDS")
# peakAnnoList_2 <- lapply(Ind2_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_2, "data/peakAnnoList_2.RDS")

peakAnnoList_2 <- readRDS("data/peakAnnoList_2.RDS")
plotAnnoBar(peakAnnoList_2, main = "Genomic Feature Distribution, Individual 2")

# Epi_list_tagMatrix = lapply(Ind2_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind2_TSS_peaks.RDS")

Ind2_TSS_peaks_plot <- readRDS("data/Ind2_TSS_peaks.RDS")



plotAvgProf(Ind2_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 2" )

plotAvgProf(Ind2_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 2" )

```


### Ind3 Peaks

```{r Ind3 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles3 <- choose.files()

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind3_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles3[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind3_peaks[[banana_peel]] <- readPeakFile(peakfiles3[file])
# }
# saveRDS(Ind3_peaks, "data/Ind3_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind3_peaks <- readRDS("data/Ind3_peaks_list.RDS")
# peakAnnoList_3 <- lapply(Ind3_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_3, "data/peakAnnoList_3.RDS")

peakAnnoList_3 <- readRDS("data/peakAnnoList_3.RDS")
plotAnnoBar(peakAnnoList_3, main = "Genomic Feature Distribution, Individual 3")

# Epi_list_tagMatrix = lapply(Ind3_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind3_TSS_peaks.RDS")

Ind3_TSS_peaks_plot <- readRDS("data/Ind3_TSS_peaks.RDS")



plotAvgProf(Ind3_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 3" )

plotAvgProf(Ind3_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 3" )

```


### Ind4 Peaks

```{r Ind4 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles4 <- choose.files()
# 
# ##This loop first established a list then (because I already knew the list had 12 files)
# ## I then imported each of these onto that list.  Once I had the list, I stored it as
# ## an R object, 
# Ind4_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles4[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind4_peaks[[banana_peel]] <- readPeakFile(peakfiles4[file])
# }
# saveRDS(Ind4_peaks, "data/Ind4_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind4_peaks <- readRDS("data/Ind4_peaks_list.RDS")
# peakAnnoList_4 <- lapply(Ind4_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_4, "data/peakAnnoList_4.RDS")

peakAnnoList_4 <- readRDS("data/peakAnnoList_4.RDS")
plotAnnoBar(peakAnnoList_4, main = "Genomic Feature Distribution, Individual 4")

# Epi_list_tagMatrix = lapply(Ind4_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind4_TSS_peaks.RDS")

Ind4_TSS_peaks_plot <- readRDS("data/Ind4_TSS_peaks.RDS")



plotAvgProf(Ind4_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 4" )

plotAvgProf(Ind4_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 4" )

```

### Ind5 Peaks
```{r Ind5 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles4 <- choose.files()
# # 
# # ##This loop first established a list then (because I already knew the list had 12 files)
# # ## I then imported each of these onto that list.  Once I had the list, I stored it as
# ## an R object,
# Ind4_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles4[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind4_peaks[[banana_peel]] <- readPeakFile(peakfiles4[file])
# }
# saveRDS(Ind4_peaks, "data/Ind4_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind5_peaks <- readRDS("data/Ind5_peaks_list.RDS")
# peakAnnoList_5 <- lapply(Ind5_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_5, "data/peakAnnoList_5.RDS")

peakAnnoList_5 <- readRDS("data/peakAnnoList_5.RDS")
plotAnnoBar(peakAnnoList_5, main = "Genomic Feature Distribution, Individual 4")

# Epi_list_tagMatrix = lapply(Ind5_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind5_TSS_peaks.RDS")

Ind5_TSS_peaks_plot <- readRDS("data/Ind5_TSS_peaks.RDS")



plotAvgProf(Ind5_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 5" )

plotAvgProf(Ind5_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 5" )

```



### Ind6 Peaks

```{r Ind6 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles6 <- choose.files()
# 
# ##This loop first established a list then (because I already knew the list had 12 files)
# ## I then imported each of these onto that list.  Once I had the list, I stored it as
# ## an R object, 
# Ind6_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles6[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind6_peaks[[banana_peel]] <- readPeakFile(peakfiles6[file])
# }
# saveRDS(Ind6_peaks, "data/Ind6_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind6_peaks <- readRDS("data/Ind6_peaks_list.RDS")
# peakAnnoList_6 <- lapply(Ind6_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_6, "data/peakAnnoList_6.RDS")

peakAnnoList_6 <- readRDS("data/peakAnnoList_6.RDS")
plotAnnoBar(peakAnnoList_6, main = "Genomic Feature Distribution, Individual 6")+ggtitle ("Genomic Feature Distribution, Individual 6")
##Epi_list_tagMatrix title was just because I was too lazy to change the name
# Epi_list_tagMatrix = lapply(Ind6_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind6_TSS_peaks.RDS")

Ind6_TSS_peaks_plot <- readRDS("data/Ind6_TSS_peaks.RDS")



plotAvgProf(Ind6_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 6" )

plotAvgProf(Ind6_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 6" )+ coord_cartesian(xlim = c(-1000, 100))

```


```{r bamqc, eval=FALSE, include=FALSE}

bamfile <- choose.files()
bamfile.labels <- gsub(".bam", "", basename(bamfile))
estimateLibComplexity(readsDupFreq(bamfile))

fragSize <- fragSizeDist(bamfile, bamfile.labels)
```
```{r eval=FALSE}
possibleTag <- list("integer"=c("AM", "AS", "CM", "CP", "FI", "H0", "H1", "H2", 
                                "HI", "IH", "MQ", "NH", "NM", "OP", "PQ", "SM",
                                "TC", "UQ"), 
                 "character"=c("BC", "BQ", "BZ", "CB", "CC", "CO", "CQ", "CR",
                               "CS", "CT", "CY", "E2", "FS", "LB", "MC", "MD",
                               "MI", "OA", "OC", "OQ", "OX", "PG", "PT", "PU",
                               "Q2", "QT", "QX", "R2", "RG", "RX", "SA", "TS",
                               "U2"))
library(Rsamtools)
bamTop100 <- scanBam(BamFile(bamfile, yieldSize = 100),
                     param = ScanBamParam(tag=unlist(possibleTag)))[[1]]$tag
tags <- names(bamTop100)[lengths(bamTop100)>0]
tags

outPath <- "splited"
dir.create(outPath)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
seqlev <- "chr1" 
seqinformation <- seqinfo(TxDb.Hsapiens.UCSC.hg38.knownGene)


which <- as(seqinformation[seqlev], "GRanges")
gal <- readBamFile(bamfile, tag=tags, which=which, asMates=TRUE, bigFile=TRUE)
shiftedBamfile <- file.path(outPath, "shifted.bam")
gal1 <- shiftGAlignmentsList(gal, outbam=shiftedBamfile)

txs <- transcripts(TxDb.Hsapiens.UCSC.hg38.knownGene)
tsse <- TSSEscore(gal1, txs)
tsse$TSSEscore
summary(tsse$values)
```



```{r bedfile annotation, fig.height=8, fig.width=12}
### bring in the Feature counted files
# Ind1_counts <- read.delim("~/ATAC_downloads/Ind1_files.txt", comment.char="#")
# Ind2_counts <- read.delim("~/ATAC_downloads/Ind2_files.txt", comment.char="#")
# Ind3_counts <- read.delim("~/ATAC_downloads/Ind3_files.txt", comment.char="#")
# Ind4_counts <- read.delim("~/ATAC_downloads/Ind4_files.txt", comment.char="#")
# Ind5_counts <- read.delim("~/ATAC_downloads/Ind5_files.txt", comment.char="#")
# Ind6_counts <- read.delim("~/ATAC_downloads/Ind6_files.txt", comment.char="#")
# 
# first_run_frag_counts <- Ind1_counts %>% 
#   full_join(Ind2_counts) %>% 
# full_join(Ind3_counts) %>% 
# full_join(Ind4_counts) %>% 
# full_join(Ind5_counts) %>% 
# full_join(Ind6_counts) 
# 
# names(first_run_frag_counts) = gsub(pattern = "_S.*", replacement = "", x = names(first_run_frag_counts))
# 
# names(first_run_frag_counts)=gsub(pattern = "^ind6.trimmed.filt_files.trimmed_", replacement = "", x = names(first_run_frag_counts))
# 
# write.csv(first_run_frag_counts,"data/first_run_frag_counts.txt")
first_run_frag_counts <- read.csv("data/first_run_frag_counts.txt", row.names = 1) 

Frag_cor <- first_run_frag_counts %>% 
  dplyr::select(Ind1_75DA24h:Ind6_71V3h) %>% 
  cor()
  
# pheatmap::pheatmap(Frag_cor , cluster_rows = TRUE, cluster_cols = TRUE)



filmat_groupmat_col <- data.frame(timeset = colnames(Frag_cor))

counts_corr_mat <-filmat_groupmat_col %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>% 
  mutate(timeset=gsub("87","2_",timeset)) %>% 
  mutate(timeset=gsub("77","3_",timeset)) %>% 
  mutate(timeset=gsub("79","4_",timeset)) %>% 
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>% 
  mutate(timeset = gsub("24h","_24h",timeset), 
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(class = if_else(trt == "DNR", "AC", if_else(
    trt == "DOX", "AC", if_else(trt == "EPI", "AC", "nAC")
  ))) %>%
  mutate(TOP2i = if_else(trt == "DNR", "yes", if_else(
    trt == "DOX", "yes", if_else(trt == "EPI", "yes", if_else(trt == "MTX", "yes", "no"))
  ))) 
                         
 mat_colors <- list( 
   trt= c("#F1B72B","#8B006D","#DF707E","#3386DD","#707031","#41B333"),
   indv=c("#1B9E77", "#D95F02" ,"#7570B3", "#E7298A" ,"#66A61E", "#E6AB02"),
   time=c("pink", "chocolate4"),
   class=c("yellow1","darkorange1"), 
   TOP2i =c("darkgreen","lightgreen"))                        
                         
names(mat_colors$trt)   <- unique(counts_corr_mat$trt)                      
names(mat_colors$indv) <- unique(counts_corr_mat$indv)
names(mat_colors$time) <- unique(counts_corr_mat$time)
names(mat_colors$class) <- unique(counts_corr_mat$class)
names(mat_colors$TOP2i) <- unique(counts_corr_mat$TOP2i)


ComplexHeatmap::pheatmap(Frag_cor,
                         # column_title=(paste0("RNA-seq log"[2]~"cpm correlation")),
        annotation_col = counts_corr_mat,
        annotation_colors = mat_colors,
        heatmap_legend_param = mat_colors,
        fontsize=10,
        fontsize_row = 8,
        angle_col="90",
        treeheight_row=25,
        fontsize_col = 8,
        treeheight_col = 20)


```

