---
title: "Peak_Calling"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
# library(ggsignif)
# library(cowplot)
# library(ggpubr)
# library(scales)
# library(sjmisc)
library(kableExtra)
# library(broom)
# library(biomaRt)
library(RColorBrewer)
# library(gprofiler2)
# library(qvalue)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
```

```{r data_loading and other functions}
drug_pal_fact <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene

loadFile_peakCall <- function(){
 file <- choose.files()
 file <- readPeakFile(file, header = FALSE)
 return(file)
}

prepGRangeObj <- function(seek_object){
 seek_object$Peaks = seek_object$V4
 seek_object$level = seek_object$V5
 seek_object$V4 = seek_object$V5 = NULL
 return(seek_object)
}
TSS = getBioRegion(TxDb=txdb, upstream=3000, downstream=3000, by = "gene", 
                   type = "start_site")

ind4_V24hpeaks <- readRDS("data/ind4_V24hpeaks.RDS")
ind1_DA24hpeaks <- readRDS("data/ind1_DA24hpeaks.RDS")
anno_ind4_V24h <- readRDS("data/anno_ind4_V24h.RDS")
anno_ind1_DA24h <- readRDS("data/anno_ind1_DA24h.RDS")
Ind1_summary  <- read.csv("data/Ind1_summary.txt", row.names = 1) %>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind2_summary  <- read.csv("data/Ind2_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind3_summary  <- read.csv("data/Ind3_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind4_summary  <- read.csv("data/Ind4_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind5_summary  <- read.csv("data/Ind5_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
Ind6_summary  <- read.csv("data/Ind6_summary.txt", row.names = 1)%>% 
  rename(X1="sample",X2="reads",X3="mapped")
```

This specific page so far contains the QC analysis after calling peaks using MACS2.

Primary scripts used for ATAC data preprocesing will be linked here in the future:

-    Currently the steps were are as follows:

    -   Basic Fastqc followed by adapter trimming and Fastqc analysis on the leftover fragments.

    -   Trimmed reads were aligned to the hg38 human genome.

    -   Mitochondrial reads (chrM) were removed

    -   samtools was used to removed non-paired, discordantly paired, and multi-mapped reads from the .bam.

    -   Markduplicates function from Picard was used to mark optical and PCR duplicates, with samtools used to remove these reads using the flag -F 1024.

    -   MACS2 was used to call peaks, with QC of the peak files below.

Initial summary of reads after each step:

### Individual 1 read summary

```{r Readssummary1}
#  library(readr) pulling in orginal files example code
#
# Ind1_summary <- read_delim("~/ATAC_downloads/Ind1/trimmed/Ind1_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind2_summary <- read_delim("~/ATAC_downloads/Ind2/trimmed/Ind2_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind3_summary <- read_delim("~/ATAC_downloads/Ind3/trimmed/Ind3_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind4_summary <- read_delim("~/ATAC_downloads/Ind4/trimmed/Ind4_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind5_summary <- read_delim("~/ATAC_downloads/Ind5/trimmed/Ind5_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# Ind6_summary <- read_delim("~/ATAC_downloads/Ind6/trimmed/Ind6_summedup.txt", 
#     delim = "\t", escape_double = FALSE, 
#     col_names = FALSE, trim_ws = TRUE)
# write.csv(Ind6_summary, "data/Ind6_summary.txt")
Ind1_reads_summary <- 
Ind1_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind1_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 1") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```

### Individual 2 read summary
```{r Readssummary2}

Ind2_reads_summary <- 
Ind2_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind2_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 2") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```

### Individual 3 read summary
```{r Readssummary3}

Ind3_reads_summary <- 
Ind3_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind3_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 3") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```

### Individual 4 read summary
```{r Readssummary4}

Ind4_reads_summary <- 
Ind4_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind4_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 4") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```
_note: reprocessed reads for Individual 4 vary from previous output.  This is due a file truncation that was detected in the process.  When the files were reprocessed, the truncated bam file was fixed, resulting in a larger number of overall reads.  Yay, I figured it out!_

### Individual 5 read summary
```{r Readssummary5}

Ind5_reads_summary <- 
Ind5_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind5_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 5") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```

### Individual 6 read summary
```{r Readssummary6}

Ind6_reads_summary <- 
Ind6_summary %>%                          
 separate(reads,into=c("reads",NA),sep= " ") %>% 
   mutate(reads=as.numeric(reads)) %>% 
   separate(mapped, into= c("mapped_reads", NA,NA, "percent_mapped_reads",NA)) %>% 
   separate(sample, into=c("one","two",NA, "4","sample",NA,"seven","8")) %>% 
   mutate(mapped_reads=as.numeric(mapped_reads)) %>% 
   mutate(type = if_else(two=="first", "total",
                         if_else(two=="noM","nuclear",
                                 if_else((seven == "fin"& two=="files"), "unique", "dedup"))))%>% 
   dplyr::select(sample,type,  reads, mapped_reads)%>% 
   pivot_longer(cols=reads:mapped_reads, names_to = "read_info", values_to = "reads") %>% 
   unite("type",type:read_info, sep="_") %>% 
   distinct() %>% 
   pivot_wider(id_cols = sample, names_from = "type", values_from = "reads") %>% 
   mutate(per_nuclear_mapped = nuclear_mapped_reads/total_mapped_reads*100) %>% 
  mutate(dedup_read_pairs=dedup_reads/2) %>% 
   dplyr::select(sample,total_reads:nuclear_mapped_reads,per_nuclear_mapped,unique_mapped_reads,dedup_reads,dedup_read_pairs)
 
 # dedup_mapped_reads)
 Ind6_reads_summary %>% 
   kable(., caption= "Reads summary from Ind 6") %>%
  kable_paper("striped", full_width = FALSE) %>%
  kable_styling(full_width = FALSE,font_size = 18) %>%
  scroll_box(width = "100%", height = "400px")

 
```


```{r fragment files list, eval=FALSE, include=FALSE}
### this was used to load fragment files for all individuals for display in the future
safename <- choose.files()
Ind5_78DA3h_frag <- read_delim(safename[1], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE)%>% separate(col=1, into=c("counts","frag_size")) %>% 
  rename(  "counts"="DA_3h_5_counts")


Ind5_78DA24h_frag <- read_delim(safename[2], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="DA_24h_5_counts")


Ind5_78DX3h_frag <- read_delim(safename[3], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="DX_3h_5_counts")


Ind5_78DX24h_frag<- read_delim(safename[4], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="DX_24h_5_counts")


Ind5_78E3h_frag <- read_delim(safename[5], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="E_3h_5_counts")


Ind5_78E24h_frag <- read_delim(safename[6], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="E_24h_5_counts")

Ind5_78M3h_frag <- read_delim(safename[7], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="M_3h_5_counts")


Ind5_78M24h_frag <- read_delim(safename[8], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="M_24h_5_counts")


Ind5_78T3h_frag <- read_delim(safename[9], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="T_3h_5_counts")



Ind5_78T24h_frag <- read_delim(safename[10], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="T_24h_5_counts")



Ind5_78V3h_frag <- read_delim(safename[11], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="V_3h_5_counts")



Ind5_78V24h_frag <- read_delim(safename[12], 
    delim = "\t", escape_double = FALSE, 
    col_names = FALSE, trim_ws = TRUE) %>% separate(col=1, into=c("counts","frag_size"))%>% 
  rename(  "counts"="V_24h_5_counts")
Ind5_frag_files <- Ind5_78V3h_frag %>% 
  left_join(.,Ind5_78V24h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78DA3h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78DA24h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78DX3h_frag, by = "frag_size") %>% 
left_join(.,Ind5_78DX24h_frag, by = "frag_size") %>% 
left_join(.,Ind5_78E3h_frag, by = "frag_size") %>% 
left_join(.,Ind5_78E24h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78M3h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78M24h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78T3h_frag, by = "frag_size") %>% 
  left_join(.,Ind5_78T24h_frag, by = "frag_size") %>% 
  pivot_longer(cols= !frag_size,names_to = "sample",values_to = "counts") %>% 
  separate(sample, into = c("trt","time","indv",NA), sep = "_") %>% 
  mutate(trt = factor(trt, levels = c("DX","E","DA","M","T","V"))) %>% 
  mutate(time = factor(time, levels = c("3h","24h"))) %>% 
  mutate(counts= as.numeric(counts), frag_size= as.numeric(frag_size))
write.csv(Ind5_frag_files,"data/Ind5_fragment_files.txt")

```

### Individual 4 fragment files:

```{r fragfiles visualize}

Ind4_frag_files <- read.csv("data/Ind4_fragment_files.txt", row.names = 1)
Ind4_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt ))+
  ggtitle("Individual 4\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind4_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt ))+
  ggtitle("Individual 4\n24 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)


```

So, fragment lengths are not so great.
Lots of noise.

### Individual 1 fragment files:

```{r fragfiles1}

Ind1_frag_files <- read.csv("data/Ind1_fragment_files.txt", row.names = 1)
Ind1_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)+
  coord_cartesian(ylim=c(0,300000))


Ind1_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 1\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)+
  coord_cartesian(ylim=c(0,300000))
```

### Individual 2 fragment files:

```{r fragfiles2}

Ind2_frag_files <- read.csv("data/Ind2_fragment_files.txt", row.names = 1)
Ind2_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 2\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind2_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 2\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```

### Individual 3 fragment files:

```{r fragfiles3}

Ind3_frag_files <- read.csv("data/Ind3_fragment_files.txt", row.names = 1)
Ind3_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 3\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind3_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 3\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```

### Individual 5 fragment files:

```{r fragfiles5}

Ind5_frag_files <- read.csv("data/Ind5_fragment_files.txt", row.names = 1)
Ind5_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="3h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 5\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind5_frag_files %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  dplyr::filter(time =="24h") %>%
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 5\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```


### Individual 6 fragment files:

```{r fragfiles6}

Ind6_frag_files <- read.csv("data/Ind6_fragment_files.txt", row.names = 1)
Ind6_frag_files %>% 
  dplyr::filter(time =="3h") %>%
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  # geom_line(aes(col=trt, alpha = 0.5, linewidth=1 ))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 6\n3 hour fragment sizes")+
  theme_classic()+
   facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
Ind6_frag_files %>% 
  dplyr::filter(time =="24h") %>%
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes(y=counts, x=frag_size, group=trt))+
  geom_line(aes(col=trt))+
  ggtitle("Individual 6\n24 hour fragment sizes")+
  theme_classic()+
  facet_wrap(~trt)+
  scale_color_manual(values=drug_pal_fact)
```


```{r readsummary 1}
total_reads_summary <- Ind1_reads_summary %>% 
 mutate(sample=gsub("75","1_",sample)) %>% 
  rbind((Ind2_reads_summary %>%
           mutate(sample=gsub("87","2_",sample)))) %>% 
  rbind((Ind3_reads_summary %>%
           mutate(sample=gsub("77","3_",sample)))) %>% 
  rbind((Ind4_reads_summary %>%
           mutate(sample=gsub("79","4_",sample)))) %>% 
  rbind((Ind5_reads_summary %>%
           mutate(sample=gsub("78","5_",sample)))) %>% 
  rbind((Ind6_reads_summary %>%
           mutate(sample=gsub("71","6_",sample)))) %>% 
  mutate(sample = gsub("24h","_24h",sample), 
       sample = gsub("3h","_3h",sample)) %>%
  separate(sample, into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels=c("DX","E","DA","M","T","V"), labels = c("DOX","EPI","DNR","MTX","TRZ","VEH")))
         
total_reads_summary %>% 
  ggplot(., aes(x=trt, y=total_reads ))+
  geom_boxplot(aes(fill=trt))+
  geom_point(aes(col=indv, size =3))+
  facet_wrap(time~.)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("total number of reads by time and treatment")



total_reads_summary %>% 
  ggplot(., aes(x=trt, y=nuclear_reads ))+
  geom_boxplot(aes(fill=trt))+
 geom_point(aes(col=indv, size =3))+
  facet_wrap(time~.)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("total number of nuclear reads by time and treatment")


total_reads_summary %>% 
  ggplot(., aes(x=trt, y=unique_mapped_reads ))+
  geom_boxplot(aes(fill=trt))+
 geom_point(aes(col=indv, size =3))+
  facet_wrap(time~.)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("total number of unique-nuclear reads by time and treatment")



total_reads_summary %>% 
  ggplot(., aes(x=trt, y=dedup_reads ))+
  geom_boxplot(aes(fill=trt))+
  geom_point(aes(col=indv, size =3))+
  facet_wrap(time~.)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("total unique, deduplicated nuclear mapped reads by time and treatment")


```
### Peak features


```{r peak info}
##collecting summary files

# Ind1_peaksummary <- read_table("~/ATAC_downloads/Ind1/trimmed/macs_output/Ind1_peaksummary.txt",
#     col_names = FALSE) %>%
#   rename(X1 ="counts", X2= "sample")
# Ind2_peaksummary <- read_table("~/ATAC_downloads/Ind2/trimmed/macs_output/Ind2_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind3_peaksummary <- read_table("~/ATAC_downloads/Ind3/trimmed/macs_output/Ind3_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind4_peaksummary <- read_table("~/ATAC_downloads/Ind4/trimmed/macs_output/Ind4_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind5_peaksummary <- read_table("~/ATAC_downloads/Ind5/trimmed/macs_output/Ind5_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Ind6_peaksummary <- read_table("~/ATAC_downloads/Ind6/trimmed/macs_output/Ind6_peaksummary.txt",
#     col_names = FALSE)%>%
#   rename(X1 ="counts", X2= "sample")
# Peaksummary <- rbind(Ind1_peaksummary,Ind2_peaksummary,Ind3_peaksummary,Ind4_peaksummary,Ind5_peaksummary,Ind6_peaksummary)
# # 
# write.csv(Peaksummary, "data/first_Peaksummarycounts.csv")
Peaksummary <- read.csv("data/first_Peaksummarycounts.csv",row.names=1)
Peaksummary %>% 
  dplyr::filter(sample != "total") %>% 
   separate(sample, into=c(NA,"indv","sample",NA,NA,NA)) %>% 
  mutate(trt=gsub("[[:digit:]]", "",sample)) %>% 
  # mutate(trt=substr(trt,-1,2))
  mutate(time = if_else(grepl("24h$", sample) ==TRUE, "24_hours","3_hours")) %>% 
  mutate(trt = case_match(trt,"DAh"~"DNR","DXh"~"DOX","Eh"~"EPI", "Mh" ~ "MTX", "Th" ~ "TRZ", "Vh" ~"VEH",.default = trt)) %>% 
  mutate(indv = factor(indv, levels = c("Ind1", "Ind2", "Ind3", "Ind4", "Ind5", "Ind6"))) %>%
  mutate(time = factor(time, levels = c("3_hours", "24_hours"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels =  c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH")))%>% 
  ggplot(., aes(x =trt, y=counts,group=trt))+
  geom_boxplot(aes(fill= trt))+
  geom_point(aes(col=indv, size =3))+
  facet_wrap(~time)+
   scale_fill_manual(values=drug_pal_fact)+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("Peak counts by treatment")+
  theme_bw()



```


### Ind1 Peaks

```{r Ind1 inital TSS setup}

# plotAnnoBar(anno_ind4_V24h, main = "Genomic Feature Distribution")+ ggtitle("Ind4 VEH 24 hour")
# plotAnnoBar(anno_ind1_DA24h, main = "Genomic Feature Distribution")+ ggtitle("Ind1 DNR 24 hour")

# ind4_V24hpeaks_gr <- prepGRangeObj(ind4_V24hpeaks)
# ind1_DA24hpeaks_gr <- prepGRangeObj((ind1_DA24hpeaks))
# Epi_list <- GRangesList(ind1_DA24hpeaks_gr, ind4_V24hpeaks_gr)
# # ##plotting the TSS average window (making an overlap of each using Epi_list as list holder)
# Epi_list_tagMatrix = lapply(Epi_list, getTagMatrix, windows = TSS)
# plotAvgProf(Epi_list_tagMatrix, xlim=c(-3000, 3000), ylab = "Count Frequency")
#plotPeakProf(Epi_list_tagMatrix, facet = "none", conf = 0.95)

## What I did here:  I called all my narrowpeak files
# peakfiles1 <- choose.files()

##these were practice for getting file names and shortening for the for loop below
# testname <- basename(peakfiles1[1])
# str_split_i(testname, "_",3)

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind1_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles1[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind1_peaks[[banana_peel]] <- readPeakFile(peakfiles1[file])
# }
# saveRDS(Ind1_peaks, "data/Ind1_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)
# peakAnnoList_1 <- lapply(Ind1_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_1, "data/peakAnnoList_1.RDS")

peakAnnoList_1 <- readRDS("data/peakAnnoList_1.RDS")
plotAnnoBar(peakAnnoList_1, main = "Genomic Feature Distribution")


# saveRDS(Epi_list_tagMatrix, "data/Ind1_TSS_peaks.RDS")

Ind1_TSS_peaks_plot <- readRDS("data/Ind1_TSS_peaks.RDS")

# Epi_list_tagMatrix = lapply(Ind1_peaks, getTagMatrix, windows = TSS)

plotAvgProf(Ind1_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 1" )

plotAvgProf(Ind1_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 1" )

```


### Ind2 Peaks

```{r Ind2 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles2 <- choose.files()

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind2_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles2[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind2_peaks[[banana_peel]] <- readPeakFile(peakfiles2[file])
# }
# saveRDS(Ind2_peaks, "data/Ind2_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind2_peaks <- readRDS("data/Ind2_peaks_list.RDS")
# peakAnnoList_2 <- lapply(Ind2_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_2, "data/peakAnnoList_2.RDS")

peakAnnoList_2 <- readRDS("data/peakAnnoList_2.RDS")
plotAnnoBar(peakAnnoList_2, main = "Genomic Feature Distribution, Individual 2")

# Epi_list_tagMatrix = lapply(Ind2_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind2_TSS_peaks.RDS")

Ind2_TSS_peaks_plot <- readRDS("data/Ind2_TSS_peaks.RDS")



plotAvgProf(Ind2_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 2" )

plotAvgProf(Ind2_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 2" )

```


### Ind3 Peaks

```{r Ind3 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles3 <- choose.files()

##This loop first established a list then (because I already knew the list had 12 files)
## I then imported each of these onto that list.  Once I had the list, I stored it as
## an R object, 
# Ind3_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles3[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind3_peaks[[banana_peel]] <- readPeakFile(peakfiles3[file])
# }
# saveRDS(Ind3_peaks, "data/Ind3_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind3_peaks <- readRDS("data/Ind3_peaks_list.RDS")
# peakAnnoList_3 <- lapply(Ind3_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_3, "data/peakAnnoList_3.RDS")

peakAnnoList_3 <- readRDS("data/peakAnnoList_3.RDS")
plotAnnoBar(peakAnnoList_3, main = "Genomic Feature Distribution, Individual 3")

# Epi_list_tagMatrix = lapply(Ind3_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind3_TSS_peaks.RDS")

Ind3_TSS_peaks_plot <- readRDS("data/Ind3_TSS_peaks.RDS")



plotAvgProf(Ind3_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 3" )

plotAvgProf(Ind3_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 3" )

```


### Ind4 Peaks

```{r Ind4 inital TSS setup}

## What I did here:  I called all my narrowpeak files

# peakfiles4 <- choose.files()
# 
# ##This loop first established a list then (because I already knew the list had 12 files)
# ## I then imported each of these onto that list.  Once I had the list, I stored it as
# ## an R object, 
# Ind4_peaks <- list()
# for (file in 1:12){
#     testname <- basename(peakfiles4[file])
#   banana_peel <- str_split_i(testname, "_",3)
#  Ind4_peaks[[banana_peel]] <- readPeakFile(peakfiles4[file])
# }
# saveRDS(Ind4_peaks, "data/Ind4_peaks_list.RDS")
# I then called annotatePeak on that list object, and stored that as a R object for later retrieval.)

Ind4_peaks <- readRDS("data/Ind4_peaks_list.RDS")
# peakAnnoList_4 <- lapply(Ind4_peaks, annotatePeak, tssRegion =c(-2000,2000), TxDb= txdb)
# saveRDS(peakAnnoList_4, "data/peakAnnoList_4.RDS")

peakAnnoList_4 <- readRDS("data/peakAnnoList_4.RDS")
plotAnnoBar(peakAnnoList_4, main = "Genomic Feature Distribution, Individual 4")

# Epi_list_tagMatrix = lapply(Ind4_peaks, getTagMatrix, windows = TSS)
# saveRDS(Epi_list_tagMatrix, "data/Ind4_TSS_peaks.RDS")

Ind4_TSS_peaks_plot <- readRDS("data/Ind4_TSS_peaks.RDS")



plotAvgProf(Ind4_TSS_peaks_plot[c(1,3,5,7,9,11)], xlim=c(-3000, 3000), ylab = "Count Frequency")+ ggtitle("3 hour Individual 4" )

plotAvgProf(Ind4_TSS_peaks_plot[c(2,4,6,8,10,12)], xlim=c(-3000, 3000),ylab = "Count Frequency")+ ggtitle("24 hour Individual 4" )

```
