---
title: "Peak_analysis"
author: "ERM"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r  package loading}
library(tidyverse)
library(ggsignif)
library(cowplot)
library(ggpubr)
library(scales)
# library(sjmisc)
library(kableExtra)
# library(broom)
# library(biomaRt)
library(RColorBrewer)
# library(gprofiler2)
# library(qvalue)
# library(ChIPseeker)
# library("TxDb.Hsapiens.UCSC.hg38.knownGene")
# library("org.Hs.eg.db")
# library(ATACseqQC)
# library(rtracklayer)
library(gridExtra)
library(edgeR)
library(ggfortify)
library(limma)
```

```{r functions to have}
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
pca_plot <-
  function(df,
           col_var = NULL,
           shape_var = NULL,
           title = "") {
    ggplot(df) + geom_point(aes_string(
      x = "PC1",
      y = "PC2",
      color = col_var,
      shape = shape_var
    ),
    size = 5) +
      labs(title = title, x = "PC 1", y = "PC 2") +
      scale_color_manual(values = c(
        "#8B006D",
        "#DF707E",
        "#F1B72B",
        "#3386DD",
        "#707031",
        "#41B333"
      ))
  }
pca_var_plot <- function(pca) {
  # x: class == prcomp
  pca.var <- pca$sdev ^ 2
  pca.prop <- pca.var / sum(pca.var)
  var.plot <-
    qplot(PC, prop, data = data.frame(PC = 1:length(pca.prop),
                                      prop = pca.prop)) +
    labs(title = 'Variance contributed by each PC',
         x = 'PC', y = 'Proportion of variance')
}

calc_pca <- function(x) {
  # Performs principal components analysis with prcomp
  # x: a sample-by-gene numeric matrix
  prcomp(x, scale. = TRUE, retx = TRUE)
}

get_regr_pval <- function(mod) {
  # Returns the p-value for the Fstatistic of a linear model
  # mod: class lm
  stopifnot(class(mod) == "lm")
  fstat <- summary(mod)$fstatistic
  pval <- 1 - pf(fstat[1], fstat[2], fstat[3])
  return(pval)
}

plot_versus_pc <- function(df, pc_num, fac) {
  # df: data.frame
  # pc_num: numeric, specific PC for plotting
  # fac: column name of df for plotting against PC
  pc_char <- paste0("PC", pc_num)
  # Calculate F-statistic p-value for linear model
  pval <- get_regr_pval(lm(df[, pc_char] ~ df[, fac]))
  if (is.numeric(df[, f])) {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_point() +
      geom_smooth(method = "lm") + labs(title = sprintf("p-val: %.2f", pval))
  } else {
    ggplot(df, aes_string(x = f, y = pc_char)) + geom_boxplot() +
      labs(title = sprintf("p-val: %.2f", pval))
  }
}
x_axis_labels = function(labels, every_nth = 1, ...) {
  axis(side = 1,
       at = seq_along(labels),
       labels = F)
  text(
    x = (seq_along(labels))[seq_len(every_nth) == 1],
    y = par("usr")[3] - 0.075 * (par("usr")[4] - par("usr")[3]),
    labels = labels[seq_len(every_nth) == 1],
    xpd = TRUE,
    ...
  )
}

```


### Initial peak calling heatmap
```{r cpm and corr plots}
first_run_frag_counts <- read.csv("data/first_run_frag_counts.txt", row.names = 1) 
Frag_cor <- first_run_frag_counts %>% 
  dplyr::select(Ind1_75DA24h:Ind6_71V3h)  %>% 
  cpm(., log = TRUE) %>% 
  cor()
  
filmat_groupmat_col <- data.frame(timeset = colnames(Frag_cor))

counts_corr_mat <-filmat_groupmat_col %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>% 
  mutate(timeset=gsub("87","2_",timeset)) %>% 
  mutate(timeset=gsub("77","3_",timeset)) %>% 
  mutate(timeset=gsub("79","4_",timeset)) %>% 
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>% 
  mutate(timeset = gsub("24h","_24h",timeset), 
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(class = if_else(trt == "DNR", "AC", if_else(
    trt == "DOX", "AC", if_else(trt == "EPI", "AC", "nAC")
  ))) %>%
  mutate(TOP2i = if_else(trt == "DNR", "yes", if_else(
    trt == "DOX", "yes", if_else(trt == "EPI", "yes", if_else(trt == "MTX", "yes", "no"))
  ))) 
                         
 mat_colors <- list( 
   trt= c("#F1B72B","#8B006D","#DF707E","#3386DD","#707031","#41B333"),
   indv=c("#1B9E77", "#D95F02" ,"#7570B3", "#E7298A" ,"#66A61E", "#E6AB02"),
   time=c("pink", "chocolate4"),
   class=c("yellow1","darkorange1"), 
   TOP2i =c("darkgreen","lightgreen"))                        
                         
names(mat_colors$trt)   <- unique(counts_corr_mat$trt)                      
names(mat_colors$indv) <- unique(counts_corr_mat$indv)
names(mat_colors$time) <- unique(counts_corr_mat$time)
names(mat_colors$class) <- unique(counts_corr_mat$class)
names(mat_colors$TOP2i) <- unique(counts_corr_mat$TOP2i)


ComplexHeatmap::pheatmap(Frag_cor,
                         # column_title=(paste0("RNA-seq log"[2]~"cpm correlation")),
        annotation_col = counts_corr_mat,
        annotation_colors = mat_colors,
        heatmap_legend_param = mat_colors,
        fontsize=10,
        fontsize_row = 8,
        angle_col="90",
        treeheight_row=25,
        fontsize_col = 8,
        treeheight_col = 20)




```
This correlation is after log2 of the counts in peaks.   The next correlation will filter out rowMeans >0.

```{r inital analysis}
first_run_frag_counts <- read.csv("data/first_run_frag_counts.txt", row.names = 1) 

##loading of the counts matrix
##then separting off the non-counts columns
PCAmat <- first_run_frag_counts %>% 
  dplyr::select(Ind1_75DA24h:Ind6_71V3h) %>% as.matrix()

annotation_mat <- data.frame(timeset=colnames(PCAmat)) %>% 
  mutate(sample = timeset) %>% 
  mutate(timeset=gsub("Ind1_75","1_",timeset)) %>% 
  mutate(timeset=gsub("Ind2_87","2_",timeset)) %>% 
  mutate(timeset=gsub("Ind3_77","3_",timeset)) %>% 
  mutate(timeset=gsub("Ind4_79","4_",timeset)) %>% 
  mutate(timeset=gsub("Ind5_78","5_",timeset)) %>%
  mutate(timeset=gsub("Ind6_71","6_",timeset)) %>% 
  mutate(timeset = gsub("24h","_24h",timeset), 
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>% 
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  # mutate(indv = factor(indv, levels = c("1", "2", "3", "4", "5", "6"))) %>%
  mutate(time = factor(time, levels = c("3h", "24h"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) 

PCA_info <- (prcomp(t(PCAmat), scale. = TRUE)) 
PCA_info_anno <- PCA_info$x %>% cbind(.,annotation_mat)
# autoplot(PCA_info)
summary(PCA_info)
# cpm(PCAmat, log=TRUE)
pca_plot(PCA_info_anno, col_var='trt', shape_var = 'time')
        
pca_plot(PCA_info_anno, col_var='trt', shape_var = 'indv')
```
This PCA is impacted by the number of reads per sample too.  
### Log2 cpm of initial peak counts
```{r filtering step initial peaks}

lcpm <- cpm(PCAmat, log=TRUE)  ### for determining the basic cutoffs
dim(lcpm)

row_means <- rowMeans(lcpm)
x_filtered <- PCAmat[row_means > 0,]
dim(x_filtered)

filt_matrix_lcpm <- cpm(x_filtered, log=TRUE)
# hist(lcpm,  main = "Histogram of total counts (unfiltered)", 
#      xlab =expression("Log"[2]*" counts-per-million"), col =4 )
# 
# hist(filt_matrix_lcpm, main = "Histogram of total counts (filtered)", 
#      xlab =expression("Log"[2]*" counts-per-million"), col =4 )
PCA_info_filter <- (prcomp(t(filt_matrix_lcpm), scale. = TRUE))
summary(PCA_info_filter)
# autoplot(PCA_info_filter)

pca_var_plot(PCA_info_filter)

pca_n45 <- calc_pca(t(filt_matrix_lcpm))
pca_n45_anno <- data.frame(annotation_mat, pca_n45$x)


head(pca_n45_anno)[,1:12]
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")

pca_n45_anno %>%
  ggplot(.,aes(x = PC1, y = PC2, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(cpm)"))+
  theme_bw()+
  guides(col="none", size =4)+
  # labs(y = "PC 2 (15.76%)", x ="PC 1 (29.06%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))






pca_n45_anno %>%
  ggplot(.,aes(x = PC3, y = PC4, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(peaks)"))+
  theme_bw()+
  guides(col="none", size =4)+
  # labs(y = "PC 2 (15.76%)", x ="PC 1 (29.06%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))


Frag_cor_filter <- filt_matrix_lcpm %>% cor()
ComplexHeatmap::pheatmap(Frag_cor_filter,
                         # column_title=(paste0("RNA-seq log"[2]~"cpm correlation")),
        annotation_col = counts_corr_mat,
        annotation_colors = mat_colors,
        heatmap_legend_param = mat_colors,
        fontsize=10,
        fontsize_row = 8,
        angle_col="90",
        treeheight_row=25,
        fontsize_col = 8,
        treeheight_col = 20)


```
 We go from `r dim(lcpm)` peaks to`r dim(x_filtered)` peaks using rowMeans (log2cpm) > 0 across all samples.  The heatmap shows good clustering in treatments, with individual 5 and some of individual 4 at 3 hours clustering outside.  This is inline with QC metrics (FRiP) and Fragment lengths graphs.

### High confidence peak set


Based on the initial peaks, I wanted to know if they same thing is seen in a high confidence set of peaks.  To this end, I did several steps in bedtools to create a high confidence set.  

-First I moved all .narrowPeak files into the same folder and ran `bedtools multiinter -i ./* >log.file.txt` to create an intersection of all peaks.  I then was only interested in segments that had a count of more than 4 (intersection existed in at least 4 of the data sets) in all files.   I filtered column #4 of the `log.file.txt` output by `awk -F"\t" '$4 > 4 {print $1"\t"$2"\t"$3 }' log.file.txt > all_filt_peaks.bed` and printed the results of anything >4 in bed format to the `all_filt_peaks.bed` file.   Upon further reading of bedtools documents, I realized the number of "peaks" was actually fragments of peaks that were intersected amoung all files.  This was not the final output I wanted so I intersected these high counted segments back with the very first initial mergedPeaks.bed file using `bedtools intersect -a mergedPeaks.bed -b all_filt_peaks.bed -wa -u > merged_filtered_peaks.bed`.  using the `-wa -u` flags allowed me to filter the first mergedPeaks file, keeping only those high confidence peaks that overlapped the `all_filt_peaks.bed` and only reporting the unique calls.
This left me with a file that went from 470,000+ to 162,264   high confidence peaks that I will analyze below.

** I added a new step on the 15th.   I filtered out the blacklisted regions using the following code: `intersectBed -v -a merged_filtered_peaks.bed -b Blacklist/hg38.blacklist.bed.gz > final_bl_filt_peaks.bed`
My final peaks file contains 162243 peaks.  Not much of a difference, but may have an impact later after I reanalyze.


```{r highconf peaks}
##the file was called all_filt_peaks before I imported into this library
##I then saved as high_conf_peaks_counts.txt

###this removes that pesky long file names
# names(high_conf_peak_counts) = gsub(pattern = "_S.*", replacement = "", x = names(high_conf_peak_counts))
# # 
# names(high_conf_peak_counts)=gsub(pattern = "^ind6.trimmed.filt_files.trimmed_", replacement = "", x = names(high_conf_peak_counts))

# write.csv(high_conf_peak_counts, "data/high_conf_peaks_bl_counts.txt")
## write_delim(all_bl_filt_peaks, "data/high_conf_peaks_bl_counts.txt")
high_conf_peak_counts <- read.csv("data/high_conf_peaks_bl_counts.txt", row.names = 1)


Frag_cor_filt <- high_conf_peak_counts %>% 
  dplyr::select(Ind1_75DA24h:Ind6_71V3h)  %>% 
  cpm(., log = TRUE) %>% 
  cor()
  
filmat_groupmat_col1 <- data.frame(timeset = colnames(Frag_cor_filt))

counts_corr_mat1 <-filmat_groupmat_col1 %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>% 
  mutate(timeset=gsub("87","2_",timeset)) %>% 
  mutate(timeset=gsub("77","3_",timeset)) %>% 
  mutate(timeset=gsub("79","4_",timeset)) %>% 
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>% 
  mutate(timeset = gsub("24h","_24h",timeset), 
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(class = if_else(trt == "DNR", "AC", if_else(
    trt == "DOX", "AC", if_else(trt == "EPI", "AC", "nAC")
  ))) %>%
  mutate(TOP2i = if_else(trt == "DNR", "yes", if_else(
    trt == "DOX", "yes", if_else(trt == "EPI", "yes", if_else(trt == "MTX", "yes", "no"))
  ))) 
                         
 mat_colors <- list( 
   trt= c("#F1B72B","#8B006D","#DF707E","#3386DD","#707031","#41B333"),
   indv=c("#1B9E77", "#D95F02" ,"#7570B3", "#E7298A" ,"#66A61E", "#E6AB02"),
   time=c("pink", "chocolate4"),
   class=c("yellow1","darkorange1"), 
   TOP2i =c("darkgreen","lightgreen"))                        
                         
names(mat_colors$trt)   <- unique(counts_corr_mat1$trt)                      
names(mat_colors$indv) <- unique(counts_corr_mat1$indv)
names(mat_colors$time) <- unique(counts_corr_mat1$time)
names(mat_colors$class) <- unique(counts_corr_mat1$class)
names(mat_colors$TOP2i) <- unique(counts_corr_mat1$TOP2i)


ComplexHeatmap::pheatmap(Frag_cor_filt,
                         # column_title=(paste0("RNA-seq log"[2]~"cpm correlation")),
        annotation_col = counts_corr_mat1,
        annotation_colors = mat_colors,
        heatmap_legend_param = mat_colors,
        fontsize=10,
        fontsize_row = 8,
        angle_col="90",
        treeheight_row=25,
        fontsize_col = 8,
        treeheight_col = 20)




```
Changes in the heatmap are as follows:  
 Ind4 and Ind5 segregate out of the full correlation.  3 hour treatments AC and non-AC cluster out into the lower right.  Very sharp AC signal seen in 3 hours  and 24 hours so far.
 
 
Next I will try my initial Differential accessibility analysis.

### DAR high confidence peak set1

```{r DAR_highconf}

##filter log cpm counts file
my_hc_counts <- high_conf_peak_counts %>% 
  dplyr::select(Geneid,Ind1_75DA24h:Ind6_71V3h) %>% 
  column_to_rownames("Geneid")

lcpm <- cpm(my_hc_counts, log=TRUE)  ### for determining the basic cutoffs



row_means <- rowMeans(lcpm)
my_hc_filtered_counts <- my_hc_counts[row_means > 0,]
dim(my_hc_filtered_counts)
##3 now have 153,348 high conf peaks
group <- c( rep(c(1,2,3,4,5,6,7,8,9,10,11,12),6))
group <- factor(group, levels =c("1","2","3","4","5","6","7","8","9","10","11","12"))
short_names <- paste0(counts_corr_mat1$indv,"_",counts_corr_mat1$trt,"_",counts_corr_mat1$time)
# saveRDS(my_hc_filtered_counts,"data/my_hc_filt_counts.RDS")
dge <- DGEList.data.frame(counts = my_hc_filtered_counts, group = group, genes = row.names(my_hc_filtered_counts))

##renaming colnames
colnames(my_hc_filtered_counts) <- short_names
dge$group$indv <- counts_corr_mat1$indv
dge$group$time <- counts_corr_mat1$time
dge$group$trt <- counts_corr_mat1$trt




indv <- counts_corr_mat1$indv
# indv <- factor(indv, levels = c(1,2,3,4,5,6))
time <- counts_corr_mat1$time
# time <- factor(time, levels =c("3h","24"))
trt <- counts_corr_mat1$trt
# trt <- factor(trt, levels = c("VEH","DOX","EPI","DNR","MTX","TRZ",))

##commented out to save time for future processing

efit2 <- readRDS("data/filt_Peaks_efit2_bl.RDS")

group_1 <- c(rep(c("DNR_24","DNR_3","DOX_24","DOX_3","EPI_24","EPI_3","MTX_24","MTX_3","TRZ_24","TRZ_3","VEH_24", "VEH_3"),6))


mm <- model.matrix(~0 +group_1)  
# colnames(mm) <- c("DNR_24", "DNtrt_n45# colnames(mm) <- c("DNR_24", "DNR_3", "DOX_24","DOX_3","EPI_24", "EPI_3","MTX_24", "MTX_3", "TRZ_24","TRZ_3","VEH_24", "VEH_3")

# y <- voom(dge$counts, mm,plot =TRUE)
# 
# corfit <- duplicateCorrelation(y, mm, block = indv)
# 
# v <- voom(dge$counts, mm, block = indv, correlation = corfit$consensus)
# 
# fit <- lmFit(v, mm, block = indv, correlation = corfit$consensus)
# colnames(mm) <- c("DNR_24","DNR_3","DOX_24","DOX_3","EPI_24","EPI_3","MTX_24","MTX_3","TRZ_24","TRZ_3","VEH_24", "VEH_3")
#
#
# cm <- makeContrasts(
#   DNR_3.VEH_3 = DNR_3-VEH_3,
#   DOX_3.VEH_3 = DOX_3-VEH_3,
#   EPI_3.VEH_3 = EPI_3-VEH_3,
#   MTX_3.VEH_3 = MTX_3-VEH_3,
#   TRZ_3.VEH_3 = TRZ_3-VEH_3,
#   DNR_24.VEH_24 =DNR_24-VEH_24,
#   DOX_24.VEH_24= DOX_24-VEH_24,
#   EPI_24.VEH_24= EPI_24-VEH_24,
#   MTX_24.VEH_24= MTX_24-VEH_24,
#   TRZ_24.VEH_24= TRZ_24-VEH_24,
#   levels = mm)

# vfit <- lmFit(y, mm)

# vfit<- contrasts.fit(vfit, contrasts=cm)
# 
# efit2 <- eBayes(vfit)
# saveRDS(efit2,"data/filt_Peaks_efit2_bl.RDS")

results = decideTests(efit2)
summary(results)
```


### Evaluation of change in peaks

```{r toptable eval}

V.DNR_3.top= topTable(efit2, coef=1, adjust.method="BH", number=Inf, sort.by="p")
V.DOX_3.top= topTable(efit2, coef=2, adjust.method="BH", number=Inf, sort.by="p")
V.EPI_3.top= topTable(efit2, coef=3, adjust.method="BH", number=Inf, sort.by="p")
V.MTX_3.top= topTable(efit2, coef=4, adjust.method="BH", number=Inf, sort.by="p")
V.TRZ_3.top= topTable(efit2, coef=5, adjust.method="BH", number=Inf, sort.by="p")
V.DNR_24.top= topTable(efit2, coef=6, adjust.method="BH", number=Inf, sort.by="p")
V.DOX_24.top= topTable(efit2, coef=7, adjust.method="BH", number=Inf, sort.by="p")
V.EPI_24.top= topTable(efit2, coef=8, adjust.method="BH", number=Inf, sort.by="p")
V.MTX_24.top= topTable(efit2, coef=9, adjust.method="BH", number=Inf, sort.by="p")
V.TRZ_24.top= topTable(efit2, coef=10, adjust.method="BH", number=Inf, sort.by="p")

# toplist_full  <- list(V.DNR_3.top, V.DOX_3.top,V.EPI_3.top,V.MTX_3.top,V.TRZ_3.top,V.DNR_24.top, V.DOX_24.top,V.EPI_24.top,V.MTX_24.top,V.TRZ_24.top)
# names(toplist_full) <- c("DNR_3", "DOX_3","EPI_3","MTX_3","TRZ_3","DNR_24", "DOX_24","EPI_24","MTX_24","TRZ_24")
# toplist_6 <-map_df(toplist_full, ~as.data.frame(.x), .id="trt_time")
# 
# toplist_6 <- toplist_6 %>% 
#   separate(trt_time, into= c("trt","time"), sep = "_") %>% 
#   mutate(trt=factor(trt, levels = c("DOX","EPI","DNR","MTX","TRZ"))) %>% 
#   mutate(time = factor(time, levels = c("3", "24"), labels = c("3 hours", "24 hours")))
# saveRDS(toplist_6, "data/toplist_6.RDS")


```

### 3 hour boxplots full set
```{r examine top3_3h}
DNR_3_top3 <- row.names(V.DNR_3.top[1:3,])

log_filt_hc <- my_hc_filtered_counts %>% 
  cpm(., log=TRUE) %>% as.data.frame()

row.names(log_filt_hc) <- row.names(my_hc_filtered_counts)
log_filt_hc %>% 
  dplyr::filter(row.names(.) %in% DNR_3_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour DNR")+
  scale_fill_manual(values = drug_pal)+
  theme_bw()
  
DOX_3_top3 <- row.names(V.DOX_3.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% DOX_3_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour DOX")+
  scale_fill_manual(values = drug_pal)+
  theme_bw()


EPI_3_top3 <- row.names(V.EPI_3.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% EPI_3_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour EPI")+
  scale_fill_manual(values = drug_pal)+
  theme_bw()

MTX_3_top3 <- row.names(V.MTX_3.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% MTX_3_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour MTX")+
  scale_fill_manual(values = drug_pal)+
  theme_bw()



TRZ_3_top3 <- row.names(V.TRZ_3.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% TRZ_3_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour TRZ")+
  scale_fill_manual(values = drug_pal)+
  theme_bw()

```
## 24 hour boxplots full set

```{r 24hourtopexpression}

DNR_24_top3 <- row.names(V.DNR_24.top[1:3,])

log_filt_hc <- my_hc_filtered_counts %>% 
  cpm(., log=TRUE) %>% as.data.frame()
row.names(log_filt_hc) <- row.names(my_hc_filtered_counts)
log_filt_hc %>% 
  dplyr::filter(row.names(.) %in% DNR_24_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour DNR")+
  scale_fill_manual(values = drug_pal)
  
DOX_24_top3 <- row.names(V.DOX_24.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% DOX_24_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour DOX")+
  scale_fill_manual(values = drug_pal)


EPI_24_top3 <- row.names(V.EPI_24.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% EPI_24_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour EPI")+
  scale_fill_manual(values = drug_pal)

MTX_24_top3 <- row.names(V.MTX_24.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% MTX_24_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour MTX")+
  scale_fill_manual(values = drug_pal)



TRZ_24_top3 <- row.names(V.TRZ_24.top[1:3,])

log_filt_hc %>%  
  dplyr::filter(row.names(.) %in% TRZ_24_top3) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour TRZ")+
  scale_fill_manual(values = drug_pal)

```

### Volcano plots of peaks

```{r volcano plots}
library(cowplot)
efit2 <- readRDS("data/filt_Peaks_efit2_bl.RDS")
# volcanoplot(efit2,coef = c(1,2,3,4,5,6),style = "p-value",
#                           # highlight = 8,
#                           # names = efit2$genes$SYMBOL,
#                           hl.col = "red",xlab = "Log2 Fold Change",
#                           ylab = NULL,pch = 16,cex = 0.35,
#                           main = "test")
# 

plot_filenames <- c("V.DNR_3.top","V.DOX_3.top","V.EPI_3.top","V.MTX_3.top",
                    "V.TRZ_.top","V.DNR_24.top","V.DOX_24.top","V.EPI_24.top",
                    "V.MTX_24.top","V.TRZ_24.top")
plot_files <- c( V.DNR_3.top,V.DOX_3.top,V.EPI_3.top,V.MTX_3.top,
                    V.TRZ_3.top,V.DNR_24.top,V.DOX_24.top,V.EPI_24.top,
                    V.MTX_24.top,V.TRZ_24.top)

volcanosig <- function(df, psig.lvl) {
    df <- df %>% 
    mutate(threshold = ifelse(adj.P.Val > psig.lvl, "A", ifelse(adj.P.Val <= psig.lvl & logFC<=0,"B","C")))
      # ifelse(adj.P.Val <= psig.lvl & logFC >= 0,"B", "C")))
    ##This is where I could add labels, but I have taken out
    # df <- df %>% mutate(genelabels = "")
    # df$genelabels[1:topg] <- df$rownames[1:topg]
    
  ggplot(df, aes(x=logFC, y=-log10(adj.P.Val))) + 
    geom_point(aes(color=threshold))+
    # geom_text_repel(aes(label = genelabels), segment.curvature = -1e-20,force = 1,size=2.5,
    # arrow = arrow(length = unit(0.015, "npc")), max.overlaps = Inf) +
    #geom_hline(yintercept = -log10(psig.lvl))+
    xlab(expression("Log"[2]*" FC"))+
    ylab(expression("-log"[10]*"adj. P Value"))+
    scale_color_manual(values = c("black", "red","blue"))+
    theme_cowplot()+
    theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(0.8))) 
}
#v1<- volcanosig(V.DA24.top, 0.01,0)
v1 <- volcanosig(V.DNR_3.top, 0.01)+ ggtitle("Daunorubicin 3 hour")
v2 <- volcanosig(V.DNR_24.top, 0.01)+ ggtitle("Daunorubicin 24 hour")+ylab("")
v3 <- volcanosig(V.DOX_3.top, 0.01)+ ggtitle("Doxorubicin 3 hour")
v4 <- volcanosig(V.DOX_24.top, 0.01)+ ggtitle("Doxorubicin 24 hour")+ylab("")
v5 <- volcanosig(V.EPI_3.top, 0.01)+ ggtitle("Epirubicin 3 hour")
v6 <- volcanosig(V.EPI_24.top, 0.01)+ ggtitle("Epirubicin 24 hour")+ylab("")
v7 <- volcanosig(V.MTX_3.top, 0.01)+ ggtitle("Mitoxantrone 3 hour")
v8 <- volcanosig(V.MTX_24.top, 0.01)+ ggtitle("Mitoxantrone 24 hour")+ylab("")
v9 <- volcanosig(V.TRZ_3.top, 0.01)+ ggtitle("Trastuzumab 3 hour")
v10 <- volcanosig(V.TRZ_24.top, 0.01)+ ggtitle("Trastuzumab 24 hour")+ylab("")
# volcanoplot(efit2,coef = 10,style = "p-value",
#                           highlight = 8,
#                           names = efit2$genes$SYMBOL,
#                           hl.col = "red",xlab = "Log2 Fold Change",
#                           ylab = NULL,pch = 16,cex = 0.35,
#                           main = "Using Trastuzumab 24 hour data and volcanoplot function")
plot_grid(v1,v2,  rel_widths =c(.8,1))
plot_grid(v3,v4,  rel_widths =c(.8,1))
plot_grid(v5,v6,  rel_widths =c(.8,1))
plot_grid(v7,v8,  rel_widths =c(.8,1))
plot_grid(v9,v10,  rel_widths =c(.8,1))

```

### PCA analysis of full set


This is the PCA above redone on the filtered matrix of my_hc_filtered_counts.  The "low' expression


```{r filtering step hcpeaks}

my_hc_filtered_counts <- readRDS("data/my_hc_filt_counts.RDS")
PCAmat_all <- my_hc_filtered_counts %>%
  cpm(., log = TRUE) %>% 
  as.matrix()

annotation_mat_all  <-
  data.frame(timeset=colnames(PCAmat_all )) %>% 
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>% 
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(indv = factor(indv, levels = c("1", "2", "3", "4", "5", "6"))) %>%
  mutate(time = factor(time, levels = c("3h", "24h"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) 

PCA_info_all  <- (prcomp(t(PCAmat_all ), scale. = TRUE)) 
PCA_info_anno_all  <- PCA_info_all$x %>% cbind(.,annotation_mat_all )
# autoplot(PCA_info)
summary(PCA_info_all)
# cpm(PCAmat, log=TRUE)
# pca_plot(PCA_info_all , col_var='trt', shape_var = 'time')
#         
# pca_plot(PCA_info_all , col_var='trt', shape_var = 'indv')


drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")

PCA_info_anno_all  %>%
  ggplot(.,aes(x = PC1, y = PC2, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(cpm)"))+
  theme_bw()+
  guides(col="none", size =4)+
  labs(y = "PC 2 (13.81%)", x ="PC 1 (16.58%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))


PCA_info_anno_all  %>%
  ggplot(.,aes(x = PC3, y = PC4, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(peaks)"))+
  theme_bw()+
  guides(col="none", size =4)+
  labs(y = "PC 4 (5.3%)", x ="PC 3 (6.65%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))

```
### PCA of trt, time, indv for full set
```{r PCAfull segments}

facs <- c("indv", "trt", "time")
names(facs) <- c("Individual", "Treatment", "Time")
drug1 <- c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH")##for changing shapes and colors
time <- rep(c("24h", "3h"),36) %>% factor(., levels = c("3h","24h"))
##gglistmaking
for (f in facs) {
  # PC1 v PC2
  pca_plot(PCA_info_anno_all, col_var = f, shape_var = time,
           title = names(facs)[which(facs == f)])
  print(last_plot())
  
  # Plot f versus PC1 and PC2
  f_v_pc1 <- arrangeGrob(plot_versus_pc(PCA_info_anno_all, 1, f))
  f_v_pc2 <- arrangeGrob(plot_versus_pc(PCA_info_anno_all, 2, f))
  grid.arrange(f_v_pc1, f_v_pc2, ncol = 2, top = names(facs)[which(facs == f)])
  # summary(plot_versus_pc(PCA_info_anno_all, 1, f))
  # summary(plot_versus_pc(PCA_info_anno_all, 2, f))
 
}







```
### Magnitude of Response full set
```{r Magresp full set}
toplist_6 <- readRDS("data/toplist_6.RDS")

toplist_6 %>% 
  group_by(time, trt) %>% 
  mutate(sigcount = if_else(adj.P.Val < 0.05,'sig','notsig'))%>%
  count(sigcount) %>% 
  pivot_wider(id_cols = c(time,trt), names_from=sigcount, values_from=n) %>% 
  mutate(prop = sig/(sig+notsig)*100) %>% 
  mutate(prop=if_else(is.na(prop),0,prop)) %>% 
  ggplot(., aes(x=trt, y= prop))+
  geom_col(aes(fill=trt))+
  geom_text(aes(label = sprintf("%.2f",prop)),
            position=position_dodge(0.9),vjust=-.2 )+
  scale_fill_manual(values =drug_pal)+
  guides(fill=guide_legend(title = "Treatment"))+
  facet_wrap(~time)+#labeller = (time = facettimelabel) )+
  theme_bw()+
  xlab("")+
  ylab("Percentage DAR peaks")+
  theme_bw()+
  ggtitle("Percent DARs (adj. P value <0.05)")+
  scale_y_continuous(expand=expansion(c(0.02,.2)))+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        # axis.ticks = element_line(linewidth = 1.5),
        # axis.line = element_line(linewidth = 1.5),
        strip.background = element_rect(fill = "transparent"),
        axis.text.x = element_text(size = 8, color = "white", angle = 0),
        axis.text.y = element_text(size = 8, color = "black", angle = 0),
        strip.text.x = element_text(size = 12, color = "black", face = "bold"))

toplist_6 %>% 
  group_by(time, trt) %>% 
  ggplot(., aes(x=trt, y=logFC))+
  geom_boxplot(aes(fill=trt))+
  ggpubr::fill_palette(palette =drug_pal)+
  guides(fill=guide_legend(title = "Treatment"))+
  # facet_wrap(sigcount~time)+
  theme_bw()+
  xlab("")+
  ylab(expression("Log"[2]*" fold change"))+
  theme_bw()+
  facet_wrap(~time)+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        # axis.ticks = element_line(linewidth = 1.5),
        # axis.line = element_line(linewidth = 1.5),
        strip.background = element_rect(fill = "transparent"),
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 12, color = "black", face = "bold"))

toplist_6 %>% 
  group_by(time, trt) %>% 
  dplyr::filter(trt != "TRZ") %>%
  ggplot(., aes( x=(adj.P.Val)))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_bw()+
  ggtitle("adj.P.Value density by time/trt")+
  facet_wrap(time~trt)

toplist_6 %>% 
  group_by(time, trt) %>% 
  # dplyr::filter(trt == "DOX") %>% 
  ggplot(., aes( x=(P.Value)))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_bw()+
  ggtitle("P.Value density by time/trt")+
  facet_wrap(time~trt)



```





### Analysis without Indv 4 and 5
#### Heatmap log2cpm

```{r no 4 or 5 log2cpm}
high_conf_peak_counts <- read.csv("data/high_conf_peaks_bl_counts.txt", row.names = 1)


Frag_cor_filt_n45 <- high_conf_peak_counts %>% 
  dplyr::select(Ind1_75DA24h:Ind3_77V3h,Ind6_71DA24h:Ind6_71V3h)  %>% 
  cpm(., log = TRUE) %>% 
  cor()
  
filmat_groupmat_col_n45 <- data.frame(timeset = colnames(Frag_cor_filt_n45))

counts_corr_mat_n45 <-filmat_groupmat_col_n45 %>% 
  mutate(timeset=gsub("75","1_",timeset)) %>% 
  mutate(timeset=gsub("87","2_",timeset)) %>% 
  mutate(timeset=gsub("77","3_",timeset)) %>% 
  mutate(timeset=gsub("79","4_",timeset)) %>% 
  mutate(timeset=gsub("78","5_",timeset)) %>%
  mutate(timeset=gsub("71","6_",timeset)) %>% 
  mutate(timeset = gsub("24h","_24h",timeset), 
       timeset = gsub("3h","_3h",timeset)) %>%
  separate(timeset, into = c(NA,"indv","trt","time"), sep= "_") %>% 
  
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(class = if_else(trt == "DNR", "AC", if_else(
    trt == "DOX", "AC", if_else(trt == "EPI", "AC", "nAC")
  ))) %>%
  mutate(TOP2i = if_else(trt == "DNR", "yes", if_else(
    trt == "DOX", "yes", if_else(trt == "EPI", "yes", if_else(trt == "MTX", "yes", "no"))
  ))) 
                         
 mat_colors_n45 <- list( 
   trt= c("#F1B72B","#8B006D","#DF707E","#3386DD","#707031","#41B333"),
   indv=c("#1B9E77", "#D95F02" ,"#7570B3", "#E6AB02"),
   time=c("pink", "chocolate4"),
   class=c("yellow1","darkorange1"), 
   TOP2i =c("darkgreen","lightgreen"))                        
                         
names(mat_colors_n45$trt)   <- unique(counts_corr_mat_n45$trt)                      
names(mat_colors_n45$indv) <- unique(counts_corr_mat_n45$indv)
names(mat_colors_n45$time) <- unique(counts_corr_mat_n45$time)
names(mat_colors_n45$class) <- unique(counts_corr_mat_n45$class)
names(mat_colors_n45$TOP2i) <- unique(counts_corr_mat_n45$TOP2i)


ComplexHeatmap::pheatmap(Frag_cor_filt_n45,
                         # column_title=(paste0("RNA-seq log"[2]~"cpm correlation")),
        annotation_col = counts_corr_mat_n45,
        annotation_colors = mat_colors_n45,
        heatmap_legend_param = mat_colors_n45,
        fontsize=10,
        fontsize_row = 8,
        angle_col="90",
        treeheight_row=25,
        fontsize_col = 8,
        treeheight_col = 20)

```

#### DAR using 1,2,3,6

```{r DEG no 4 or 5}

my_hc_counts_n45 <- high_conf_peak_counts %>% 
  dplyr::select(Geneid,Ind1_75DA24h:Ind3_77V3h,Ind6_71DA24h:Ind6_71V3h) %>% 
  column_to_rownames("Geneid")

lcpm_n45 <- cpm(my_hc_counts_n45, log=TRUE)  ### for determining the basic cutoffs



row_means_n45 <- rowMeans(lcpm_n45)
my_hc_filtered_counts_n45 <- my_hc_counts_n45[row_means_n45 > 0,]
dim(my_hc_filtered_counts_n45)

# saveRDS(my_hc_filtered_counts_n45,"data/my_hc_filt_counts_n45.RDS")
##3 now have 151,800 high conf peaks
group_n45 <- c( rep(c(1,2,3,4,5,6,7,8,9,10,11,12),4))
group_n45 <- factor(group_n45, levels =c("1","2","3","4","5","6","7","8","9","10","11","12"))
short_names_n45 <- paste0(counts_corr_mat_n45$indv,"_",counts_corr_mat_n45$trt,"_",counts_corr_mat_n45$time)

dge_n45 <- DGEList.data.frame(counts = my_hc_filtered_counts_n45, group = group_n45, genes = row.names(my_hc_filtered_counts_n45))

##renaming colnames
colnames(my_hc_filtered_counts_n45) <- short_names_n45
# dge_n45$group$indv <- counts_corr_mat_n45$indv
# dge_n45$group$time <- counts_corr_mat_n45$time
# dge_n45$group$trt <- counts_corr_mat_n45$trt



indv_n45 <- counts_corr_mat_n45$indv
# indv <- factor(indv, levels = c(1,2,3,4,5,6))
time_n45 <- counts_corr_mat_n45$time
# time <- factor(time, levels =c("3h","24"))
trt_n45 <- counts_corr_mat_n45$trt
# trt <- factor(trt, levels = c("DOX","EPI","DNR","MTX","TRZ","VEH"))

efit2_n45 <- readRDS("data/filt_Peaks_efit2_n45.RDS")
##commented out to save time for future processing

group_n45 <- c(rep(c("DNR_24","DNR_3","DOX_24","DOX_3","EPI_24","EPI_3","MTX_24","MTX_3","TRZ_24","TRZ_3","VEH_24", "VEH_3"),4))

mm_n4 <- model.matrix(~0 +group_n45)
# mm_n45 <- model.matrix(~0 + indv_n45 +trt_n45+time_n45)
# colnames(mm) <- c("DNR_24", "DNR_3", "DOX_24","DOX_3","EPI_24", "EPI_3","MTX_24", "MTX_3", "TRZ_24","TRZ_3","VEH_24", "VEH_3")

# 
# y_n4 <- voom(dge_n45$counts,mm_n4)
# 
# 
# corfit_n4 <- duplicateCorrelation(y_n4, mm_n4, block = indv_n45)
# 
# v_n4 <- voom(dge_n45$counts, mm_n4, block = indv_n45, correlation = corfit_n4$consensus)
# 
# # 
# # 
# fit_n4 <- lmFit(v_n4, mm_n45, block = indv_n45, correlation = corfit_n4$consensus)
# 
# colnames(mm_n4) <- c("DNR_24","DNR_3","DOX_24","DOX_3","EPI_24","EPI_3","MTX_24","MTX_3","TRZ_24","TRZ_3","VEH_24", "VEH_3")


# cm_n4 <-makeContrasts(
#   DNR_3.VEH_3 = DNR_3-VEH_3,
#   DOX_3.VEH_3 = DOX_3-VEH_3,
#   EPI_3.VEH_3 = EPI_3-VEH_3,
#   MTX_3.VEH_3 = MTX_3-VEH_3,
#   TRZ_3.VEH_3 = TRZ_3-VEH_3,
#   DNR_24.VEH_24 =DNR_24-VEH_24,
#   DOX_24.VEH_24= DOX_24-VEH_24,
#   EPI_24.VEH_24= EPI_24-VEH_24,
#   MTX_24.VEH_24= MTX_24-VEH_24,
#   TRZ_24.VEH_24= TRZ_24-VEH_24,
#   levels = mm_n4)

# vfit_n4 <- lmFit(y_n4, mm_n4)

# vfit_n4<- contrasts.fit(vfit_n4, contrasts=cm_n4)
#
# efit2_n45 <- eBayes(vfit_n4)

# saveRDS(efit2_n45,"data/filt_Peaks_efit2_n45.RDS")

results_n45 = decideTests(efit2_n45)
summary(results_n45)


```




### Evaluation of change in peaks

```{r toptable eval_n45}

V.DNR_3.top_n45= topTable(efit2_n45, coef=1, adjust.method="BH", number=Inf, sort.by="p")
V.DOX_3.top_n45= topTable(efit2_n45, coef=2, adjust.method="BH", number=Inf, sort.by="p")
V.EPI_3.top_n45= topTable(efit2_n45, coef=3, adjust.method="BH", number=Inf, sort.by="p")
V.MTX_3.top_n45= topTable(efit2_n45, coef=4, adjust.method="BH", number=Inf, sort.by="p")
V.TRZ_3.top_n45= topTable(efit2_n45, coef=5, adjust.method="BH", number=Inf, sort.by="p")
V.DNR_24.top_n45= topTable(efit2_n45, coef=6, adjust.method="BH", number=Inf, sort.by="p")
V.DOX_24.top_n45= topTable(efit2_n45, coef=7, adjust.method="BH", number=Inf, sort.by="p")
V.EPI_24.top_n45= topTable(efit2_n45, coef=8, adjust.method="BH", number=Inf, sort.by="p")
V.MTX_24.top_n45= topTable(efit2_n45, coef=9, adjust.method="BH", number=Inf, sort.by="p")
V.TRZ_24.top_n45= topTable(efit2_n45, coef=10, adjust.method="BH", number=Inf, sort.by="p")

# toplist_full_n45  <- list(V.DNR_3.top_n45, V.DOX_3.top_n45,V.EPI_3.top_n45,V.MTX_3.top_n45,V.TRZ_3.top_n45,V.DNR_24.top_n45, V.DOX_24.top_n45,V.EPI_24.top_n45,V.MTX_24.top_n45,V.TRZ_24.top_n45)
# names(toplist_full_n45) <- c("DNR_3", "DOX_3","EPI_3","MTX_3","TRZ_3","DNR_24", "DOX_24","EPI_24","MTX_24","TRZ_24")
# toplist_n45 <-map_df(toplist_full_n45, ~as.data.frame(.x), .id="trt_time")
# 
# toplist_n45 <- toplist_n45 %>%
#   separate(trt_time, into= c("trt","time"), sep = "_") %>%
#   mutate(trt=factor(trt, levels = c("DOX","EPI","DNR","MTX","TRZ"))) %>%
#   mutate(time = factor(time, levels = c("3", "24"), labels = c("3 hours", "24 hours")))
# saveRDS(toplist_n45, "data/toplist_n45.RDS")

```

### 3 hour boxplots without 4 and 5
```{r examine top3_3h_n45}
DNR_3_top3_n45 <- row.names(V.DNR_3.top_n45[1:3,])

log_filt_hc_n45 <- my_hc_filtered_counts_n45 %>% 
  cpm(., log=TRUE) %>% as.data.frame()

row.names(log_filt_hc_n45) <- row.names(my_hc_filtered_counts_n45)
log_filt_hc_n45 %>% 
  dplyr::filter(row.names(.) %in% DNR_3_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour DNR")+
  scale_fill_manual(values = drug_pal)
  
DOX_3_top3_n45 <- row.names(V.DOX_3.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% DOX_3_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour DOX")+
  scale_fill_manual(values = drug_pal)


EPI_3_top3_n45 <- row.names(V.EPI_3.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% EPI_3_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour EPI")+
  scale_fill_manual(values = drug_pal)

MTX_3_top3_n45 <- row.names(V.MTX_3.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% MTX_3_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour MTX")+
  scale_fill_manual(values = drug_pal)



TRZ_3_top3_n45 <- row.names(V.TRZ_3.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% TRZ_3_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 3 hour TRZ")+
  scale_fill_manual(values = drug_pal)

```


### 24 hour boxplots without 4 and 5



```{r 24hour n45}



DNR_24_top3_n45 <- row.names(V.DNR_24.top_n45[1:3,])

log_filt_hc_n45 <- my_hc_filtered_counts_n45 %>% 
  cpm(., log=TRUE) %>% as.data.frame()
row.names(log_filt_hc_n45) <- row.names(my_hc_filtered_counts_n45)
log_filt_hc_n45 %>% 
  dplyr::filter(row.names(.) %in% DNR_24_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour DNR")+
  scale_fill_manual(values = drug_pal)
  
DOX_24_top3_n45 <- row.names(V.DOX_24.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% DOX_24_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour DOX")+
  scale_fill_manual(values = drug_pal)


EPI_24_top3_n45 <- row.names(V.EPI_24.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% EPI_24_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour EPI")+
  scale_fill_manual(values = drug_pal)

MTX_24_top3_n45 <- row.names(V.MTX_24.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% MTX_24_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour MTX")+
  scale_fill_manual(values = drug_pal)



TRZ_24_top3_n45 <- row.names(V.TRZ_24.top_n45[1:3,])

log_filt_hc_n45 %>%  
  dplyr::filter(row.names(.) %in% TRZ_24_top3_n45) %>% 
  mutate(Peak = row.names(.)) %>% 
  pivot_longer(cols = !Peak, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("indv","trt","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  facet_wrap(Peak~.)+
  ggtitle("top 3 DAR in 24 hour TRZ")+
  scale_fill_manual(values = drug_pal)

```



### Volcano plots of peaks (n45)

```{r volcano plots n45}
library(cowplot)
efit2_n45 <- readRDS("data/filt_Peaks_efit2_n45.RDS")


# plot_filenames <- c("V.DNR_3.top","V.DOX_3.top","V.EPI_3.top","V.MTX_3.top",
#                     "V.TRZ_.top","V.DNR_24.top","V.DOX_24.top","V.EPI_24.top",
#                     "V.MTX_24.top","V.TRZ_24.top")
# plot_files <- c( V.DNR_3.top,V.DOX_3.top,V.EPI_3.top,V.MTX_3.top,
#                     V.TRZ_3.top,V.DNR_24.top,V.DOX_24.top,V.EPI_24.top,
#                     V.MTX_24.top,V.TRZ_24.top)

volcanosig <- function(df, psig.lvl) {
    df <- df %>% 
    mutate(threshold = ifelse(adj.P.Val > psig.lvl, "A", ifelse(adj.P.Val <= psig.lvl & logFC<=0,"B","C")))
      # ifelse(adj.P.Val <= psig.lvl & logFC >= 0,"B", "C")))
    ##This is where I could add labels, but I have taken out
    # df <- df %>% mutate(genelabels = "")
    # df$genelabels[1:topg] <- df$rownames[1:topg]
    
  ggplot(df, aes(x=logFC, y=-log10(adj.P.Val))) + 
    geom_point(aes(color=threshold))+
    # geom_text_repel(aes(label = genelabels), segment.curvature = -1e-20,force = 1,size=2.5,
    # arrow = arrow(length = unit(0.015, "npc")), max.overlaps = Inf) +
    #geom_hline(yintercept = -log10(psig.lvl))+
    xlab(expression("Log"[2]*" FC"))+
    ylab(expression("-log"[10]*"adj. P Value"))+
    scale_color_manual(values = c("black", "red","blue"))+
    theme_cowplot()+
    theme(legend.position = "none",
              plot.title = element_text(size = rel(1.5), hjust = 0.5),
              axis.title = element_text(size = rel(0.8))) 
}
#v1<- volcanosig(V.DA24.top, 0.01,0)
v1n <- volcanosig(V.DNR_3.top_n45, 0.01)+ ggtitle("Daunorubicin 3 hour")+ylim(0,16)
v2n <- volcanosig(V.DNR_24.top_n45, 0.01)+ ggtitle("Daunorubicin 24 hour")+ylab("")+ ylim(0,16)
v3n <- volcanosig(V.DOX_3.top_n45, 0.01)+ ggtitle("Doxorubicin 3 hour")+ ylim(0,16)
v4n <- volcanosig(V.DOX_24.top_n45, 0.01)+ ggtitle("Doxorubicin 24 hour")+ylab("")+ ylim(0,16)
v5n <- volcanosig(V.EPI_3.top_n45, 0.01)+ ggtitle("Epirubicin 3 hour")+ ylim(0,16)
v6n <- volcanosig(V.EPI_24.top_n45, 0.01)+ ggtitle("Epirubicin 24 hour")+ylab("")+ ylim(0,16)
v7n <- volcanosig(V.MTX_3.top_n45, 0.01)+ ggtitle("Mitoxantrone 3 hour")+ ylim(0,16)
v8n <- volcanosig(V.MTX_24.top_n45, 0.01)+ ggtitle("Mitoxantrone 24 hour")+ylab("")+ ylim(0,16)
v9n <- volcanosig(V.TRZ_3.top_n45, 0.01)+ ggtitle("Trastuzumab 3 hour")+ ylim(0,16)
v10n <- volcanosig(V.TRZ_24.top_n45, 0.01)+ ggtitle("Trastuzumab 24 hour")+ylab("")+ ylim(0,16)
# volcanoplot(efit2,coef = 10,style = "p-value",
#                           highlight = 8,
#                           names = efit2$genes$SYMBOL,
#                           hl.col = "red",xlab = "Log2 Fold Change",
#                           ylab = NULL,pch = 16,cex = 0.35,
#                           main = "Using Trastuzumab 24 hour data and volcanoplot function")
plot_grid(v1n,v2n,  rel_widths =c(.8,1))
plot_grid(v3n,v4n,  rel_widths =c(.8,1))
plot_grid(v5n,v6n,  rel_widths =c(.8,1))
plot_grid(v7n,v8n,  rel_widths =c(.8,1))
plot_grid(v9n,v10n,  rel_widths =c(.8,1))
# plot_grid(v1n)
```

### PCA analysis without 4 and 5


```{r filtering step wo 4-5}

my_hc_filtered_counts_n45 <- readRDS("data/my_hc_filt_counts_n45.RDS")
PCAmat_n45 <- my_hc_filtered_counts_n45 %>%
  cpm(., log = TRUE) %>% 
  as.matrix()

annotation_mat_n45  <-
  data.frame(timeset=colnames(PCAmat_n45 )) %>% 
  separate(timeset, into = c("indv","trt","time"), sep= "_") %>% 
  mutate(trt= case_match(trt, 'DX' ~'DOX', 'E'~'EPI', 'DA'~'DNR', 'M'~'MTX', 'T'~'TRZ', 'V'~'VEH',.default = trt)) %>% 
  mutate(indv = factor(indv, levels = c("1", "2", "3", "4", "5", "6"))) %>%
  mutate(time = factor(time, levels = c("3h", "24h"), labels= c("3 hours","24 hours"))) %>% 
  mutate(trt = factor(trt, levels = c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH"))) 

PCA_info_n45  <- (prcomp(t(PCAmat_n45 ), scale. = TRUE)) 
PCA_info_anno_n45  <- PCA_info_n45$x %>% cbind(.,annotation_mat_n45 )
# autoplot(PCA_info)
summary(PCA_info_n45)
# cpm(PCAmat, log=TRUE)
# pca_plot(PCA_info_n45 , col_var='trt', shape_var = 'time')
#         
# pca_plot(PCA_info_n45 , col_var='trt', shape_var = 'indv')


drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")

PCA_info_anno_n45  %>%
  ggplot(.,aes(x = PC1, y = PC2, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(cpm)"))+
  theme_bw()+
  guides( size =4)+
  labs(y = "PC 2 (13.81%)", x ="PC 1 (22.46%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))


PCA_info_anno_n45  %>%
  ggplot(.,aes(x = PC3, y = PC4, col=trt, shape=time, group=indv))+
  geom_point(size= 5)+
  scale_color_manual(values=drug_pal)+
   ggrepel::geom_text_repel(aes(label = indv))+
  #scale_shape_manual(name = "Time",values= c("3h"=0,"24h"=1))+
  ggtitle(expression("PCA of log"[2]*"(peaks)"))+
  theme_bw()+
  guides(col="none", size =4)+
  labs(y = "PC 4 (5.52%)", x ="PC 3 (8.2%)")+
  theme(plot.title=element_text(size= 14,hjust = 0.5),
        axis.title = element_text(size = 12, color = "black"))

```

### PCA of trt, time, indv w/o 4 and 5


```{r PCAtrt time indv n45}

facs <- c("indv", "trt", "time")
names(facs) <- c("Individual", "Treatment", "Time")
drug1 <- c("DOX","EPI", "DNR", "MTX", "TRZ", "VEH")##for changing shapes and colors
time <- rep(c("24h", "3h"),24) %>% factor(., levels = c("3h","24h"))
##gglistmaking
for (f in facs) {
  # PC1 v PC2
  pca_plot(PCA_info_anno_n45, col_var = f, shape_var = time,
           title = names(facs)[which(facs == f)])
  print(last_plot())
  
  # Plot f versus PC1 and PC2
  f_v_pc1 <- arrangeGrob(plot_versus_pc(PCA_info_anno_n45, 1, f))
  f_v_pc2 <- arrangeGrob(plot_versus_pc(PCA_info_anno_n45, 2, f))
  grid.arrange(f_v_pc1, f_v_pc2, ncol = 2, top = names(facs)[which(facs == f)])
  # summary(plot_versus_pc(PCA_info_anno_all, 1, f))
  # summary(plot_versus_pc(PCA_info_anno_all, 2, f))
 
}

```

### Magnitude of Response

```{r magresp_45}
toplist_n45 <- readRDS("data/toplist_n45.RDS")
toplist_n45 %>% 
  group_by(time, trt) %>% 
  mutate(sigcount = if_else(adj.P.Val < 0.05,'sig','notsig'))%>%
  count(sigcount) %>% 
  pivot_wider(id_cols = c(time,trt), names_from=sigcount, values_from=n) %>% 
  mutate(prop = sig/(sig+notsig)*100) %>% 
  mutate(prop=if_else(is.na(prop),0,prop)) %>% 
  ggplot(., aes(x=trt, y= prop))+
  geom_col(aes(fill=trt))+
  geom_text(aes(label = sprintf("%.2f",prop)),
            position=position_dodge(0.9),vjust=-.2 )+
  scale_fill_manual(values =drug_pal)+
  guides(fill=guide_legend(title = "Treatment"))+
  facet_wrap(~time)+#labeller = (time = facettimelabel) )+
  theme_bw()+
  xlab("")+
  ylab("Percentage DAR peaks")+
  theme_bw()+
  ggtitle("Percent DARs (adj. P value <0.05)")+
  scale_y_continuous(expand=expansion(c(0.02,.2)))+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        # axis.ticks = element_line(linewidth = 1.5),
        # axis.line = element_line(linewidth = 1.5),
        strip.background = element_rect(fill = "transparent"),
        axis.text.x = element_text(size = 8, color = "white", angle = 0),
        axis.text.y = element_text(size = 8, color = "black", angle = 0),
        strip.text.x = element_text(size = 12, color = "black", face = "bold"))

toplist_n45 %>% 
  group_by(time, trt) %>% 
  ggplot(., aes(x=trt, y=logFC))+
  geom_boxplot(aes(fill=trt))+
  ggpubr::fill_palette(palette =drug_pal)+
  guides(fill=guide_legend(title = "Treatment"))+
  # facet_wrap(sigcount~time)+
  theme_bw()+
  xlab("")+
  ylab(expression("Log"[2]*" fold change"))+
  theme_bw()+
  facet_wrap(~time)+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        # axis.ticks = element_line(linewidth = 1.5),
        # axis.line = element_line(linewidth = 1.5),
        strip.background = element_rect(fill = "transparent"),
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 12, color = "black", face = "bold"))



toplist_n45 %>% 
  group_by(time, trt) %>% 
  dplyr::filter(trt != "TRZ") %>%
  ggplot(., aes( x=(adj.P.Val)))+
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_bw()+
  ggtitle("adj.P.Value density by time/trt")+
  facet_wrap(time~trt)

toplist_n45 %>% 
  group_by(time, trt) %>% 
  # dplyr::filter(trt == "DOX") %>% 
  ggplot(., aes( x=(P.Value)))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_bw()+
  ggtitle("P.Value density by time/trt")+
  facet_wrap(time~trt)


```


