---
title: "SNP & TAD"
author: "Renee Matthews"
date: "2025-06-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library(ChIPpeakAnno)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)
library(readxl)
library(ComplexHeatmap)
library(gwascat)
library(liftOver)
```


### Loading data frames

```{r loading data}
### Pulling the all regions granges list from the motif list of lists
Motif_list_gr <- readRDS("data/Final_four_data/re_analysis/Motif_list_granges.RDS")
### no change motif_list_gr names so they do not overwrite the dataframes
names(Motif_list_gr) <- paste0(names(Motif_list_gr), "_gr")

### this pulls out the all_regions_gr granges frame I made previously with 155,557 regions listed
list2env(Motif_list_gr[10],envir= .GlobalEnv)


annotated_DARs<- readRDS("data/Final_four_data/re_analysis/DOX_DAR_annotated_peaks_chipannno.RDS")

Left_ventricle_TAD <- import(con = "C://Users/renee/Downloads/hg38.TADs/hg38/VentricleLeft_STL003_Leung_2015-raw_TADs.txt", format = "bed",genome="hg38")
mcols(Left_ventricle_TAD)$TAD_id <- paste0("TAD_", seq_along(Left_ventricle_TAD))


Schneider_all_SNPS <- read_delim("data/other_papers/Schneider_all_SNPS.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

Schneider_all_SNPS_df <- Schneider_all_SNPS %>%
  dplyr::rename("RSID"="#Uploaded_variation") %>% 
  dplyr::select(RSID,Location,SYMBOL,Gene, SOURCE) %>%
  distinct(RSID,Location,SYMBOL,.keep_all = TRUE) %>% 
  dplyr::rename("Close_SYMBOL"="SYMBOL") %>% 
  dplyr::filter(!str_starts(Location, "H")) %>% 
  separate_wider_delim(Location,delim=":",names=c("Chr","Coords")) %>% 
  separate_wider_delim(Coords,delim= "-", names= c("Start","End")) %>% 
  mutate(Chr=paste0("chr",Chr)) %>% 
  group_by(RSID) %>% 
  reframe(Chr=unique(Chr),
            Start=unique(Start),
            End=unique(End),
            Close_SYMBOL=paste(unique(Close_SYMBOL),collapse=";"),
            Gene=paste(Gene,collapse=";"),
            SOURCE=paste(SOURCE,collapse=";")
            ) %>% 
  GRanges() %>% as.data.frame 

schneider_gr <-Schneider_all_SNPS_df%>%
  dplyr::select(seqnames,start,end,RSID:SOURCE) %>%
  distinct() %>% 
  GRanges()

toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()
all_results_pivot <- all_results %>% 
dplyr::select(genes,logFC,source) %>% 
  pivot_wider(., id_cols = genes, names_from = source, values_from = logFC) %>% 
  dplyr::select(genes,DOX_3,EPI_3,DNR_3,MTX_3,TRZ_3,DOX_24,EPI_24,DNR_24,MTX_24,TRZ_24)


toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))

Assigned_genes_toPeak <- annotated_DARs$DOX_24 %>% as.data.frame() %>% 
  dplyr::select(mcols.genes,annotation, geneId, distanceToTSS) %>% 
  dplyr::rename("Peakid"=mcols.genes)

RNA_results <-
toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  tidyr::unite("sample",time, id) %>% 
  pivot_wider(., id_cols = c(ENTREZID,SYMBOL),names_from = sample, values_from = logFC) %>% 
  rename_with(~ str_replace(., "hours", "RNA"))

Peak_gene_RNA_LFC <- Assigned_genes_toPeak %>% 
  left_join(., RNA_results, by =c("geneId"="ENTREZID"))


entrez_ids <- Assigned_genes_toPeak$geneId  


gene_info <- AnnotationDbi::select(
  org.Hs.eg.db,
  keys = entrez_ids,
  columns = c("SYMBOL"),
  keytype = "ENTREZID"
)
gene_info_collapsed <- gene_info %>%
  group_by(ENTREZID) %>%
  summarise(SYMBOL = paste(unique(SYMBOL), collapse = ","), .groups = "drop")
DOX_DAR_24hr_table <- annotated_DARs$DOX_24 %>% 
  as.data.frame()

Top2b_peaks <- import(con="data/other_papers/ChIP3_TOP2B_CM_87-1.bed",format = "bed",genome="hg38")

```



### Enrichment test of sig DAR and non-sig DAR of DOX within SNP-containing TADS
```{r}

test_ol <- join_overlap_intersect(Left_ventricle_TAD, schneider_gr)
df <- as.data.frame(test_ol, row.names = NULL)
TAD_SNP_ol <- test_ol %>% as.data.frame() %>% 
  distinct(TAD_id, RSID)
peak_ol <- join_overlap_intersect(all_regions_gr, Left_ventricle_TAD)

TAD_SNP_Peak_ol <- peak_ol %>% 
  as.data.frame() %>% 
  dplyr::filter(TAD_id %in% TAD_SNP_ol$TAD_id)
snp_ol <- join_overlap_inner(schneider_gr, Left_ventricle_TAD)
TAD_peak_ol <- peak_ol %>% 
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE)

left_ventricle_ol <- join_overlap_inner(all_regions_gr ,Left_ventricle_TAD) %>% 
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE) %>% 
  dplyr::filter(TAD_id %in% TAD_SNP_ol$TAD_id)

peak_df <- as.data.frame(left_ventricle_ol)
SNP_df <- as.data.frame(snp_ol)

peak_snp_pairs <- inner_join(peak_df, SNP_df, by = "TAD_id", suffix = c(".peak", ".snp")) %>%
  mutate(
    peak_center = (start.peak + end.peak) / 2,
    distance = abs(peak_center - start.snp)  # or any metric you prefer
  )




```

```{r TAD colors}
reds <- colorRampPalette(brewer.pal(9, "Reds")[3:9])(12)
greens <- colorRampPalette(brewer.pal(9, "Greens")[3:9])(12)
blues <- colorRampPalette(brewer.pal(9, "Blues")[3:9])(12)
purples <- colorRampPalette(brewer.pal(9, "Purples")[3:9])(12)
oranges <- colorRampPalette(brewer.pal(9, "Oranges")[3:9])(12)



tads <- unique(peak_snp_pairs$TAD_id)
num_tads <- length(tads)

color_spectrum <- c(reds, greens, blues, purples, oranges)[1:num_tads]

if (num_tads > length(color_spectrum)) {
  stop("Not enough colors for TADs. Add more palettes.")
}
tad_colors <- color_spectrum[1:num_tads]
names(tad_colors) <- tads  # Assign color names to TAD IDs


#ha <- HeatmapAnnotation(TAD = df$TAD_id, col = list(TAD = tad_colors))

```

```{r}
Top2b_overlap_regions <-join_overlap_inner(all_regions_gr ,Top2b_peaks) %>%
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE) 
```


```{r}
DOX_24_DAR <- as.data.frame(annotated_DARs$DOX_24)
EPI_24_DAR <- as.data.frame(annotated_DARs$EPI_24)
DNR_24_DAR <- as.data.frame(annotated_DARs$DNR_24)
MTX_24_DAR <- as.data.frame(annotated_DARs$MTX_24)

DOX_3_DAR <- as.data.frame(annotated_DARs$DOX_3)
EPI_3_DAR <- as.data.frame(annotated_DARs$EPI_3)
DNR_3_DAR <- as.data.frame(annotated_DARs$DNR_3)
MTX_3_DAR <- as.data.frame(annotated_DARs$MTX_3)


TAD_count_df <- DOX_24_DAR %>% 
  dplyr::select(mcols.genes, mcols.adj.P.Val,annotation:distanceToTSS) %>% 
  mutate(sig_24=if_else(mcols.adj.P.Val<0.05,"sig","not_sig")) %>% 
  mutate(sig_24=factor(sig_24, levels = c("sig","not_sig"))) %>% 
  mutate(TAD_all_status=if_else(mcols.genes %in% peak_ol$Peakid,"TAD_peak","not_TAD_peak")) %>% 
  mutate(SNP_TAD_status= if_else(mcols.genes %in% TAD_SNP_Peak_ol$Peakid,"SNP_TAD","not_SNP_TAD")) %>%
  mutate(Top2b_peak= if_else(mcols.genes %in% Top2b_overlap_regions$Peakid, "TOP2B_peak","not_TOP2B_peak"))
  
# TAD_count_df %>% #dplyr::filter(TAD_all_status=="TAD_peak") %>% 
#   group_by(sig_24,SNP_TAD_status,TAD_all_status) %>% 
#   tally 

print("Odds ratio  testing proportion SNP-containing TADs of sig-DOX DARs vs non-sig DARs at 24 hours")
TAD_count_df %>% dplyr::filter(TAD_all_status=="TAD_peak") %>% 
  group_by(sig_24,SNP_TAD_status) %>% 
  tally %>% 
  pivot_wider(., id_cols = sig_24, names_from = SNP_TAD_status, values_from = n) %>% 
  column_to_rownames( "sig_24") %>% as.matrix() %>% 
  epitools::oddsratio(method = "wald")



TAD_count_df %>% 
  dplyr::filter(TAD_all_status=="TAD_peak") %>% 
   group_by(sig_24,SNP_TAD_status) %>% 
  tally ()%>% 
   mutate(sig_24=factor(sig_24, levels = c("sig","not_sig"))) %>% 
  ggplot(.,aes(x=sig_24, y= n,fill=SNP_TAD_status))+
  geom_col(position="fill")+
  theme_bw()+
  ggtitle("Proportion of significant regions by 24 hours")+
  ylab("proportion")



```
### Proportion of DARs that overlap TOP2B peaks in a TAD
```{r}
TAD_count_df %>% 
  dplyr::filter((TAD_all_status=="TAD_peak")) %>% 
  dplyr::filter(SNP_TAD_status=="SNP_TAD") %>% 
  group_by(SNP_TAD_status, Top2b_peak, sig_24) %>% 
  tally() %>% 
  pivot_wider(., id_cols=sig_24, names_from = Top2b_peak, values_from = n) %>% 
  print() %>% 
  column_to_rownames("sig_24") %>% 
  fisher.test()
```

### Calculating Distance to TAD-SNP from peak  
#### DOX 24 hours
```{r}
DOX_DAR_sig <- DOX_24_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")
DOX_DAR_sig_3 <- DOX_3_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")

EPI_DAR_sig <- EPI_24_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")

EPI_DAR_sig_3 <- EPI_3_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")

DNR_DAR_sig <- DNR_24_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")
DNR_DAR_sig_3 <- DNR_3_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")

MTX_DAR_sig <- MTX_24_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")
MTX_DAR_sig_3 <- MTX_3_DAR %>%
  dplyr::filter(mcols.adj.P.Val<0.05) %>% 
  distinct (mcols.genes) %>% 
  dplyr::rename("Peakid"="mcols.genes")

snp_tad_df <-
  join_overlap_inner(schneider_gr, Left_ventricle_TAD) %>%
  as_tibble() %>%
  dplyr::select(RSID, snp_start = start, snp_chr = seqnames, TAD_id)


peak_tad_df <-
join_overlap_inner(all_regions_gr, Left_ventricle_TAD) %>%
  as_tibble() %>%
  dplyr::select(Peakid, peak_start = start, peak_chr = seqnames, TAD_id)

peak_snp_pairs <- peak_tad_df %>%
  inner_join(snp_tad_df, by = "TAD_id")


peak_snp_pairs_dist <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_24= if_else(Peakid %in% DOX_DAR_sig$Peakid, "sig","not_sig"))



peak_snp_pairs_dist %>% 
  mutate(sig_24=factor(sig_24, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_24, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")+
  ggtitle("DOX 24 hour distances of DAR-SNP pairs and non-DAR-SNP pairs")

wilcox.test(distance ~ sig_24, data = peak_snp_pairs_dist)

Cardiotox_gwas_df <- peak_snp_pairs_dist %>% 
  dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)


Cardiotox_gwas_collaped_df <-
peak_snp_pairs_dist %>% 
  dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  group_by(Peakid, peak_chr, peak_start, TAD_id, sig_24) %>%
  summarise(
    min_distance = min(distance),
    mean_distance = mean(distance),
    snp_list = paste(unique(RSID), collapse = ","),
    .groups = "drop"
  ) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  left_join(., Peak_gene_RNA_LFC, by=c("Peakid"="Peakid")) %>% 
  left_join(.,gene_info_collapsed, by=c("geneId"="ENTREZID")) %>% 
  mutate(SYMBOL=if_else(is.na(SYMBOL.x),SYMBOL.y,if_else(SYMBOL.x==SYMBOL.y, SYMBOL.x,paste0(SYMBOL.x,"_",SYMBOL.y)))) %>% 
  tidyr::unite(., name,Peakid,SYMBOL,snp_list) %>% 
  mutate(snp_dist=case_when(min_distance <2000 ~"2kb",
                            min_distance > 2000 & min_distance<20000 ~ "20kb",
                            min_distance >20000 ~">20kb"))
  

```

```{r DOX 3 hour snp tad}
peak_snp_pairs_dist_DOX_3 <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_3= if_else(Peakid %in% DOX_DAR_sig_3$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_DOX_3 %>% 
  mutate(sig_3=factor(sig_3, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_3, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")

wilcox.test(distance ~ sig_3, data = peak_snp_pairs_dist_DOX_3)

Cardiotox_gwas_EPI <- peak_snp_pairs_dist_DOX_3 %>% 
  dplyr::filter(sig_3=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)


```

Looking at SNPs that directly overlap DARs
```{r}
snp_peak_ol <- join_overlap_inner(all_regions_gr,schneider_gr)
  SNP_DAR_overlap_direct <- snp_peak_ol %>% 
    as.data.frame() %>% 
      mutate(Dox_24=if_else(Peakid %in% DOX_DAR_sig$Peakid,"yes","no")) %>% 
  mutate(Epi_24=if_else(Peakid %in% EPI_DAR_sig$Peakid,"yes","no")) %>% 
  mutate(Dnr_24=if_else(Peakid %in% DNR_DAR_sig$Peakid,"yes","no")) %>% 
  mutate(MTx_24=if_else(Peakid %in% MTX_DAR_sig$Peakid,"yes","no")) %>% 
    mutate(Dox_3=if_else(Peakid %in% DOX_DAR_sig_3$Peakid,"yes","no")) %>% 
  mutate(Epi_3=if_else(Peakid %in% EPI_DAR_sig_3$Peakid,"yes","no")) %>% 
  mutate(Dnr_3=if_else(Peakid %in% DNR_DAR_sig_3$Peakid,"yes","no")) %>% 
  mutate(Mtx_3=if_else(Peakid %in% MTX_DAR_sig_3$Peakid,"yes","no")) %>% 
    dplyr::select(Peakid,RSID,Dox_24:Mtx_3) 
  
```


#### EPI 24 hours  

```{r EPI SNPpairs}
peak_snp_pairs_dist_EPI <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_24= if_else(Peakid %in% EPI_DAR_sig$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_EPI %>% 
  mutate(sig_24=factor(sig_24, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_24, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")

wilcox.test(distance ~ sig_24, data = peak_snp_pairs_dist)

Cardiotox_gwas_EPI <- peak_snp_pairs_dist_EPI %>% 
  dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```

```{r EPI SNPpairs 3hr}
peak_snp_pairs_dist_EPI_3 <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_3= if_else(Peakid %in% EPI_DAR_sig_3$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_EPI_3 %>% 
  mutate(sig_3=factor(sig_3, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_3, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")

wilcox.test(distance ~ sig_3, data = peak_snp_pairs_dist_EPI_3)

Cardiotox_gwas_EPI_3 <- peak_snp_pairs_dist_EPI_3 %>% 
  dplyr::filter(sig_3=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```



#### DNR 24 hours 

```{r DNR SNPpairs}
peak_snp_pairs_dist_DNR <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_24= if_else(Peakid %in% DNR_DAR_sig$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_DNR %>% 
  mutate(sig_24=factor(sig_24, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_24, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")+
  ggtitle("DNR 24 hour distances of DAR-SNP pairs and non-DAR-SNP pairs")

wilcox.test(distance ~ sig_24, data = peak_snp_pairs_dist)

Cardiotox_gwas_DNR <- peak_snp_pairs_dist_DNR %>% 
  dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```

```{r DNR SNPpairs 3hr}
peak_snp_pairs_dist_DNR_3 <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_3= if_else(Peakid %in% DNR_DAR_sig_3$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_DNR_3 %>% 
  mutate(sig_3=factor(sig_3, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_3, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")+
  ggtitle("3 hour DNR")

wilcox.test(distance ~ sig_3, data = peak_snp_pairs_dist_DNR_3)

Cardiotox_gwas_DNR_3 <- peak_snp_pairs_dist_DNR_3 %>% 
  dplyr::filter(sig_3=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```


#### MTX 24 hours 

```{r MTX SNPpairs}
peak_snp_pairs_dist_MTX <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_24= if_else(Peakid %in% MTX_DAR_sig$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_MTX %>% 
  mutate(sig_24=factor(sig_24, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_24, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")+
  ggtitle("MTX 24 hour distances of DAR-SNP pairs and non-DAR-SNP pairs")

wilcox.test(distance ~ sig_24, data = peak_snp_pairs_dist)

Cardiotox_gwas_MTX <- peak_snp_pairs_dist_MTX %>% 
  dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```


```{r MTX SNPpairs 3hr}
peak_snp_pairs_dist_MTX_3 <- peak_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) %>% 
  mutate(sig_3= if_else(Peakid %in% MTX_DAR_sig_3$Peakid, "sig","not_sig"))

peak_snp_pairs_dist_MTX_3 %>% 
  mutate(sig_3=factor(sig_3, levels= c("sig","not_sig"))) %>% 
  ggplot(., aes(x= sig_3, y=distance))+
  geom_boxplot()+
  theme_bw()+
  geom_signif(comparisons = list(c("sig", "not_sig")), 
              map_signif_level = FALSE, test = "wilcox.test")+
  ggtitle("3 hour MTX")

wilcox.test(distance ~ sig_3, data = peak_snp_pairs_dist_MTX_3)

Cardiotox_gwas_MTX_3 <- peak_snp_pairs_dist_MTX_3 %>% 
  dplyr::filter(sig_3=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID)



```

### Creating SNP_TAD distance DF

For combining the above 24 hour trt-distance to SNP data frames for box-plots

```{r Boxplot combo, fig.width=7}

drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
SNP_TAD_dist_DF <- bind_rows((peak_snp_pairs_dist_MTX %>% 
             mutate(trt="MTX")),
          (peak_snp_pairs_dist %>%
               mutate(trt="DOX"))) %>% 
  bind_rows(.,(peak_snp_pairs_dist_EPI %>% 
                 mutate(trt="EPI"))) %>% 
  bind_rows(.,(peak_snp_pairs_dist_DNR %>% 
                 mutate(trt="DNR"))) %>% 
  mutate(trt=factor(trt,levels=c("DOX","EPI","DNR","MTX"))) %>% 
   mutate(sig_24=factor(sig_24, levels= c("sig","not_sig"))) 

SNP_TAD_dist_DF%>% 
  ggplot(., aes(x= interaction(sig_24,trt), y=distance))+
  geom_boxplot(aes(fill=trt))+
  theme_bw()+
  geom_signif(comparisons = list(c("sig.DOX", "not_sig.DOX"),
                                 c("sig.EPI","not_sig.EPI"),
                                 c("sig.DNR", "not_sig.DNR"),
                                 c("sig.MTX", "not_sig.MTX")),
                              # step_increase = 0.1, 
              map_signif_level = FALSE, 
              test = "wilcox.test")+
  ggtitle("ALL dist 24 hours")+
  scale_fill_manual(values=drug_pal)
```

```{r Boxplot combo 3hour, fig.width=7}
SNP_TAD_dist_DF_3 <- bind_rows((peak_snp_pairs_dist_MTX_3 %>% 
             mutate(trt="MTX")),
          (peak_snp_pairs_dist_DOX_3 %>%
               mutate(trt="DOX"))) %>% 
  bind_rows(.,(peak_snp_pairs_dist_EPI_3 %>% 
                 mutate(trt="EPI"))) %>% 
  bind_rows(.,(peak_snp_pairs_dist_DNR_3 %>% 
                 mutate(trt="DNR"))) %>% 
  mutate(trt=factor(trt,levels=c("DOX","EPI","DNR","MTX"))) %>% 
   mutate(sig_3=factor(sig_3, levels= c("sig","not_sig"))) 

SNP_TAD_dist_DF_3%>% 
  ggplot(., aes(x= interaction(sig_3,trt), y=distance))+
  geom_boxplot(aes(fill=trt))+
  theme_bw()+
  geom_signif(comparisons = list(c("sig.DOX", "not_sig.DOX"),
                                 c("sig.EPI","not_sig.EPI"),
                                 c("sig.DNR", "not_sig.DNR"),
                                 c("sig.MTX", "not_sig.MTX")),
                              # step_increase = 0.1, 
              map_signif_level = FALSE, 
              test = "wilcox.test")+
  ggtitle("ALL dist 3 hours")+
  scale_fill_manual(values=drug_pal)
```



### Alternative of heatmap plot (supplemental figure 19) 
```{r, cardiotox heatmapnon-sig plus sig, fig.height=14, fig.width=10}

ATAC_all_adj.pvals <- all_results%>%
dplyr::select(source,genes,adj.P.Val) %>%
    pivot_wider(id_cols=genes, values_from = adj.P.Val, names_from = source)
# saveRDS(ATAC_all_adj.pvals,"data/Final_four_data/re_analysis/ATAC_all_adj_pvals.RDS")
sig_mat_cardiotox <- ATAC_all_adj.pvals %>%
  dplyr::filter(genes %in% peak_snp_pairs_dist$Peakid) %>% 
  left_join(peak_snp_pairs_dist, by=c("genes"="Peakid")) %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
   group_by(genes, peak_chr, peak_start, TAD_id, sig_24) %>%
  summarise(
    min_distance = min(distance),
    mean_distance = mean(distance),
    snp_list = paste(unique(RSID), collapse = ","),
    .groups = "drop"
  ) %>% 
  left_join(ATAC_all_adj.pvals) %>% 
  tidyr::unite(., name,genes,snp_list) %>% 
  dplyr::select(name, DNR_3:TRZ_24) %>% 
  column_to_rownames("name") %>% 
  as.matrix()

AR_Cardiotox_gwas_collaped_df <-
peak_snp_pairs_dist %>% 
  # dplyr::filter(sig_24=="sig") %>% 
  group_by(TAD_id,RSID) %>% 
  slice_min(order_by = distance, with_ties = FALSE) %>%
  ungroup() %>% 
  arrange(snp_chr,snp_start) %>% 
  group_by(Peakid, peak_chr, peak_start, TAD_id, sig_24) %>%
  summarise(
    min_distance = min(distance),
    mean_distance = mean(distance),
    snp_list = paste(unique(RSID), collapse = ","),
    .groups = "drop"
  ) %>% 
  left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,snp_list) %>%
  mutate(snp_dist=case_when(min_distance <2000 ~"2kb",
                            min_distance > 2000 & min_distance<20000 ~ "20kb",
                            min_distance >20000 ~">20kb"))


Cardotox_mat_2 <-   AR_Cardiotox_gwas_collaped_df %>%
  dplyr::select(name,DOX_3:TRZ_24) %>% 
  column_to_rownames("name") %>% 
  as.matrix()

annot_map_df_2 <- AR_Cardiotox_gwas_collaped_df %>% 
  dplyr::select(name,snp_dist,sig_24) %>% 
  column_to_rownames("name") 
annot_map_2 <-
  ComplexHeatmap::rowAnnotation(
    snp_dist=AR_Cardiotox_gwas_collaped_df$snp_dist,
    TAD_id=AR_Cardiotox_gwas_collaped_df$TAD_id,
    DOX_24hr_DAR=AR_Cardiotox_gwas_collaped_df$sig_24,
    col= list(snp_dist=c("2kb"="goldenrod4",
                               "20kb"="pink",
                               ">20kb"="tan2"),
              TAD_id=tad_colors))
# all.equal(rownames(sig_mat_cardiotox), rownames(Cardotox_mat_2))
# all.equal(colnames(sig_mat_cardiotox), colnames(Cardotox_mat_2))
# 
# setdiff(colnames(sig_mat_cardiotox), colnames(Cardotox_mat_2))
# setdiff(colnames(Cardotox_mat_2), colnames(sig_mat_cardiotox))
# 
# intersect(colnames(sig_mat_cardiotox), colnames(Cardotox_mat_2))
# setdiff(colnames(sig_mat_cardiotox), colnames(Cardotox_mat_2))
# setdiff(colnames(Cardotox_mat_2), colnames(sig_mat_cardiotox))

simply_map_lfc_2 <- ComplexHeatmap::Heatmap(Cardotox_mat_2,
                        left_annotation = annot_map_2,
                        show_row_names = TRUE,
                       row_names_max_width= ComplexHeatmap::max_text_width(rownames(Cardotox_mat_2),                                                        gp=gpar(fontsize=14)),
                        heatmap_legend_param = list(direction = "horizontal"),
                       
                        show_column_names = TRUE,
                        cluster_rows = FALSE,
                        cluster_columns = FALSE,
                        cell_fun = function(j, i, x, y, width, height, fill) {
  rowname <- rownames(Cardotox_mat_2)[i]
  colname <- colnames(Cardotox_mat_2)[j]
  if (!is.na(sig_mat_cardiotox[rowname, colname]) &&
      sig_mat_cardiotox[rowname, colname] < 0.05) {
    grid.text("*", x, y, gp = gpar(fontsize = 20))
  }
})




ComplexHeatmap::draw(simply_map_lfc_2, 
     merge_legend = TRUE, 
     heatmap_legend_side = "left", 
    annotation_legend_side = "left")



```



### Accessibility changes of SNP- directly overlapping DARs
```{r}
drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
raw_counts <- read_delim("data/Final_four_data/re_analysis/Raw_unfiltered_counts.tsv",delim="\t") %>% 
  column_to_rownames("Peakid") %>% 
  as.matrix()

lcpm <- cpm(raw_counts, log= TRUE)
  ### for determining the basic cutoffs
filt_raw_counts <- raw_counts[rowMeans(lcpm)> 0,]

filt_raw_counts_noY <- filt_raw_counts[!grepl("chrY",rownames(filt_raw_counts)),]

ATAC_adj.pvals <-all_results %>%
dplyr::select(source,genes,adj.P.Val) %>%
    dplyr::filter(genes %in% SNP_DAR_overlap_direct$Peakid) %>%
    separate(source, into = c("trt", "time")) %>% 
    mutate(
    time = paste0(time, "h"),  # convert "3" → "3h"
    trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ")),
    group=paste0(trt,"_",time)) %>% 
  mutate(group=factor(group,levels = c("DOX_3h", "EPI_3h", "DNR_3h", "MTX_3h", "TRZ_3h", "VEH_3h",
        "DOX_24h", "EPI_24h", "DNR_24h", "MTX_24h", "TRZ_24h", "VEH_24h"))) %>% 
  dplyr::rename("Peakid"=genes)

  
```


```{r}
ATAC_counts_lcpm <- filt_raw_counts_noY %>%
  cpm(., log = TRUE) %>% 
  as.data.frame() %>% 
  rownames_to_column("Peakid")
```


```{r}
for (peak in SNP_DAR_overlap_direct$Peakid) {
  PEAK <- SNP_DAR_overlap_direct$Peakid[SNP_DAR_overlap_direct$Peakid == peak]

  # Prep expression data
  peak_expr <- ATAC_counts_lcpm %>%
    filter(Peakid == peak) %>%
    pivot_longer(cols = !Peakid, names_to = "sample", values_to = "lcpm") %>%
    separate(sample, into = c("ind", "trt", "time")) %>%
    mutate(
      time = paste0(time),  # if already "3h"/"24h"
      group = paste0(trt, "_", time),
      group = factor(group, levels = c(
        "DOX_3h", "EPI_3h", "DNR_3h", "MTX_3h", "TRZ_3h", "VEH_3h",
        "DOX_24h", "EPI_24h", "DNR_24h", "MTX_24h", "TRZ_24h", "VEH_24h"
      ))
    )

  # Get peak-specific p-values
  peak_pvals <- ATAC_adj.pvals %>%
    filter(Peakid==peak)

  # Merge in p-values by group
  peak_plot_data <- left_join(peak_expr, peak_pvals, by = c("Peakid", "group", "time"))

  # Create label position below box
  label_positions <- peak_plot_data %>%
    group_by(group) %>%
    summarise(y = min(lcpm, na.rm = TRUE) - 0.5, .groups = "drop")

  peak_plot_data <- left_join(peak_plot_data, label_positions, by = "group")
  peak_plot_data <- peak_plot_data %>%
  separate(group, into = c("trt", "time"), sep = "_", remove = FALSE)

  # Plot
  peak_plot <- ggplot(peak_plot_data, aes(x = group, y = lcpm)) +
    geom_boxplot(aes(fill = trt)) +
    geom_text(
      aes(y = y,
          label = ifelse(trt != "VEH" & !is.na(adj.P.Val),
                         paste0("", signif(adj.P.Val, 2)),
                         "")),
      size = 3,
      vjust = 1.2
    ) +
    scale_fill_manual(values = drug_pal) +
    theme_bw() +
    ggtitle(paste0("ATAC Log2cpm of ", PEAK)) +
    ylab("log2 cpm ATAC") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot(peak_plot)
}
```


```{r}

filt_raw_counts_noY %>%
  cpm(., log = TRUE) %>% 
  as.data.frame() %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::filter(Peakid %in% SNP_DAR_overlap_direct$Peakid) %>% 
  pivot_longer(., cols= !Peakid, names_to = "sample",values_to = "log2cpm") %>% 
  separate_wider_delim(, cols=sample, names =c("ind","trt","time"),delim="_",cols_remove = FALSE) %>% 
  mutate(
      time = factor(time, levels = c("3h", "24h")),
      trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ", "VEH"))
    ) %>%
    ggplot(aes(x = time, y = log2cpm)) +
    geom_boxplot(aes(fill = trt)) +
    scale_fill_manual(values = drug_pal) +
    theme_bw() +
  facet_wrap(~Peakid, scales="free_y")+
    ylab("log2 cpm ATAC regions") 
```
```{r, eval=FALSE, include=FALSE}
DOX_dar_diff <- DOX_DAR_24hr_table %>% 
  dplyr::filter(mcols.adj.P.Val<0.05)%>% 
  dplyr::rename("Peakid"=mcols.genes)
```


```{r DARS loci}


# TAD_SNP_Peak_ol %>% 
#   dplyr::filter(TAD_id =="TAD_102") %>% 
#   dplyr::filter( Peakid%in%DOX_DAR_sig$Peakid)

filt_raw_counts_noY %>%
  cpm(., log = TRUE) %>% 
  as.data.frame() %>% 
  rownames_to_column("Peakid") %>% 
  dplyr::filter(Peakid =="chr1.173823770.173825267") %>% 
  pivot_longer(., cols= !Peakid, names_to = "sample",values_to = "log2cpm") %>% 
  separate_wider_delim(, cols=sample, names =c("ind","trt","time"),delim="_",cols_remove = FALSE) %>% 
  mutate(
      time = factor(time, levels = c("3h", "24h")),
      trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ", "VEH"))
    ) %>%
    ggplot(aes(x = time, y = log2cpm)) +
    geom_boxplot(aes(fill = trt)) +
    scale_fill_manual(values = drug_pal) +
    theme_bw() +
  facet_wrap(~Peakid, scales="free_y")+
    ylab("log2 cpm ATAC regions") 
```



### SNP DAR direct overlap heatmap


```{r}
SNP_DAR_overlap_mat <-
SNP_DAR_overlap_direct %>% 
  dplyr::select(Peakid,RSID) %>% 
  left_join(., snp_tad_df,by= c("RSID"="RSID")) %>% 
  dplyr::select(Peakid, TAD_id, RSID) %>% 
 left_join(., all_results_pivot, by=c("Peakid"="genes")) %>% 
  tidyr::unite(., name,Peakid,RSID) 

SNP_DAR_sig_mat <-   SNP_DAR_overlap_direct %>% 
    dplyr::select(Peakid,RSID) %>% 
  left_join(., snp_tad_df,by= c("RSID"="RSID")) %>% 
  dplyr::select(Peakid, TAD_id, RSID) %>% 
    left_join(., ATAC_all_adj.pvals, by=c("Peakid"="genes")) %>% 
    tidyr::unite(., name,Peakid,RSID) %>% 
    column_to_rownames("name") %>% 
  as.matrix()


Cardotox_mat_3 <-   SNP_DAR_overlap_mat %>%
  dplyr::select(name,DOX_3:TRZ_24) %>% 
  column_to_rownames("name") %>% 
  as.matrix()

annot_map_df_3 <- SNP_DAR_overlap_mat %>% 
  dplyr::select(name,TAD_id) %>% 
  column_to_rownames("name") 
annot_map_3 <-
  ComplexHeatmap::rowAnnotation(TAD_id=SNP_DAR_overlap_mat$TAD_id)


simply_map_lfc_3 <- ComplexHeatmap::Heatmap(Cardotox_mat_3,
                        #                   col = col_fun,
                        left_annotation = annot_map_3,
                        column_title="Cardiotox SNP direct overlaps",
                        show_row_names = TRUE,
                       row_names_max_width= ComplexHeatmap::max_text_width(rownames(Cardotox_mat_3),                                                        gp=gpar(fontsize=14)),
                        heatmap_legend_param = list(direction = "horizontal"),
                        show_column_names = TRUE,
                        cluster_rows = FALSE,
                        cluster_columns = FALSE,
                       cell_fun = function(j, i, x, y, width, height, fill) {
  rowname <- rownames(Cardotox_mat_3)[i]
  colname <- colnames(Cardotox_mat_3)[j]

  if (!is.na(SNP_DAR_sig_mat[rowname, colname]) &&
      SNP_DAR_sig_mat[rowname, colname] < 0.05) {
    grid.text("*", x, y, gp = gpar(fontsize = 20))
  }
})




ComplexHeatmap::draw(simply_map_lfc_3, 
     merge_legend = TRUE, 
      
     heatmap_legend_side = "left", 
    annotation_legend_side = "left")


```

```{r, eval=FALSE, include=FALSE}

### this was for later data retrieval
ATAC_all_adj.pvals %>% 
  dplyr::filter(genes=="chr14.76772505.76773251
"|genes=="chr19.46300600.46301262")

toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))
toplistall_RNA %>% 
  tidyr::unite(group, time,id) %>% 
  dplyr::select(group:SYMBOL,adj.P.Val) %>% 
  pivot_wider(id_cols = c(ENTREZID,SYMBOL), names_from = group,values_from = adj.P.Val) %>% 
  dplyr::filter(SYMBOL=="CDKN1A")



H3K27_toplist <- readRDS("data/Final_four_data/re_analysis/Toptable_results_H3K27ac_data.RDS")

K27_results  <- H3K27_toplist %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

K27_results %>% 
  dplyr::select(source,genes,adj.P.Val) %>% 
  pivot_wider(id_cols = genes, names_from = source,values_from = adj.P.Val) %>% 
  dplyr::filter(genes=="chr6.36674959.36687167")

  
```

