---
title: "TE_analysis_DOX_DAR"
author: "Renee Matthews"
date: "2025-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)

```

Loading repeatmasker data:

```{r repeatmasker df}
repeatmasker <- read.delim("data/other_papers/repeatmasker.tsv")
```

Subsetting repeatmasker for analysis by class/family
```{r subset repeatmasker}
reClass_list <- repeatmasker %>% 
  distinct(repClass)

Line_repeats <- repeatmasker %>% 
  dplyr::filter(repClass == "LINE") %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

Sine_repeats <- repeatmasker %>% 
  dplyr::filter(repClass == "SINE") %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

LTR_repeats <- repeatmasker %>% 
  dplyr::filter(repClass == "LTR") %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

DNA_repeats <- repeatmasker %>% 
  dplyr::filter(repClass == "DNA") %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

retroposon_repeats <- repeatmasker %>% 
  dplyr::filter(repClass == "Retroposon") %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

all_TEs_gr <- repeatmasker %>% 
 makeGRangesFromDataFrame(., keep.extra.columns = TRUE, seqnames.field = "genoName", start.field = "genoStart", end.field = "genoEnd",starts.in.df.are.0based=TRUE)

```

### Initial overlaps of TEs vs all regions (155,557)


```{r loading toptable-covert to granges}

toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")
all_regions <- toptable_results$DOX_24$genes

Collapsed_peaks <- read_delim("data/Final_four_data/collapsed_new_peaks.txt",
                              delim = "\t", 
                              escape_double = FALSE, 
                              trim_ws = TRUE)

Col_TSS_data_gr <- Collapsed_peaks %>% 
  dplyr::filter(chr != "chrY") %>%
  dplyr::filter(Peakid %in% all_regions) %>% 
  GRanges()

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

my_DOX_data <- all_results %>% 
  dplyr::filter(source=="DOX_3"|source=="DOX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_EPI_data <- all_results %>% 
  dplyr::filter(source=="EPI_3"|source=="EPI_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_DNR_data <- all_results %>% 
  dplyr::filter(source=="DNR_3"|source=="DNR_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_MTX_data <- all_results %>% 
  dplyr::filter(source=="MTX_3"|source=="MTX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))


```

### Overlapping all peaks with TEs
```{r}
overlap_TE_gr <- join_overlap_intersect(Col_TSS_data_gr,all_TEs_gr)
TE_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>% 
  distinct(Peakid)

LINE_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="LINE") %>% 
  distinct(Peakid)

SINE_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="SINE") %>% 
  distinct(Peakid)

LTR_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="LTR") %>% 
  distinct(Peakid)

DNA_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="DNA") %>% 
  distinct(Peakid)

SVA_peaks <- overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="Retroposon") %>% 
  distinct(Peakid)

# join sig data by toptable information 

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()

annotated_peaks <-   all_results %>%
  dplyr::filter(source=="DOX_3"|source=="DOX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val)) %>% 
  mutate(TE_status=if_else(genes %in% TE_peaks$Peakid,"TE_peak","not_TE_peak"),
         LINE_status=if_else(genes %in% LINE_peaks$Peakid,"LINE_peak","not_LINE_peak"),
         SINE_status=if_else(genes %in% SINE_peaks$Peakid,"SINE_peak","not_SINE_peak"),
         LTR_status=if_else(genes %in% LTR_peaks$Peakid,"LTR_peak","not_LTR_peak"),
         DNA_status=if_else(genes %in% DNA_peaks$Peakid,"DNA_peak","not_DNA_peak"),
         SVA_status=if_else(genes %in% SVA_peaks$Peakid,"SVA_peak","not_SVA_peak")) %>% 
  mutate(DOX_sig_3=if_else(adj.P.Val_DOX_3<0.05,"sig","not_sig"),
         DOX_sig_24=if_else(adj.P.Val_DOX_24<0.05,"sig","not_sig")) %>% 
  mutate(DOX_sig_3=factor(DOX_sig_3,levels=c("sig","not_sig")),
         DOX_sig_24=factor(DOX_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_EPI_data,by=c("genes"="genes")) %>% 
  mutate(EPI_sig_3=if_else(adj.P.Val_EPI_3<0.05,"sig","not_sig"),
         EPI_sig_24=if_else(adj.P.Val_EPI_24<0.05,"sig","not_sig")) %>% 
  mutate(EPI_sig_3=factor(EPI_sig_3,levels=c("sig","not_sig")),
         EPI_sig_24=factor(EPI_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_DNR_data,by=c("genes"="genes")) %>% 
  mutate(DNR_sig_3=if_else(adj.P.Val_DNR_3<0.05,"sig","not_sig"),
         DNR_sig_24=if_else(adj.P.Val_DNR_24<0.05,"sig","not_sig")) %>% 
  mutate(DNR_sig_3=factor(DNR_sig_3,levels=c("sig","not_sig")),
         DNR_sig_24=factor(DNR_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_MTX_data,by=c("genes"="genes")) %>% 
  mutate(MTX_sig_3=if_else(adj.P.Val_MTX_3<0.05,"sig","not_sig"),
         MTX_sig_24=if_else(adj.P.Val_MTX_24<0.05,"sig","not_sig")) %>% 
  mutate(MTX_sig_3=factor(MTX_sig_3,levels=c("sig","not_sig")),
         MTX_sig_24=factor(MTX_sig_24,levels=c("sig","not_sig"))) 

```


```{r, eval=FALSE}
### making supplementary table 13  annotated peaks

all_TEs_for_anno <- overlap_TE_gr %>% 
  as.data.frame() %>% 
  group_by(Peakid) %>% 
  reframe(repName=paste0(repName,collapse = ";"),
          repClass=paste0(repClass, collapse = ";"),
          repFamily=paste0(repFamily, collapse = ";"))


annotated_DARs<- readRDS("data/Final_four_data/re_analysis/DOX_DAR_annotated_peaks_chipannno.RDS")

Base_frame <- annotated_DARs$DOX_3 %>%  as.data.frame()

Base_frame %>% 
  dplyr::select(mcols.genes,annotation,geneId,transcriptId,distanceToTSS) %>% 
  dplyr::rename("Peakid"=mcols.genes,
                "ENTREZID"=geneId) %>% 
  left_join(.,all_TEs_for_anno, by = c("Peakid"="Peakid")) %>% 
  write.csv(.,"data/Final_four_data/re_analysis/ATAC_excel_outputs/S13_Table.csv")
```



```{r exploring making matrices}
DOX_3_TE_mat <- annotated_peaks %>% 
  group_by(TE_status,DOX_sig_3) %>% 
  tally() %>% 
  pivot_wider(., id_cols=TE_status,names_from = DOX_sig_3,values_from = n) %>% 
  column_to_rownames("TE_status") %>% 
  as.matrix()
```
From the code above,
#### DOX
```{r DOX3 hour types}

# Vector of status-type column names in your data
status_columns <- c("TE_status", "SINE_status", "LINE_status", "LTR_status", "DNA_status", "SVA_status")

# Create a list of matrices, named by status type
DOX_3_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), DOX_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = DOX_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DOX_3_status_matrices) <- status_columns


odds_ratio_results_DOX_3 <- map(DOX_3_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```
```{r DOX_24 matrix}
# Create a list of matrices, named by status type
DOX_24_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), DOX_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = DOX_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DOX_24_status_matrices) <- status_columns


odds_ratio_results_DOX_24 <- map(DOX_24_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```

#### EPI
```{r EPI3 hour types}

# Vector of status-type column names in your data
status_columns <- c("TE_status", "SINE_status", "LINE_status", "LTR_status", "DNA_status", "SVA_status")

# Create a list of matrices, named by status type
EPI_3_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), EPI_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = EPI_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(EPI_3_status_matrices) <- status_columns


odds_ratio_results_EPI_3 <- map(EPI_3_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```
```{r EPI_24 matrix}
# Create a list of matrices, named by status type
EPI_24_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), EPI_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = EPI_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(EPI_24_status_matrices) <- status_columns


odds_ratio_results_EPI_24 <- map(EPI_24_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```


#### DNR
```{r DNR3 hour types}

# Vector of status-type column names in your data
status_columns <- c("TE_status", "SINE_status", "LINE_status", "LTR_status", "DNA_status", "SVA_status")

# Create a list of matrices, named by status type
DNR_3_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), DNR_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = DNR_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DNR_3_status_matrices) <- status_columns


odds_ratio_results_DNR_3 <- map(DNR_3_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```
```{r DNR_24 matrix}
# Create a list of matrices, named by status type
DNR_24_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), DNR_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = DNR_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DNR_24_status_matrices) <- status_columns


odds_ratio_results_DNR_24 <- map(DNR_24_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```


#### MTX
```{r MTX3 hour types}

# Vector of status-type column names in your data
status_columns <- c("TE_status", "SINE_status", "LINE_status", "LTR_status", "DNA_status", "SVA_status")

# Create a list of matrices, named by status type
MTX_3_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), MTX_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = MTX_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(MTX_3_status_matrices) <- status_columns


odds_ratio_results_MTX_3 <- map(MTX_3_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```
```{r MTX_24 matrix}
# Create a list of matrices, named by status type
MTX_24_status_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- annotated_peaks %>%
    group_by(across(all_of(status_col)), MTX_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = MTX_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(MTX_24_status_matrices) <- status_columns


odds_ratio_results_MTX_24 <- map(MTX_24_status_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})

```






#### Combining the data and applying BH pvalue adjustments
```{r}
# odds_ratio_results_DOX_3
# odds_ratio_results_DOX_24
# odds_ratio_results_DOX_24_sig_up
# odds_ratio_results_DOX_24_sig_down

combined_df <- bind_rows(
  map_dfr(odds_ratio_results_DOX_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DOX_3hr"),
  map_dfr(odds_ratio_results_DOX_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DOX_24hr"),
  map_dfr(odds_ratio_results_EPI_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "EPI_3hr"),
  map_dfr(odds_ratio_results_EPI_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "EPI_24hr"),
  map_dfr(odds_ratio_results_DNR_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DNR_3hr"),
  map_dfr(odds_ratio_results_DNR_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DNR_24hr"),
  map_dfr(odds_ratio_results_MTX_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "MTX_3hr"),
  map_dfr(odds_ratio_results_MTX_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "MTX_24hr")
)
# saveRDS(combined_df,"data/Final_four_data/re_analysis/OR_results_TE_df_1bp_alltrt.RDS")
```

```{r}
TE_sig_mat <- combined_df %>% 
  dplyr::select( status,source,chi_sq_p) %>%
  group_by(source) %>%
  mutate(rank_val=rank(chi_sq_p, ties.method = "first")) %>%
  mutate(BH_correction= p.adjust(chi_sq_p,method= "BH")) %>% 
  pivot_wider(., id_cols = status, names_from = source, values_from = BH_correction) %>% 
  column_to_rownames("status") %>% 
  as.matrix()

col_fun_OR = colorRamp2(c(0,1,1.5,5), c("blueviolet","white","lightgreen","green3" ))

# TE_od_mat <- 
combined_df %>% 
  dplyr::select(status, source, odds_ratio) %>%
  group_by(source) %>%
  pivot_wider(., id_cols = status, names_from = source, values_from = odds_ratio) %>% 
  column_to_rownames("status") %>% 
  as.matrix() %>% 
   ComplexHeatmap::Heatmap(. ,col = col_fun_OR, 
                          cluster_rows=FALSE, 
                          cluster_columns=FALSE, 
                          column_names_side = "top", 
                          column_names_rot = 45,
                          # na_col = "black",
                          cell_fun = function(j, i, x, y, width, height, fill) {if (!is.na(TE_sig_mat[i, j]) && TE_sig_mat[i, j] < 0.05  && .[i, j] > 1) {
            grid.text("*", x, y, gp = gpar(fontsize = 20))}})

```
### Looking at LTR class breakdown

```{r}
TE_catagories <- overlap_TE_gr %>% as.data.frame() %>% 
  dplyr::select(Peakid,repName:id) %>% 
  distinct() %>% 
  mutate(repClass_org = repClass) %>% #copy repClass for storage
  mutate(repClass=if_else(##relable repClass with other
    repClass_org=="LINE", repClass_org,if_else(repClass_org=="SINE",repClass_org,if_else(repClass_org=="LTR", repClass_org, if_else(repClass_org=="DNA", repClass_org, if_else(repClass_org=="Retroposon",repClass_org,"Other")))))) 



LTR_df <- LTR_repeats %>% 
  as.data.frame() %>% 
  mutate(repName=factor(repName))

scale_fill_LTRs <-  function(...){
  ggplot2:::manual_scale(
    'fill', 
    values = setNames(c( "#8DD3C7",
                         "#FFFFB3",
                         "#BEBADA" ,
                         "#FB8072",
                         "#80B1D3",
                         "#FDB462",
                         "#B3DE69",
                         "#FCCDE5",
                         "#D9D9D9",
                         "#BC80BD",
                         "#CCEBC5",
                         "pink4",
                         "cornflowerblue",
                         "chocolate",
                         "brown",
                         "green",
                         "yellow4",
                         "purple",
                         "darkorchid4",
                         "coral4",
                         "darkolivegreen4",
                         "darkorange"), unique(LTR_df$repFamily)), 
    ...
  )
}

# TE_catagories
```


```{r}
h.genome_df <- repeatmasker %>% 
  mutate(repClass_org = repClass) %>% #copy repClass for storage
  mutate(repClass=if_else(##relable repClass with other
    repClass_org=="LINE", repClass_org,if_else(repClass_org=="SINE",repClass_org,if_else(repClass_org=="LTR", repClass_org, if_else(repClass_org=="DNA", repClass_org, if_else(repClass_org=="Retroposon",repClass_org,"Other")))))) %>% 
  mutate(Peakid=paste0(rownames(.),"_TE")) %>% 
  dplyr::select(Peakid,repName,repClass, repFamily,repClass_org) %>%
   mutate(TE_status ="TE_peak", trt="h.genome")

ggLTR_df <-annotated_peaks %>%
  dplyr::left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(LTR_status=="LTR_peak") %>%
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::rename("Peakid"=genes) %>% 
  dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="all_peaks")

```


```{r}
DNR_3_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(DNR_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_3")

DNR_24_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
 dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_24")

DOX_3_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(DOX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_3")

DOX_24_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(DOX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_24")

EPI_3_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(EPI_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_3")

EPI_24_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_24")

MTX_3_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(MTX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_3")

MTX_24_df <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  dplyr::filter(MTX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_24")

```

```{r}
h.genome_LTR_combo<-h.genome_df %>% 
  dplyr::filter(repClass_org=="LTR") %>% 
  rbind(ggLTR_df) %>% 
  rbind(DOX_3_df) %>% 
  rbind(DOX_24_df) %>% 
  rbind(EPI_3_df) %>% 
  rbind(EPI_24_df) %>% 
  rbind(DNR_3_df) %>% 
  rbind(DNR_24_df) %>% 
  rbind(MTX_3_df) %>% 
  rbind(MTX_24_df)

h.genome_LTR_combo %>% 
  dplyr::filter(TE_status=="TE_peak") %>% 
  mutate(trt=factor(trt, levels=c("h.genome","all_peaks","DOX_3","EPI_3","DNR_3","MTX_3","DOX_24","EPI_24","DNR_24","MTX_24"))) %>% 
  ggplot(., aes(x=trt, fill= repFamily))+
  geom_bar(position="fill", col="black")+
  theme_bw()+
  ggtitle("LTR breakdown across response classes")+
  scale_fill_LTRs()
```


```{r}
ggLINE_df <-annotated_peaks %>%
  dplyr::left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  # dplyr::filter(LTR_status=="LINE_peak") %>%
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::rename("Peakid"=genes) %>% 
  dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="all_peaks")


DNR_3_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(DNR_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_3")

DNR_24_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
 dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_24")

DOX_3_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(DOX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_3")

DOX_24_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(DOX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_24")

EPI_3_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(EPI_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_3")

EPI_24_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_24")

MTX_3_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(MTX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_3")

MTX_24_df_LINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  dplyr::filter(MTX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_24")

```

```{r}
h.genome_LINE_combo<-h.genome_df %>% 
  dplyr::filter(repClass_org=="LINE") %>% 
  rbind(ggLINE_df) %>% 
  rbind(DOX_3_df_LINE) %>% 
  rbind(DOX_24_df_LINE) %>% 
  rbind(EPI_3_df_LINE) %>% 
  rbind(EPI_24_df_LINE) %>% 
  rbind(DNR_3_df_LINE) %>% 
  rbind(DNR_24_df_LINE) %>% 
  rbind(MTX_3_df_LINE) %>% 
  rbind(MTX_24_df_LINE)

h.genome_LINE_combo %>% 
  dplyr::filter(TE_status=="TE_peak") %>% 
  mutate(trt=factor(trt, levels=c("h.genome","all_peaks","DOX_3","EPI_3","DNR_3","MTX_3","DOX_24","EPI_24","DNR_24","MTX_24"))) %>% 
  ggplot(., aes(x=trt, fill= repFamily))+
  geom_bar(position="fill", col="black")+
  theme_bw()+
  ggtitle("LINE breakdown across response classes")#+
  # scale_fill_LINEs()
```




```{r for SINE}
ggSINE_df <-annotated_peaks %>%
  dplyr::left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  # dplyr::filter(LTR_status=="SINE_peak") %>%
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::rename("Peakid"=genes) %>% 
  dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="all_peaks")


DNR_3_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(DNR_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_3")

DNR_24_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
 dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DNR_24")

DOX_3_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(DOX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_3")

DOX_24_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(DOX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="DOX_24")

EPI_3_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(EPI_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_3")

EPI_24_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="EPI_24")

MTX_3_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(MTX_sig_3=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_3")

MTX_24_df_SINE <- annotated_peaks %>%
  left_join(TE_catagories,by=c("genes" = "Peakid")) %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  dplyr::filter(MTX_sig_24=="sig") %>% 
  dplyr::rename("Peakid"=genes) %>% 
   dplyr::select(Peakid, repName, repClass,repFamily,repClass_org,TE_status) %>% 
  distinct(Peakid, TE_status,repClass,.keep_all = TRUE) %>% 
  mutate(trt="MTX_24")
MTX_24_df_SINE %>% 
  group_by(repFamily) %>% 
    tally()

```

```{r sine breakdown}
h.genome_SINE_combo<-h.genome_df %>% 
  dplyr::filter(repClass_org=="SINE") %>% 
  rbind(ggSINE_df) %>% 
  rbind(DOX_3_df_SINE) %>% 
  rbind(DOX_24_df_SINE) %>% 
  rbind(EPI_3_df_SINE) %>% 
  rbind(EPI_24_df_SINE) %>% 
  rbind(DNR_3_df_SINE) %>% 
  rbind(DNR_24_df_SINE) %>% 
  rbind(MTX_3_df_SINE) %>% 
  rbind(MTX_24_df_SINE)

h.genome_SINE_combo %>% 
  dplyr::filter(TE_status=="TE_peak") %>% 
  mutate(trt=factor(trt, levels=c("h.genome","all_peaks","DOX_3","EPI_3","DNR_3","MTX_3","DOX_24","EPI_24","DNR_24","MTX_24"))) %>% 
  ggplot(., aes(x=trt, fill= repFamily))+
  geom_bar(position="fill", col="black")+
  theme_bw()+
  ggtitle("SINE breakdown across response classes")#+
  # scale_fill_LINEs()
```

#### Looking at enrichment of SINE families by treatment-time
```{r}
MIR_overlaps <- 
overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repClass=="SINE") %>% 
  dplyr::select(Peakid,repName, repClass,repFamily) %>% 
  group_by(Peakid) %>%  
  reframe(repFamily= paste(unique(repFamily), collapse = ";"),
                             MIR_overlap=if_else("MIR" %in% repFamily, "MIR_peak","not_MIR_peak")) %>% 
  left_join(annotated_peaks, by=c("Peakid"="genes"))

```

```{r DOX3 DOX24}

DOX_3_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, DOX_sig_3) %>% 
  tally %>% 
  pivot_wider(id_cols= DOX_sig_3,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("DOX_sig_3")  
DOX_3_MIR
chisq.test(DOX_3_MIR)

DOX_24_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, DOX_sig_24) %>% 
  tally %>% 
  pivot_wider(id_cols= DOX_sig_24,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("DOX_sig_24") 
DOX_24_MIR
chisq.test(DOX_24_MIR)
```

```{r EPI3 EPI24}

EPI_3_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, EPI_sig_3) %>% 
  tally %>% 
  pivot_wider(id_cols= EPI_sig_3,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("EPI_sig_3")  
EPI_3_MIR
chisq.test(EPI_3_MIR)

EPI_24_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, EPI_sig_24) %>% 
  tally %>% 
  pivot_wider(id_cols= EPI_sig_24,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("EPI_sig_24") 
EPI_24_MIR
chisq.test(EPI_24_MIR)
```

```{r DNR3 DNR24}

DNR_3_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, DNR_sig_3) %>% 
  tally %>% 
  pivot_wider(id_cols= DNR_sig_3,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("DNR_sig_3")  
DNR_3_MIR
chisq.test(DNR_3_MIR)

DNR_24_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, DNR_sig_24) %>% 
  tally %>% 
  pivot_wider(id_cols= DNR_sig_24,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("DNR_sig_24") 
DNR_24_MIR
chisq.test(DNR_24_MIR)
```

```{r MTX3 MTX24}

MTX_3_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, MTX_sig_3) %>% 
  tally %>% 
  pivot_wider(id_cols= MTX_sig_3,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("MTX_sig_3")  
MTX_3_MIR
chisq.test(MTX_3_MIR)

MTX_24_MIR <- MIR_overlaps %>% 
  group_by(MIR_overlap, MTX_sig_24) %>% 
  tally %>% 
  pivot_wider(id_cols= MTX_sig_24,names_from = MIR_overlap, values_from = n) %>% 
  column_to_rownames("MTX_sig_24") 
MTX_24_MIR
chisq.test(MTX_24_MIR)
```


```{r}
mir_tables <- c("DOX_3_MIR","DOX_24_MIR", "EPI_3_MIR","EPI_24_MIR", "DNR_3_MIR","DNR_24_MIR","MTX_3_MIR", "MTX_24_MIR") 
## making a dataframe of chisquare pvalues
mir_pval_df <- data.frame(
  Treatment_Time = mir_tables,
  P_value = sapply(mir_tables, function(x) {
    tbl <- get(x)
    test_result <- chisq.test(tbl)
    test_result$p.value
  })
)
mir_pval_df <- mir_pval_df %>%
  mutate(signif_label = case_when(
    P_value < 0.001 ~ "***",
    P_value < 0.01  ~ "**",
    P_value < 0.05  ~ "*",
    TRUE            ~ "ns"
  ))

print(mir_pval_df)

n <- length(mir_tables)
signif_df <- data.frame(
  xmin = seq(1, by = 2, length.out = n),
  xmax = seq(2, by = 2, length.out = n),
  y_position = rep(1.05, n),  # tweak if needed
  annotation = mir_pval_df$signif_label,
  Treatment_Time = mir_pval_df$Treatment_Time) %>% 
 mutate(Treatment_Time= factor(Treatment_Time, levels = c("DOX_3_MIR",
                                "DOX_24_MIR",
                                "EPI_3_MIR",
                                "EPI_24_MIR",
                                "DNR_3_MIR",
                                "DNR_24_MIR",
                                "MTX_3_MIR",
                                "MTX_24_MIR"))) 
signif_df$group <- 1:nrow(signif_df)

signif_df
```

```{r}
extract_mir_counts <- function(tbl_name) {
  df <- get(tbl_name)
  
  # Add significance labels (assuming row 1 = sig, row 2 = not sig)
  df$Significance <- c("Significant", "Not_Significant")

  # Reshape to long format
  df_long <- df %>%
    pivot_longer(cols = c("MIR_peak", "not_MIR_peak"),
                 names_to = "MIR_status",
                 values_to = "Count") %>%
    mutate(Treatment_Time = tbl_name)

  return(df_long)
}


# Combine all into one dataframe
mir_prop_df <- bind_rows(lapply(mir_tables, extract_mir_counts))


# Convert columns to factors
mir_prop_df$MIR_status <- factor(mir_prop_df$MIR_status, levels = c("MIR_peak", "not_MIR_peak"))
mir_prop_df$Significance <- factor(mir_prop_df$Significance, levels = c("Significant", "Not_Significant"))

# # Normalize to proportions
mir_prop_df <- mir_prop_df %>%
  group_by(Treatment_Time, Significance) %>%
  mutate(Proportion = Count / sum(Count)) %>%
  ungroup() %>% 
  mutate(x_axis = interaction(Significance, Treatment_Time, 
                              levels = c( # list levels in the exact plotting order
                                "Significant.DOX_3_MIR",
                                "Not_Significant.DOX_3_MIR",
                                "Significant.DOX_24_MIR",
                                "Not_Significant.DOX_24_MIR",
                                "Significant.EPI_3_MIR",
                                "Not_Significant.EPI_3_MIR",
                                "Significant.EPI_24_MIR",
                                "Not_Significant.EPI_24_MIR",
                                "Significant.DNR_3_MIR",
                                "Not_Significant.DNR_3_MIR",
                                "Significant.DNR_24_MIR",
                                "Not_Significant.DNR_24_MIR",
                                "Significant.MTX_3_MIR",
                                "Not_Significant.MTX_3_MIR",
                                "Significant.MTX_24_MIR",
                                "Not_Significant.MTX_24_MIR"
                              )))

mir_prop_df %>% 
  mutate(Treatment_Time= factor(Treatment_Time, levels = c("DOX_3_MIR",
                                "DOX_24_MIR",
                                "EPI_3_MIR",
                                "EPI_24_MIR",
                                "DNR_3_MIR",
                                "DNR_24_MIR",
                                "MTX_3_MIR",
                                "MTX_24_MIR"))) %>% 
  mutate(MIR_status=factor(MIR_status,levels=c("MIR_peak","not_MIR_peak")),
         Significance=factor(Significance,levels = c("Significant","Not_Significant"))) %>% 
  ggplot(., aes(x=interaction(Significance,Treatment_Time), y=Proportion, fill=MIR_status))+
      geom_bar(stat = "identity", position = "fill") +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1.2)) +
  scale_fill_manual(values = c("MIR_peak" = "cornflowerblue", "not_MIR_peak" = "darkblue")) +
  labs(
    title = "MIR vs not-MIR Peak Proportions Across Treatments",
    x = "Treatment-Time",
    y = "Proportion",
    fill = "MIR Status"
  ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))# +
  geom_signif(data = signif_df, 
              aes(xmin=xmin,
                  xmax=xmax, 
                  annotations=annotation, 
                  y_position=y_position, 
                  group=group, 
                  manual=TRUE,
                  tip_length = 0.03,
            inherit.aes = FALSE))
```


```{r All chromatin regions}
All_chromatin_MIR_overlaps <- 
overlap_TE_gr %>% 
  as.data.frame() %>%
  # dplyr::filter(repClass=="SINE") %>% 
  dplyr::select(Peakid,repName, repClass,repFamily) %>% 
  group_by(Peakid) %>%  
  reframe(repFamily= paste(unique(repFamily), collapse = ";"),
                             MIR_overlap=if_else("MIR" %in% repFamily, "MIR_peak","not_MIR_peak")) %>% 
  left_join(annotated_peaks, by=c("Peakid"="genes"))

MIR_annotated_peaks <- annotated_peaks %>% 
  left_join(All_chromatin_MIR_overlaps) %>% 
  mutate(MIR_overlap=if_else(is.na(MIR_overlap),"not_MIR_peak",MIR_overlap))
```

```{r}
All_DOX_3 <- MIR_annotated_peaks %>% 
  group_by(DOX_sig_3,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=DOX_sig_3,values_from = n, names_from = MIR_overlap) %>% 
  column_to_rownames("DOX_sig_3")
chisq.test(All_DOX_3)

All_DOX_24 <- MIR_annotated_peaks %>% 
  group_by(DOX_sig_24,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=DOX_sig_24,values_from = n, names_from = MIR_overlap) %>% 
   column_to_rownames("DOX_sig_24")

chisq.test(All_DOX_24)
```


```{r}
All_EPI_3 <- MIR_annotated_peaks %>% 
  group_by(EPI_sig_3,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=EPI_sig_3,values_from = n, names_from = MIR_overlap) %>% 
  column_to_rownames("EPI_sig_3")
chisq.test(All_EPI_3)

All_EPI_24 <- MIR_annotated_peaks %>% 
  group_by(EPI_sig_24,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=EPI_sig_24,values_from = n, names_from = MIR_overlap) %>% 
   column_to_rownames("EPI_sig_24")

chisq.test(All_EPI_24)
```


```{r}

All_DNR_3 <- MIR_annotated_peaks %>% 
  group_by(DNR_sig_3,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=DNR_sig_3,values_from = n, names_from = MIR_overlap) %>% 
  column_to_rownames("DNR_sig_3")
chisq.test(All_DNR_3)

All_DNR_24 <- MIR_annotated_peaks %>% 
  group_by(DNR_sig_24,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=DNR_sig_24,values_from = n, names_from = MIR_overlap) %>% 
   column_to_rownames("DNR_sig_24")

chisq.test(All_DNR_24)
```

```{r}
All_MTX_3 <- MIR_annotated_peaks %>% 
  group_by(MTX_sig_3,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=MTX_sig_3,values_from = n, names_from = MIR_overlap) %>% 
  column_to_rownames("MTX_sig_3")
chisq.test(All_MTX_3)

All_MTX_24 <- MIR_annotated_peaks %>% 
  group_by(MTX_sig_24,MIR_overlap) %>% 
  tally() %>% 
  pivot_wider(id_cols=MTX_sig_24,values_from = n, names_from = MIR_overlap) %>% 
   column_to_rownames("MTX_sig_24")

chisq.test(All_MTX_24)
```


```{r}
All_extract_mir_counts <- function(tbl_name) {
  df <- get(tbl_name)
  
  # Add significance labels (assuming row 1 = sig, row 2 = not sig)
  df$Significance <- c("Significant", "Not_Significant")

  # Reshape to long format
  df_long <- df %>%
    pivot_longer(cols = c("MIR_peak", "not_MIR_peak"),
                 names_to = "MIR_status",
                 values_to = "Count") %>%
    mutate(Treatment_Time = tbl_name)

  return(df_long)
}

All_mir_tables <- c("All_DOX_3","All_DOX_24", "All_EPI_3","All_EPI_24", "All_DNR_3","All_DNR_24","All_MTX_3", "All_MTX_24") 
## making a dataframe of chisquare pvalues
All_mir_pval_df <- data.frame(
  Treatment_Time = All_mir_tables,
  P_value = sapply(All_mir_tables, function(x) {
    tbl <- get(x)
    test_result <- chisq.test(tbl)
    test_result$p.value
  })
)
All_mir_pval_df <- All_mir_pval_df %>%
  mutate(signif_label = case_when(
    P_value < 0.001 ~ "***",
    P_value < 0.01  ~ "**",
    P_value < 0.05  ~ "*",
    TRUE            ~ "ns"
  ))

print(All_mir_pval_df)

All_mir_prop_df <- bind_rows(lapply(All_mir_tables, All_extract_mir_counts))

All_mir_prop_df %>% 
  pivot_wider(id_cols = c(Treatment_Time,Significance), values_from = Count, names_from = MIR_status) %>% 
  left_join(All_mir_pval_df, by =c("Treatment_Time"= "Treatment_Time")) %>% 
  rowwise() %>% 
  mutate(prop=round((MIR_peak/sum(MIR_peak,not_MIR_peak))*100, 4)) %>% 
  DT::datatable()
```
#### Third time's the charm:

```{r}
all_chrom_regions <- MIR_annotated_peaks %>% 
  group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n)

DOX_DAR_set_3 <- MIR_annotated_peaks %>% 
  dplyr::filter(DOX_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)
DOX_DAR_set_24 <- MIR_annotated_peaks %>% 
  dplyr::filter(DOX_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)


EPI_DAR_set_3 <- MIR_annotated_peaks %>% 
  dplyr::filter(EPI_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)
EPI_DAR_set_24 <- MIR_annotated_peaks %>% 
  dplyr::filter(EPI_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)

DNR_DAR_set_3 <- MIR_annotated_peaks %>% 
  dplyr::filter(DNR_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)
DNR_DAR_set_24 <- MIR_annotated_peaks %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)

MTX_DAR_set_3 <- MIR_annotated_peaks %>% 
  dplyr::filter(MTX_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)
MTX_DAR_set_24 <- MIR_annotated_peaks %>% 
  dplyr::filter(MTX_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions)

```

now to collect dataframes and do chisquare test:

```{r ,fig.height=10}
All_extract_DAR_AR_counts <- function(tbl_name) {
  df <- get(tbl_name)
  
  # Add significance labels (assuming row 1 = sig, row 2 = not sig)
  df$type <- c("DAR", "AR")

  # Reshape to long format
  df_long <- df %>%
    pivot_longer(cols = c("MIR_peak", "not_MIR_peak"),
                 names_to = "MIR_status",
                 values_to = "Count") %>%
    mutate(Treatment_Time = tbl_name)

  return(df_long)
}

All_DAR_AR_tables <- c("DOX_DAR_set_3","DOX_DAR_set_24", "EPI_DAR_set_3","EPI_DAR_set_24", "DNR_DAR_set_3","DNR_DAR_set_24","MTX_DAR_set_3", "MTX_DAR_set_24") 
## making a dataframe of chisquare pvalues
All_DAR_AR_pval_df <- data.frame(
  Treatment_Time = All_DAR_AR_tables,
  P_value = sapply(All_DAR_AR_tables, function(x) {
    tbl <- get(x)
    test_result <- chisq.test(tbl)
    test_result$p.value
  })
)
All_DAR_AR_pval_df <- All_DAR_AR_pval_df %>%
  mutate(signif_label = case_when(
    P_value < 0.001 ~ "***",
    P_value < 0.01  ~ "**",
    P_value < 0.05  ~ "*",
    TRUE            ~ "ns"
  ))

All_DAR_AR_pval_df


All_DAR_AR_prop_df <- bind_rows(lapply(All_DAR_AR_tables, All_extract_DAR_AR_counts))

All_DAR_AR_prop_df %>% 
  pivot_wider(id_cols = c(Treatment_Time,type), values_from = Count, names_from = MIR_status) %>% 
  left_join(All_DAR_AR_pval_df, by =c("Treatment_Time"= "Treatment_Time")) %>% 
  rowwise() %>% 
  mutate(prop=round((MIR_peak/sum(MIR_peak,not_MIR_peak))*100, 4)) %>% 
  DT::datatable()
```

#### Fourth time, this time only SINEs
```{r}
all_chrom_regions_so <- MIR_annotated_peaks %>% 
  dplyr::filter(SINE_status=="SINE_peak") %>% 
  group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n)

DOX_DAR_set_3_so <- MIR_annotated_peaks %>% 
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(DOX_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)
DOX_DAR_set_24_so <- MIR_annotated_peaks %>% 
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(DOX_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)


EPI_DAR_set_3_so <- MIR_annotated_peaks %>%
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(EPI_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)
EPI_DAR_set_24_so <- MIR_annotated_peaks %>% 
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(EPI_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)

DNR_DAR_set_3_so <- MIR_annotated_peaks %>%
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(DNR_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)
DNR_DAR_set_24_so <- MIR_annotated_peaks %>%
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(DNR_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)

MTX_DAR_set_3_so <- MIR_annotated_peaks %>% 
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(MTX_sig_3=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)
MTX_DAR_set_24_so <- MIR_annotated_peaks %>% 
   dplyr::filter(SINE_status=="SINE_peak") %>% 
  dplyr::filter(MTX_sig_24=="sig") %>% 
   group_by(MIR_overlap) %>% 
  tally %>% 
  pivot_wider(names_from = MIR_overlap, values_from = n) %>% 
  bind_rows(all_chrom_regions_so)
```





```{r SINE only background}
All_extract_DAR_AR_counts_so <- function(tbl_name) {
  df <- get(tbl_name)
  
  # Add significance labels (assuming row 1 = sig, row 2 = not sig)
  df$type <- c("DAR", "AR")

  # Reshape to long format
  df_long <- df %>%
    pivot_longer(cols = c("MIR_peak", "not_MIR_peak"),
                 names_to = "MIR_status",
                 values_to = "Count") %>%
    mutate(Treatment_Time = tbl_name)

  return(df_long)
}

All_DAR_AR_tables_so <- c("DOX_DAR_set_3_so","DOX_DAR_set_24_so", "EPI_DAR_set_3_so","EPI_DAR_set_24_so", "DNR_DAR_set_3_so","DNR_DAR_set_24_so","MTX_DAR_set_3_so", "MTX_DAR_set_24_so") 
## making a dataframe of chisquare pvalues
All_DAR_AR_pval_df_so <- data.frame(
  Treatment_Time = All_DAR_AR_tables_so,
  P_value = sapply(All_DAR_AR_tables_so, function(x) {
    tbl <- get(x)
    test_result <- chisq.test(tbl)
    test_result$p.value
  })
)
All_DAR_AR_pval_df_so <- All_DAR_AR_pval_df_so %>%
  mutate(signif_label = case_when(
    P_value < 0.001 ~ "***",
    P_value < 0.01  ~ "**",
    P_value < 0.05  ~ "*",
    TRUE            ~ "ns"
  ))

All_DAR_AR_pval_df_so


All_DAR_AR_prop_df_so <- bind_rows(lapply(All_DAR_AR_tables_so, All_extract_DAR_AR_counts_so))

All_DAR_AR_prop_df_so %>% 
  pivot_wider(id_cols = c(Treatment_Time,type), values_from = Count, names_from = MIR_status) %>% 
  left_join(All_DAR_AR_pval_df_so, by =c("Treatment_Time"= "Treatment_Time")) %>% 
  rowwise() %>% 
  mutate(prop=round((MIR_peak/sum(MIR_peak,not_MIR_peak))*100, 4)) %>% 
  DT::datatable()
```
#### sine data

```{r making dataframes for filt}
saveRDS(overlap_TE_gr,"data/Final_four_data/re_analysis/TE_overlapping_granges_output.RDS")
Overlapping_peaks <-
  overlap_TE_gr %>% 
  as.data.frame() %>%
  dplyr::filter(repFamily=="MIR"|
                  repFamily=="Alu"|
                  repFamily=="L1"|
                  repFamily=="L2"|
                  repFamily=="ERVK"|
                  repFamily=="ERV1"|
                  repFamily=="ERVL-MaLR"|
                  repFamily=="TcMar"|
                  repFamily=="hAT")
  
Family_list <- c("MIR",
                  "Alu",
                  "L1",
                  "L2",
                  "ERVK",
                  "ERV1",
                  "ERVL-MaLR",
                  "TcMar",
                  "hAT")

# Convert once to avoid repeating
df <- as.data.frame(overlap_TE_gr)

# Use a list to store them
peak_lists <- lapply(Family_list, function(fam) {
  df %>%
    dplyr::filter(repFamily == fam | repClass == fam) %>%
    dplyr::distinct(Peakid)
})

# Name each element
names(peak_lists) <- paste0(Family_list, "_peaks")
```


```{r}
all_filt <- all_results %>%
  dplyr::filter(source %in% c("DOX_3", "DOX_24")) %>% 
  dplyr::select(source, genes, logFC, adj.P.Val) %>% 
  tidyr::pivot_wider(id_cols = genes, names_from = source, values_from = c(logFC, adj.P.Val)) %>% 
  mutate(
    TE_status = if_else(genes %in% TE_peaks$Peakid, "TE_peak", "not_TE_peak"),
    MIR_status = if_else(genes %in% peak_lists$MIR_peaks$Peakid, "MIR_peak", "not_MIR_peak"),
    Alu_status = if_else(genes %in% peak_lists$Alu_peaks$Peakid, "Alu_peak", "not_Alu_peak"),
    L1_status = if_else(genes %in% peak_lists$L1_peaks$Peakid, "L1_peak", "not_L1_peak"),
    L2_status = if_else(genes %in% peak_lists$L2_peaks$Peakid, "L2_peak", "not_L2_peak"),
    ERVK_status = if_else(genes %in% peak_lists$ERVK_peaks$Peakid, "ERVK_peak", "not_ERVK_peak"),
    ERV1_status = if_else(genes %in% peak_lists$ERV1_peaks$Peakid, "ERV1_peak", "not_ERV1_peak"),
    `ERVL-MaLR_status` = if_else(genes %in% peak_lists$`ERVL-MaLR_peaks`$Peakid, "ERVL-MaLR_peak", "not_ERVL-MaLR_peak"),
    TcMar_status = if_else(genes %in% peak_lists$TcMar_peaks$Peakid, "TcMar_peak", "not_TcMar_peak"),
    hAT_status = if_else(genes %in% peak_lists$hAT_peaks_peaks$Peakid, "hAT_peak", "not_hAT_peak")) %>% 
  mutate(DOX_sig_3=if_else(adj.P.Val_DOX_3<0.05,"sig","not_sig"),
         DOX_sig_24=if_else(adj.P.Val_DOX_24<0.05,"sig","not_sig")) %>% 
  mutate(DOX_sig_3=factor(DOX_sig_3,levels=c("sig","not_sig")),
         DOX_sig_24=factor(DOX_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_EPI_data,by=c("genes"="genes")) %>% 
  mutate(EPI_sig_3=if_else(adj.P.Val_EPI_3<0.05,"sig","not_sig"),
         EPI_sig_24=if_else(adj.P.Val_EPI_24<0.05,"sig","not_sig")) %>% 
  mutate(EPI_sig_3=factor(EPI_sig_3,levels=c("sig","not_sig")),
         EPI_sig_24=factor(EPI_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_DNR_data,by=c("genes"="genes")) %>% 
  mutate(DNR_sig_3=if_else(adj.P.Val_DNR_3<0.05,"sig","not_sig"),
         DNR_sig_24=if_else(adj.P.Val_DNR_24<0.05,"sig","not_sig")) %>% 
  mutate(DNR_sig_3=factor(DNR_sig_3,levels=c("sig","not_sig")),
         DNR_sig_24=factor(DNR_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_MTX_data,by=c("genes"="genes")) %>% 
  mutate(MTX_sig_3=if_else(adj.P.Val_MTX_3<0.05,"sig","not_sig"),
         MTX_sig_24=if_else(adj.P.Val_MTX_24<0.05,"sig","not_sig")) %>% 
  mutate(MTX_sig_3=factor(MTX_sig_3,levels=c("sig","not_sig")),
         MTX_sig_24=factor(MTX_sig_24,levels=c("sig","not_sig"))) 


```

### DOX all
```{r DOXsine3 status}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
DOX_3_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), DOX_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = DOX_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DOX_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_DOX_3<- map(DOX_3_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```

```{r DOXsine3}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
DOX_24_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), DOX_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = DOX_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DOX_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_DOX_24<- map(DOX_24_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```


### EPI all
```{r EPIsine3}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
EPI_3_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), EPI_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = EPI_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(EPI_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_EPI_3<- map(EPI_3_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```

```{r EPIsine3 status}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
EPI_24_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), EPI_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = EPI_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(EPI_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_EPI_24<- map(EPI_24_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```


### DNR all
```{r DNRsine3}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
DNR_3_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), DNR_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = DNR_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DNR_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_DNR_3<- map(DNR_3_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```

```{r DNRsine3 status}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
DNR_24_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), DNR_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = DNR_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(DNR_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_DNR_24<- map(DNR_24_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```


### MTX all
```{r MTXsine3}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
MTX_3_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), MTX_sig_3) %>%
    tally() %>%
    pivot_wider(
      names_from = MTX_sig_3,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(MTX_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_MTX_3<- map(MTX_3_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```

```{r MTXsine3 status}
# Vector of status-type column names in your data
status_columns <- c("MIR_status",
                  "Alu_status",
                  "L1_status",
                  "L2_status",
                  "ERVK_status",
                  "ERV1_status",
                  "ERVL-MaLR_status",
                  "TcMar_status",
                  "hAT_status")

# Create a list of matrices, named by status type
MTX_24_status_filt_matrices <- map(status_columns, function(status_col) {
  # Extract prefix (e.g., "TE", "SINE") from column name like "TE_status"
  prefix <- sub("_status$", "", status_col)
  expected_rows <- c(paste0(prefix, "_peak"), paste0("not_", prefix, "_peak"))
  expected_cols <- c("sig", "not_sig")
  
  # Build matrix
  mat <- all_filt %>%
    group_by(across(all_of(status_col)), MTX_sig_24) %>%
    tally() %>%
    pivot_wider(
      names_from = MTX_sig_24,
      values_from = n,
      values_fill = list(n = 0)
    ) %>%
    column_to_rownames(var = status_col) %>%
    as.matrix()
   print(mat)
  
  # Fill missing expected rows
  for (r in setdiff(expected_rows, rownames(mat))) {
    mat <- rbind(mat, setNames(rep(0, length(expected_cols)), expected_cols))
    rownames(mat)[nrow(mat)] <- r
  }

  # Fill missing expected columns
  for (c in setdiff(expected_cols, colnames(mat))) {
    mat <- cbind(mat, setNames(rep(0, nrow(mat)), c))
  }

  # Order
  mat <- mat[expected_rows, expected_cols, drop = FALSE]
})

# Set names so you can easily refer to each status
names(MTX_3_status_filt_matrices) <- status_columns


odds_ratio_results_filt_MTX_24<- map(MTX_24_status_filt_matrices, function(mat) {
  if (!all(dim(mat) == c(2, 2))) return(NULL)
  
  result <- epitools::oddsratio(mat, method = "wald")
  
  or <- result$measure[2, "estimate"]
  lower <- result$measure[2, "lower"]
  upper <- result$measure[2, "upper"]
  
  pval_chisq <- if("chi.square" %in% colnames(result$p.value) && nrow(result$p.value) >= 2) {
    result$p.value[2, "chi.square"]
  } else {
    NA_real_
  }
  
  list(
    odds_ratio = or,
    lower_ci = lower,
    upper_ci = upper,
    chi_sq_p = pval_chisq
  )
})
```


#### Combining the data and applying BH pvalue adjustments
```{r}
names(odds_ratio_results_filt_DOX_24) <- names(odds_ratio_results_filt_DOX_3)
names(odds_ratio_results_filt_EPI_24) <- names(odds_ratio_results_filt_EPI_3)
names(odds_ratio_results_filt_DNR_24) <- names(odds_ratio_results_filt_DNR_3)
names(odds_ratio_results_filt_MTX_24) <- names(odds_ratio_results_filt_MTX_3)

all_statuses <- unique(unlist(lapply(
  list(
    odds_ratio_results_filt_DOX_3, odds_ratio_results_filt_DOX_24,
    odds_ratio_results_filt_EPI_3, odds_ratio_results_filt_EPI_24,
    odds_ratio_results_filt_DNR_3, odds_ratio_results_filt_DNR_24,
    odds_ratio_results_filt_MTX_3, odds_ratio_results_filt_MTX_24
  ), names
)))

all_sources <- c("DOX_3hr", "DOX_24hr", "EPI_3hr", "EPI_24hr", 
                 "DNR_3hr", "DNR_24hr", "MTX_3hr", "MTX_24hr")

# Now build the full long data frame
all_results_long <- bind_rows(
  map_dfr(odds_ratio_results_filt_DOX_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DOX_3hr"),
  map_dfr(odds_ratio_results_filt_DOX_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DOX_24hr"),
  map_dfr(odds_ratio_results_filt_EPI_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "EPI_3hr"),
  map_dfr(odds_ratio_results_filt_EPI_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "EPI_24hr"),
  map_dfr(odds_ratio_results_filt_DNR_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DNR_3hr"),
  map_dfr(odds_ratio_results_filt_DNR_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "DNR_24hr"),
  map_dfr(odds_ratio_results_filt_MTX_3, ~as.data.frame(.x), .id = "status") %>% mutate(source = "MTX_3hr"),
  map_dfr(odds_ratio_results_filt_MTX_24, ~as.data.frame(.x), .id = "status") %>% mutate(source = "MTX_24hr")
)

# Force inclusion of all status × source combinations
combined_df_filt <- expand_grid(status = all_statuses, source = all_sources) %>%
  left_join(all_results_long, by = c("status", "source"))
# saveRDS(combined_df,"data/Final_four_data/re_analysis/OR_results_TE_df_1bp_alltrt.RDS")
```

```{r supplementary data}
my_column_order <- c("DOX_3hr",  "EPI_3hr","DNR_3hr","MTX_3hr", "DOX_24hr", "EPI_24hr", "DNR_24hr","MTX_24hr")
### Correct pvalues
TE_sig_mat_filt <- combined_df_filt %>% 
  dplyr::select( status,source,chi_sq_p) %>%
  group_by(source) %>%
  mutate(rank_val=rank(chi_sq_p, ties.method = "first")) %>%
  mutate(BH_correction= p.adjust(chi_sq_p,method= "BH")) %>% 
  pivot_wider(., id_cols = status, names_from = source, values_from = BH_correction) %>% 
  column_to_rownames("status") %>% 
  as.matrix()

col_fun_OR = colorRamp2(c(0,1,1.5,5), c("blueviolet","white","lightgreen","green3" ))

OR_mat <- combined_df_filt %>% 
  dplyr::select(status, source, odds_ratio) %>%
  group_by(source) %>%
  pivot_wider(id_cols = status, names_from = source, values_from = odds_ratio) %>% 
  column_to_rownames("status") %>% 
  as.matrix()
# Reorder columns
OR_mat <- OR_mat[, my_column_order]

# Match the significance matrix accordingly
sig_mat <- TE_sig_mat_filt[, my_column_order]

   ComplexHeatmap::Heatmap(
  OR_mat,
  col = col_fun_OR,
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  column_names_side = "top",
  column_names_rot = 45,
  cell_fun = function(j, i, x, y, width, height, fill) {
    if (!is.na(sig_mat[i, j]) && sig_mat[i, j] < 0.05 && OR_mat[i, j] > 1) {
      grid.text("*", x, y, gp = gpar(fontsize = 20))
    }
  }
)

```
