---
title: "Overlapping other data"
author: "Renee Matthews"
date: "2025-06-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
		dev = c("png","pdf")
)
```

```{css, echo=FALSE}
pre {
  max-height: 400px;
  overflow-y: auto;
}

pre[class] {
  max-height: 200px;
}
```

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(broom)
library(RColorBrewer)
library(ChIPseeker)
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("org.Hs.eg.db")
library(rtracklayer)
library(edgeR)
library(ggfortify)
library(limma)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(scales)
library(BiocParallel)
library(ggpubr)
library(devtools)
library(biomaRt)
library(eulerr)
library(smplot2)
library(genomation)
library(ggsignif)
library(plyranges)
library(ggrepel)
library(epitools)
library(circlize)
library(readxl)
library(regioneR)
library(GenomicRanges)
library(gwascat)
library(liftOver)

```


#### Loading in dataframes  


```{r loading data}
toptable_results <- readRDS("data/Final_four_data/re_analysis/Toptable_results.RDS")

all_results  <- toptable_results %>%
  imap(~ .x %>% tibble::rownames_to_column(var = "rowname") %>%
         mutate(source = .y)) %>%
  bind_rows()


Top2b_peaks <- import(con="data/other_papers/ChIP3_TOP2B_CM_87-1.bed",format = "bed",genome="hg38")

Motif_list_gr <- readRDS( "data/Final_four_data/re_analysis/Motif_list_granges.RDS")
list2env(Motif_list_gr,envir = .GlobalEnv)
df_list <- plyr::llply(Motif_list_gr[c(1:9)], as.data.frame)
list2env(df_list,envir=.GlobalEnv)

Left_ventricle <- import(con = "C://Users/renee/Downloads/hg38.TADs/hg38/VentricleLeft_STL003_Leung_2015-raw_TADs.txt", format = "bed",genome="hg38")

DOX_3_sig_gr <-
all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>% 
  mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_3") %>% 
   dplyr::filter(adj.P.Val<0.05) %>% 
  separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges()

DOX_24_sig_gr <-
all_results %>% 
  dplyr::select(source,genes, logFC,adj.P.Val) %>%
   mutate("Peakid"=genes) %>% 
  dplyr::filter(source=="DOX_24") %>% 
   dplyr::filter(adj.P.Val<0.05) %>% 
  separate_wider_delim(., cols="genes",names = c("seqnames","start","end"), delim= ".") %>% 
  GRanges()  
   
# mrc_lookup <- bind_rows(
#   (EAR_open  %>% dplyr::select(Peakid) %>% mutate(mrc = "EAR_open")),  
#   (EAR_close %>%  dplyr::select(Peakid) %>%mutate(mrc = "EAR_close")),
#   (ESR_open  %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_open")),
#   (ESR_close %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_close")),
#   (ESR_opcl   %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_opcl")),
#   (ESR_clop   %>%  dplyr::select(Peakid) %>%mutate(mrc = "ESR_clop")),
#   (LR_open   %>%  dplyr::select(Peakid) %>%mutate(mrc = "LR_open")),
#   (LR_close  %>%  dplyr::select(Peakid) %>%mutate(mrc = "LR_close")),
#   (NR        %>%  dplyr::select(Peakid) %>%mutate(mrc = "NR"))
# ) %>%
#   distinct(Peakid, mrc) 


MCF7_DARs_hyper <- read_excel("C:/Users/renee/Downloads/MCF7-doxATAC/Table 4.XLSX", 
    sheet = "hyper") %>% GRanges()
MCF7_DARs_hypo <- read_excel("C:/Users/renee/Downloads/MCF7-doxATAC/Table 4.XLSX", 
    sheet = "hypo") %>% GRanges()

MCF7_ARsmcf7_1 <- read_excel("C:/Users/renee/Downloads/MCF7-doxATAC/Table 3.XLSX") %>% 
  GRanges()
  MCF7_DARs_hyper$names <- paste0("hyper_", seq_along(seqnames(MCF7_DARs_hyper)))
 MCF7_DARs_hypo$names <- paste0("hypo_", seq_along(seqnames(MCF7_DARs_hypo)))
 
 MCF7_DAR_all <- c(MCF7_DARs_hyper,MCF7_DARs_hypo)
 
 
```


```{r liftOver of MCF7}
ch = import.chain("C:/Users/renee/ATAC_folder/liftOver_genome/hg19ToHg38.over.chain")
MCF7_ARsmcf7_1_LO <- as.data.frame(liftOver(MCF7_ARsmcf7_1,ch)) %>% 
  GRanges()

MCF7_DARs_hyper_LO <- as.data.frame(liftOver(MCF7_DARs_hyper,ch)) %>% 
  GRanges()

MCF7_DARs_hypo_LO <- as.data.frame(liftOver(MCF7_DARs_hypo,ch)) %>% 
  GRanges()

MCF7_DAR_all <- c(MCF7_DARs_hyper_LO,MCF7_DARs_hypo_LO)
```

### Overlapping Top2b and all ATAC regions

```{r}

Allregion_ol <- join_overlap_intersect(all_regions,Top2b_peaks)%>% 
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE)

left_ventricle_ol <- join_overlap_intersect(all_regions ,Left_ventricle) %>% 
  as.data.frame() %>% 
  distinct(Peakid,.keep_all = TRUE)

MCF7_AR_ol <- join_overlap_intersect(all_regions, MCF7_ARsmcf7_1_LO)

MCF7_hyper_ol <- join_overlap_intersect(all_regions, MCF7_DARs_hyper_LO)
MCF7_hypo_ol <- join_overlap_intersect(all_regions, MCF7_DARs_hypo_LO)

MCF7_DAR_all_ol <- join_overlap_intersect(all_regions, MCF7_DAR_all)


DOX_MCF7_DARS_ol <- join_overlap_intersect(DOX_24_sig_gr, MCF7_DAR_all)



```
Proportion of Tob2b peaks found in ATAC peak by treatment:
```{r}
annotated_regions <- all_results %>% 
  dplyr::filter(source=="DOX_3"|source=="DOX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val)) %>% 
  mutate(top_2b_ol=case_when(genes %in% Allregion_ol$Peakid~"TOP2b_peak",
         TRUE ~"not_TOP2b_peak")) %>% 
  mutate(sig_3=if_else(adj.P.Val_DOX_3<0.05,"sig","not_sig"),
         sig_24=if_else(adj.P.Val_DOX_24<0.05,"sig","not_sig")) %>% 
  mutate(sig_3=factor(sig_3,levels=c("sig","not_sig")),
         sig_24=factor(sig_24,levels=c("sig","not_sig"))) %>% 
  # left_join(., mrc_lookup, by =c("genes"="Peakid")) %>% 
  # mutate(mrc=tidyr::replace_na(mrc, "not_mrc")) %>% 
  mutate(TAD_ol=case_when(genes%in% left_ventricle_ol$Peakid~"TAD_peak",
                          TRUE ~"not_TAD_peak")) %>% 
  mutate(MCF7_AR=case_when(genes %in% MCF7_AR_ol$Peakid~"MCF7AR_peak",
         TRUE ~"not_MCF7AR_peak")) %>% 
   mutate(MCF7_hyper=case_when(genes %in% MCF7_hyper_ol$Peakid~"MCF7hyper_peak",
         TRUE ~"not_MCF7hyper_peak")) %>% 
   mutate(MCF7_hypo=case_when(genes %in% MCF7_hypo_ol$Peakid~"MCF7hypo_peak",
         TRUE ~"not_MCF7hypo_peak")) 
annotated_regions %>% 
  group_by(sig_3,top_2b_ol) %>% tally%>% 
 pivot_wider(., id_cols = sig_3, names_from = top_2b_ol, values_from = n)


annotated_regions %>% 
  group_by(sig_24,top_2b_ol) %>% tally %>% 
 pivot_wider(., id_cols = sig_24, names_from = top_2b_ol, values_from = n)

# annotated_regions %>% 
#   group_by(mrc,top_2b_ol) %>% tally %>% 
#   pivot_wider(., id_cols = mrc, names_from = top_2b_ol, values_from = n)

annotated_regions %>% 
  group_by(sig_3,top_2b_ol) %>% tally%>% 
 pivot_wider(., id_cols = sig_3, names_from = top_2b_ol, values_from = n) %>%
  column_to_rownames("sig_3") %>% 
  as.matrix() %>% 
  chisq.test(.)

annotated_regions %>% 
   group_by(sig_24,top_2b_ol) %>% tally%>% 
 pivot_wider(., id_cols = sig_24, names_from = top_2b_ol, values_from = n) %>%
  column_to_rownames("sig_24") %>% 
  as.matrix() %>% 
  chisq.test(.)

# annotated_regions %>% 
#   group_by(mrc,TAD_ol) %>% tally%>% 
#  pivot_wider(., id_cols = mrc, names_from = TAD_ol, values_from = n) 

annotated_regions %>% 
  group_by(TAD_ol, top_2b_ol) %>% tally%>% 
 pivot_wider(., id_cols = c( top_2b_ol), names_from = TAD_ol, values_from = n)
```

```{r}
annotated_regions %>% 
  group_by(sig_3,top_2b_ol) %>% 
  ggplot(., aes(x=sig_3, fill=top_2b_ol))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle(" 3 hour DARs and TOP2b")+
  ylab("proportion")
  

annotated_regions %>% 
  group_by(sig_24,top_2b_ol) %>% 
  ggplot(., aes(x=sig_24, fill=top_2b_ol))+
  geom_bar(position="fill")+
  theme_bw()+
  ggtitle(" 24 hour DARs and TOP2b")+
  ylab("proportion")



top2b_3hr_or <- annotated_regions %>% 
  group_by(sig_3,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=sig_3, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("sig_3") %>% 
  as.matrix() %>% 
  epitools::oddsratio(., method="wald")

top2b_24hr_or <- annotated_regions %>% 
  group_by(sig_24,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=sig_24, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("sig_24") %>% 
  as.matrix() %>% 
  epitools::oddsratio(., method="wald")

ggplot_format_odds <- data.frame("or_value" = c(top2b_3hr_or$measure[2, "estimate"],top2b_24hr_or$measure[2, "estimate"]),
"lower_ci" = c(top2b_3hr_or$measure[2, "lower"],top2b_24hr_or$measure[2, "lower"]),
"upper_ci" = c(top2b_3hr_or$measure[2, "upper"],top2b_24hr_or$measure[2, "upper"]),
"p_value" = c(top2b_3hr_or$p.value[2,"chi.square"],top2b_24hr_or$p.value[2,"chi.square"]),
group=c("3hour","24hour"))
 ggplot_format_odds %>% 
   mutate(group=factor(group, levels= c("3hour","24hour"))) %>% 
ggplot(., aes(x = group, y = or_value)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  labs(
    title = "Odds Ratio of TOP2b Peak Overlap",
    y = "Odds Ratio (95% confidence interval)",
    x = "time"
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5)
  )
```

```{r}
annotated_DARs<- readRDS("data/Final_four_data/re_analysis/DOX_DAR_annotated_peaks_chipannno.RDS")
gene_N_peak <-
annotated_DARs$DOX_3 %>% 
  as.data.frame() %>%
  dplyr::select(mcols.genes,annotation, geneId:distanceToTSS)

toplistall_RNA <- readRDS("data/other_papers/toplistall_RNA.RDS") %>% 
  mutate(logFC = logFC*(-1))



RNA_results <-
toplistall_RNA %>% 
  dplyr::select(time:logFC) %>% 
  tidyr::unite("sample",time, id) %>% 
  pivot_wider(., id_cols = c(ENTREZID,SYMBOL),names_from = sample, values_from = logFC) %>% 
  rename_with(~ str_replace(., "hours", "RNA"))


RNA_adj.pvals <-
toplistall_RNA %>% 
dplyr::select(time:SYMBOL,adj.P.Val) %>% 
  tidyr::unite("sample",id, time) %>% 
  pivot_wider(., id_cols = c(ENTREZID,SYMBOL),names_from = sample, values_from = adj.P.Val) %>% 
  rename_with(~ str_replace(., "hours", "pval"))

```

```{r}
my_DOX_data <- all_results %>% 
  dplyr::filter(source=="DOX_3"|source=="DOX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_EPI_data <- all_results %>% 
  dplyr::filter(source=="EPI_3"|source=="EPI_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_DNR_data <- all_results %>% 
  dplyr::filter(source=="DNR_3"|source=="DNR_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))

my_MTX_data <- all_results %>% 
  dplyr::filter(source=="MTX_3"|source=="MTX_24") %>% 
  dplyr::select(source,genes,logFC,adj.P.Val) %>% 
  pivot_wider(.,id_cols=genes,names_from = source, values_from = c(logFC, adj.P.Val))
```
adding DOX_sig and other trts for enrichment with top2b

```{r}
TSS_listed_df <- annotated_regions %>% 
  # mutate(DOX_sig_3=if_else(adj.P.Val_DOX_3<0.05,"sig","not_sig"),
  #        DOX_sig_24=if_else(adj.P.Val_DOX_24<0.05,"sig","not_sig")) %>% 
  # mutate(DOX_sig_3=factor(DOX_sig_3,levels=c("sig","not_sig")),
  #        DOX_sig_24=factor(DOX_sig_24,levels=c("sig","not_sig"))) %>%
  left_join(.,my_EPI_data,by=c("genes"="genes")) %>% 
  mutate(EPI_sig_3=if_else(adj.P.Val_EPI_3<0.05,"sig","not_sig"),
         EPI_sig_24=if_else(adj.P.Val_EPI_24<0.05,"sig","not_sig")) %>% 
  mutate(EPI_sig_3=factor(EPI_sig_3,levels=c("sig","not_sig")),
         EPI_sig_24=factor(EPI_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_DNR_data,by=c("genes"="genes")) %>% 
  mutate(DNR_sig_3=if_else(adj.P.Val_DNR_3<0.05,"sig","not_sig"),
         DNR_sig_24=if_else(adj.P.Val_DNR_24<0.05,"sig","not_sig")) %>% 
  mutate(DNR_sig_3=factor(DNR_sig_3,levels=c("sig","not_sig")),
         DNR_sig_24=factor(DNR_sig_24,levels=c("sig","not_sig"))) %>% 
  left_join(.,my_MTX_data,by=c("genes"="genes")) %>% 
  mutate(MTX_sig_3=if_else(adj.P.Val_MTX_3<0.05,"sig","not_sig"),
         MTX_sig_24=if_else(adj.P.Val_MTX_24<0.05,"sig","not_sig")) %>% 
  mutate(MTX_sig_3=factor(MTX_sig_3,levels=c("sig","not_sig")),
         MTX_sig_24=factor(MTX_sig_24,levels=c("sig","not_sig"))) %>% 
  dplyr::rename("DOX_sig_3"=sig_3, "DOX_sig_24"= sig_24) %>% 
  left_join(., gene_N_peak, by= c("genes"="mcols.genes"))
```
make the odds ratio dataframe
```{r}
DOX_top2b_3hr_or <-
  TSS_listed_df %>% 
  group_by(DOX_sig_3,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=DOX_sig_3, names_from = top_2b_ol, values_from = n) %>%   column_to_rownames("DOX_sig_3") %>% 
  as.matrix() %>% 
  fisher.test(.)

DOX_top2b_24hr_or <- TSS_listed_df %>% 
  group_by(DOX_sig_24,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=DOX_sig_24, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("DOX_sig_24") %>% 
  as.matrix() %>% 
  fisher.test(.)

EPI_top2b_3hr_or <-
  TSS_listed_df %>% 
  group_by(EPI_sig_3,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=EPI_sig_3, names_from = top_2b_ol, values_from = n) %>%   column_to_rownames("EPI_sig_3") %>% 
  as.matrix() %>% 
  fisher.test(.)
EPI_top2b_24hr_or <- TSS_listed_df %>% 
  group_by(EPI_sig_24,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=EPI_sig_24, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("EPI_sig_24") %>% 
  as.matrix() %>% 
  fisher.test(.)
DNR_top2b_3hr_or <-
  TSS_listed_df %>% 
  group_by(DNR_sig_3,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=DNR_sig_3, names_from = top_2b_ol, values_from = n) %>%   column_to_rownames("DNR_sig_3") %>% 
  as.matrix() %>% 
  fisher.test(.)

DNR_top2b_24hr_or <- TSS_listed_df %>% 
  group_by(DNR_sig_24,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=DNR_sig_24, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("DNR_sig_24") %>% 
  as.matrix() %>% 
 fisher.test(.)
MTX_top2b_3hr_or <-
  TSS_listed_df %>% 
  group_by(MTX_sig_3,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=MTX_sig_3, names_from = top_2b_ol, values_from = n) %>%   column_to_rownames("MTX_sig_3") %>% 
  as.matrix() %>% 
  fisher.test(.)

MTX_top2b_24hr_or <- TSS_listed_df %>% 
  group_by(MTX_sig_24,top_2b_ol) %>% 
  tally %>% 
  pivot_wider(., id_cols=MTX_sig_24, names_from = top_2b_ol, values_from = n) %>% 
  column_to_rownames("MTX_sig_24") %>% 
  as.matrix() %>% 
  fisher.test(.)


# ggplot_format_odds <- data.frame("or_value" = c(top2b_3hr_or$measure[2, "estimate"],top2b_24hr_or$measure[2, "estimate"]),
# "lower_ci" = c(top2b_3hr_or$measure[2, "lower"],top2b_24hr_or$measure[2, "lower"]),
# "upper_ci" = c(top2b_3hr_or$measure[2, "upper"],top2b_24hr_or$measure[2, "upper"]),
# "p_value" = c(top2b_3hr_or$p.value[2,"chi.square"],top2b_24hr_or$p.value[2,"chi.square"]),
# group=c("3hour","24hour"))
```

```{r thanks chatgpt}
# Define the variable names
var_names <- c("DOX_top2b_3hr_or", "DOX_top2b_24hr_or", 
               "EPI_top2b_3hr_or", "EPI_top2b_24hr_or",
               "DNR_top2b_3hr_or", "DNR_top2b_24hr_or",
                "MTX_top2b_3hr_or", "MTX_top2b_24hr_or")

# Optional: label for grouping
group_labels <- c("DOX_3hr", "DOX_24hr", "EPI_3hr", "EPI_24hr", "DNR_3hr", "DNR_24hr", "MTX_3hr", "MTX_24hr")

# Build the data frame
OR_all_trt_result_df <- do.call(rbind, lapply(seq_along(var_names), function(i) {
  var <- get(var_names[i])
  
  data.frame(
    or_value  = unname(var$estimate),  # remove the name "odds ratio"
    lower_ci  = var$conf.int[1],
    upper_ci  = var$conf.int[2],
    p_value   = var$p.value,
    group     = group_labels[i]
  )
}))
```

```{r}
OR_all_trt_result_df %>% 
  separate_wider_delim(.,cols="group", names = c("trt","time"), delim = "_",cols_remove = FALSE) %>% 
    mutate(time= factor(time, levels =c("3hr","24hr")),
         trt=factor(trt, levels= c("DOX", "EPI", "DNR", "MTX"))) %>% 
  # mutate(significant=if_else(p_value <0.05,"TRUE","FALSE")) %>% 
  mutate(
    significant = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      TRUE ~ ""
    )
  ) %>% 
ggplot(., aes(x = trt, y = or_value)) +
   geom_point(aes(color = trt), size=4)+
   geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  geom_text(
  aes(y = upper_ci + 0.1 * or_value, label = significant),
  hjust = 0,  # aligns text to the left of the y point
  size = 4,
  color = "black"
)+
  labs(
    title = "Odds Ratio of TOP2b Peak Overlap",
    y = "Odds Ratio (95% confidence interval)",
    x = "treatment"
  ) +
  # coord_flip()+
  theme_classic() +
  facet_wrap(~time)+
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5)
  )
  
```

```{r}
top2b_overlap <- join_overlap_inner(all_regions,Top2b_peaks)
 AR_total     <- length(unique(all_regions$Peakid))

 
 Top2B_total  <- length(unique(Top2b_peaks$name))
overlap_n    <- length(unique(top2b_overlap$Peakid)) 
fit_top2b <- euler(c(
  "ARs" = AR_total-overlap_n,
  "Top2B" = Top2B_total-length(unique(top2b_overlap$name)),
  "ARs&Top2B" = overlap_n
))

plot(fit_top2b, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between AR and TOP2B peaks")

length(intersect(unique(top2b_overlap$Peakid), unique(all_regions$Peakid)))  # should match overlap_n
```

### MCF7 data

```{r}

annotated_regions %>% 
  group_by(sig_3,MCF7_AR) %>% tally %>% 
 pivot_wider(., id_cols = sig_3, names_from = MCF7_AR, values_from = n) %>% 
  column_to_rownames("sig_3") %>%
  print() %>% 
  fisher.test()


annotated_regions %>% 
  group_by(sig_24,MCF7_AR) %>% tally %>% 
 pivot_wider(., id_cols = sig_24, names_from = MCF7_AR, values_from = n) %>% 
  column_to_rownames("sig_24") %>%
  print() %>% 
  fisher.test()
##### MCF7 hyper

annotated_regions %>% 
  group_by(sig_3,MCF7_hyper) %>% tally %>% 
 pivot_wider(., id_cols = sig_3, names_from = MCF7_hyper, values_from = n) %>% 
  column_to_rownames("sig_3") %>%
  print() %>% 
  fisher.test()


annotated_regions %>% 
  group_by(sig_24,MCF7_hyper) %>% tally %>% 
 pivot_wider(., id_cols = sig_24, names_from = MCF7_hyper, values_from = n) %>% 
  column_to_rownames("sig_24") %>%
  print() %>% 
  fisher.test()
##### MCF7 hypo
annotated_regions %>% 
  group_by(sig_3,MCF7_hypo) %>% tally %>% 
 pivot_wider(., id_cols = sig_3, names_from = MCF7_hypo, values_from = n) %>% 
  column_to_rownames("sig_3") %>%
  print() %>% 
  fisher.test()


annotated_regions %>% 
  group_by(sig_24,MCF7_hypo) %>% tally %>% 
 pivot_wider(., id_cols = sig_24, names_from = MCF7_hypo, values_from = n) %>% 
  column_to_rownames("sig_24") %>%
  print() %>% 
  fisher.test()
```
#### Venns of MCF7 data
```{r}


 #  names(MCF7_DARs_hyper) <- paste0("hyper_", seq_along(seqnames(MCF7_DARs_hyper)))
 # names(MCF7_DARs_hypo) <- paste0("hypo_", seq_along(seqnames(MCF7_DARs_hypo)))
#### MCF7 and AR

AR_total     <- length(unique(all_regions$Peakid))
MCF_AR_total  <- length(unique(MCF7_ARsmcf7_1_LO$Peak_ID))-length(unique(MCF7_AR_ol$Peak_ID))
overlap_n    <- length(unique(MCF7_AR_ol$Peakid)) 
fit_mcf7_ar <- euler(c(
  "ARs" = AR_total-overlap_n,
  "MCF7_AR_1" = MCF_AR_total,
  "ARs&MCF7_AR_1" = overlap_n
))

plot(fit_mcf7_ar, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between AR and MCF7 AR (sample 1) peaks")


#### MCF7 hyper
AR_total     <- length(unique(all_regions$Peakid))
 MCF7_hyper_total  <- length(MCF7_DARs_hyper$names)-length(unique(MCF7_hyper_ol$names))
overlap_n    <- length(unique(MCF7_hyper_ol$Peakid)) 
fit_mcf7_hyper <- euler(c(
  "ARs" = AR_total-overlap_n,
  "MCF7_hyper_total" = MCF7_hyper_total,
  "ARs&MCF7_hyper_total" = overlap_n
))

plot(fit_mcf7_hyper, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between AR and MCF7 hyper-DARs ")

####MCF7 hypo only
AR_total     <- length(unique(all_regions$Peakid))
 MCF7_hypo_total  <- length(unique(MCF7_DARs_hypo$names))-length(unique(MCF7_hypo_ol$names))
overlap_n    <- length(unique(MCF7_hypo_ol$Peakid)) 
fit_mcf7_hypo <- euler(c(
  "ARs" = AR_total-overlap_n,
  "MCF7_hypo_total" = MCF7_hypo_total,
  "ARs&MCF7_hypo_total" = overlap_n
))

plot(fit_mcf7_hypo, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between AR and MCF7 hypo-DARs ")

#### MCF& all dars
AR_total     <- length(unique(all_regions$Peakid))
   MCF_DAR_total  <- MCF7_hypo_total+MCF7_hyper_total
overlap_n_MCF_dar    <- length(unique(MCF7_hyper_ol$Peakid))+length(unique(MCF7_hypo_ol$Peakid))
fit_mcf7_all_dar <- euler(c(
  "ARs" = AR_total-length(unique(MCF7_hyper_ol$Peakid))+length(unique(MCF7_hypo_ol$Peakid)),
  "MCF7_DAR" = MCF_DAR_total,
  "ARs&MCF7_DAR" = overlap_n_MCF_dar
))

plot(fit_mcf7_all_dar, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between AR and MCF7  DARs")
 

 

```

```{r}
DOX_DAR_total     <- length(unique(DOX_24_sig_gr$Peakid))
   MCF7_DAR_total  <- length(unique(MCF7_DAR_all$names))-length(unique(DOX_MCF7_DARS_ol$names))
overlap_n_MCF7_dar    <- length(unique(DOX_MCF7_DARS_ol$Peakid))
fit_mcf7_all_doxdar <- euler(c(
  "DOX_DARs" = DOX_DAR_total-length(unique(DOX_MCF7_DARS_ol$Peakid)),
  "MCF7_DAR" = MCF7_DAR_total,
  "DOX_DARs&MCF7_DAR" = overlap_n_MCF7_dar
))

plot(fit_mcf7_all_doxdar, fills = list(fill = c("skyblue", "lightcoral"), alpha = 0.6),
     labels = FALSE, edges = TRUE, quantities = TRUE,
     main = "Overlap between DOX-DARs(24 hours) and MCF7 DARs")

DOX_MCF7_DARS_ol %>% as.data.frame %>% distinct(Peakid) %>% tally

```
#### significance of MCF7 data
Are AR overlapping MCF7-ARs greater than expected by chance? (using sample 1,non-resistant MCF7)
```{r}
# genome <- BSgenome.Hsapiens.UCSC.hg38
# BiocManager::install("BSgenome.Hsapiens.UCSC.hg38.masked")
# combined_gr <- GRangesList(all_regions, MCF7_ARsmcf7_1_LO)
# universe <- GenomicRanges::reduce(combined_gr)
# # Get common chromosomes
# common_chrs <- intersect(seqlevels(MCF7_ARsmcf7_1_LO), seqlevels(all_regions))
# 
# Apply pruning to both datasets
# MCF7_ARsmcf7_1_LO <- keepSeqlevels(MCF7_ARsmcf7_1_LO, common_chrs, pruning.mode = "coarse")
# all_regions    <- keepSeqlevels(all_regions, common_chrs, pruning.mode = "coarse")
### number of cores used by test. documentation says to use mc.cores=8 (8 is my preference)
# param <- SnowParam(workers = 8)
# perm_test_AR_MCF7AR_combogr <- permTest(A= all_regions,
#                           B= MCF7_ARsmcf7_1_LO,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           universe=universe,
# # universe = union_accessible_regions,
#                           verbose = TRUE,
# BPPARAM = param)
#
##permtest #2 using universe="union_accessible_regions)
# saveRDS(perm_test_AR_MCF7AR_uni,"data/Final_four_data/re_analysis/perm_test_AR_MCF7AR_uni.RDS")

perm_test_AR_MCF7AR_uni <- readRDS("data/Final_four_data/re_analysis/perm_test_AR_MCF7AR_uni.RDS")
#original permutation test with whole genome
# saveRDS(perm_test_AR_MCF7AR,"data/Final_four_data/re_analysis/perm_test_AR_MCF7AR.RDS")


#using combined_gr <- GRangesList(all_regions, MCF7_ARsmcf7_1)
# universe <- GenomicRanges::reduce(combined_gr) to create a merged universe of ranges from both sets
# saveRDS(perm_test_AR_MCF7AR_combogr,"data/Final_four_data/re_analysis/perm_test_AR_MCF7AR_combogr_100.RDS")
# saveRDS(perm_test_AR_MCF7AR_combogr,"data/Final_four_data/re_analysis/perm_test_AR_MCF7AR_combogr_1000.RDS")
perm_test_AR_MCF7AR_combogr_1000 <- readRDS("data/Final_four_data/re_analysis/perm_test_AR_MCF7AR_combogr_1000.RDS")
perm_test_AR_MCF7AR <- readRDS("data/Final_four_data/re_analysis/perm_test_AR_MCF7AR.RDS")

# perm_test_AR_MCF7AR_combogr
plot(perm_test_AR_MCF7AR_uni)
plot(perm_test_AR_MCF7AR_combogr_1000)
plot(perm_test_AR_MCF7AR)

plot(perm_test_AR_MCF7AR, xlim = range(perm_test_AR_MCF7AR$numOverlaps$permuted))
```
Are DOX_DARS significantly more likely to overlap MCF7_DARs than chance?
```{r}

# MCF7_DAR_all <- keepSeqlevels(MCF7_DAR_all, common_chrs, pruning.mode = "coarse")
# all_regions    <- keepSeqlevels(all_regions, common_chrs, pruning.mode = "coarse")
# 
# perm_test_DAR_MCF7_DAR <- permTest(A= DOX_24_sig_gr,
#                           B= MCF7_DAR_all,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome="hg38",
#                           count.once= TRUE,
#                           verbose = TRUE)
# saveRDS(perm_test_DAR_MCF7_DAR,"data/Final_four_data/re_analysis/perm_test_DAR_MCF7_DAR.RDS")

perm_test_DAR_MCF7_DAR <- readRDS("data/Final_four_data/re_analysis/perm_test_DAR_MCF7_DAR.RDS")

perm_test_DAR_MCF7_DAR
plot(perm_test_DAR_MCF7_DAR)

plot(perm_test_DAR_MCF7_DAR, xlim = range(perm_test_DAR_MCF7_DAR$numOverlaps$permuted))
```
### Calculating Distance to TAD-SNP from peak of MCF7 DAR data  

```{r loading distance files}
Left_ventricle_TAD <- import(con = "C://Users/renee/Downloads/hg38.TADs/hg38/VentricleLeft_STL003_Leung_2015-raw_TADs.txt", format = "bed",genome="hg38")
mcols(Left_ventricle_TAD)$TAD_id <- paste0("TAD_", seq_along(Left_ventricle_TAD))

Schneider_all_SNPS <- read_delim("data/other_papers/Schneider_all_SNPS.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

Schneider_all_SNPS_df <- Schneider_all_SNPS %>%
  dplyr::rename("RSID"="#Uploaded_variation") %>% 
  dplyr::select(RSID,Location,SYMBOL,Gene, SOURCE) %>%
  distinct(RSID,Location,SYMBOL,.keep_all = TRUE) %>% 
  dplyr::rename("Close_SYMBOL"="SYMBOL") %>% 
  dplyr::filter(!str_starts(Location, "H")) %>% 
  separate_wider_delim(Location,delim=":",names=c("Chr","Coords")) %>% 
  separate_wider_delim(Coords,delim= "-", names= c("Start","End")) %>% 
  mutate(Chr=paste0("chr",Chr)) %>% 
  group_by(RSID) %>% 
  reframe(Chr=unique(Chr),
            Start=unique(Start),
            End=unique(End),
            Close_SYMBOL=paste(unique(Close_SYMBOL),collapse=";"),
            Gene=paste(Gene,collapse=";"),
            SOURCE=paste(SOURCE,collapse=";")
            ) %>% 
  GRanges() %>% as.data.frame 

schneider_gr <-Schneider_all_SNPS_df%>%
  dplyr::select(seqnames,start,end,RSID:SOURCE) %>%
  distinct() %>% 
  GRanges()
```

```{r dataframe overlapping}
snp_tad_df <-
  join_overlap_inner(schneider_gr, Left_ventricle_TAD) %>%
  as_tibble() %>%
  dplyr::select(RSID, snp_start = start, snp_chr = seqnames, TAD_id)


MCF7_DAR_tad_df <-
join_overlap_inner(MCF7_DAR_all, Left_ventricle_TAD) %>%
  as_tibble() %>%
  dplyr::select(names, peak_start = start, peak_chr = seqnames, TAD_id)

MCF7_DAR_snp_pairs <- MCF7_DAR_tad_df %>%
  inner_join(snp_tad_df, by = "TAD_id")

MCF7_DAR_snp_pairs_dist <-MCF7_DAR_snp_pairs %>%
  mutate(distance = abs(peak_start - snp_start)) 

saveRDS(MCF7_DAR_snp_pairs_dist,"data/Final_four_data/re_analysis/MCF7_DAR_snp_pairs_dist.RDS")
```



### significance of Snyder data (Heart left-ventricle)
```{r permtest,fig.width=10}
Snyder_41peaks <- read.delim("data/other_papers/ENCFF966JZT_bed_Snyder_41peaks.bed",header=TRUE) %>% 
  GRanges()

genome <- BSgenome.Hsapiens.UCSC.hg38
# perm_test_hlv <- permTest(A= all_regions,
#                           B= Snyder_41peaks,
#                           ntimes=1000,
#                           randomize.function=randomizeRegions,
#                           evaluate.function = numOverlaps,
#                           genome=genome,
#                           count.once= TRUE,
#                           verbose = TRUE)
# saveRDS(perm_test_hlv,"data/Final_four_data/re_analysis/perm_test_results_HLV.RDS")

perm_test_hlv <- readRDS("data/Final_four_data/re_analysis/perm_test_results_HLV.RDS")

perm_test_hlv
plot(perm_test_hlv)

plot(perm_test_hlv, xlim = range(perm_test_hlv$numOverlaps$permuted))

```

#### TOP2B and TOP2A expression (log2cpm from RNA data)

```{r expression}

drug_pal <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
RNA_counts <- readRDS("data/other_papers/cpmcount.RDS") %>%
  dplyr::rename_with(.,~gsub(pattern="Da",replacement="DNR",.)) %>% 
 dplyr::rename_with(.,~gsub(pattern="Do",replacement="DOX",.)) %>% 
  dplyr::rename_with(.,~gsub(pattern="Ep",replacement="EPI",.)) %>% 
   dplyr::rename_with(.,~gsub(pattern="Mi",replacement="MTX",.)) %>% 
    dplyr::rename_with(.,~gsub(pattern="Tr",replacement="TRZ",.)) %>% 
       dplyr::rename_with(.,~gsub(pattern="Ve",replacement="VEH",.)) %>% 
  rownames_to_column("ENTREZID")


RNA_results %>% 
  dplyr::filter(SYMBOL=="TOP2B")

RNA_counts %>% 
  dplyr::filter(ENTREZID =="7153") %>% 
  pivot_longer(cols = !ENTREZID, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("trt","ind","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  # facet_wrap(~SYMBOL, scales="free_y")+
    scale_fill_manual(values = drug_pal)+
  ggtitle("RNA Log2cpm of TOP2a")+
  theme_bw()+
  ylab("log2 cpm RNA")


RNA_counts %>% 
  dplyr::filter(ENTREZID =="7155") %>% 
  pivot_longer(cols = !ENTREZID, names_to = "sample", values_to = "counts") %>% 
  separate("sample", into = c("trt","ind","time")) %>% 
  mutate(time=factor(time, levels = c("3h","24h"))) %>% 
  mutate(trt=factor(trt, levels= c("DOX","EPI","DNR","MTX","TRZ","VEH"))) %>% 
  ggplot(., aes (x = time, y=counts))+
  geom_boxplot(aes(fill=trt))+
  # facet_wrap(~SYMBOL, scales="free_y")+
    scale_fill_manual(values = drug_pal)+
  ggtitle("RNA Log2cpm of TOP2b")+
  theme_bw()+
  ylab("log2 cpm RNA")

```

```{r Viewing  TAD102 genes}
TAD_102_genes <- c("TNFSF18","PRDX6", "TEX50", "KLHL20", "DARS2", "TNFSF4", "SLC9C2", "ANKRD45", "CENPL", "GAS5")

TAD_plot_genes <- RNA_results %>% 
  dplyr::filter(SYMBOL%in% TAD_102_genes) %>% 
  dplyr::select(ENTREZID,SYMBOL)

 ### Filter pvalues
 clean_RNA_adj.pvals <-  RNA_adj.pvals %>% 
    # dplyr::filter(ENTREZID=="55157") %>% 
    pivot_longer(cols = contains("pval"), names_to = "sample", values_to = "adj.p.val") %>% 
    separate(sample, into = c("trt", "time","pval")) %>% 
    mutate(
    time = paste0(time, "h"),  # convert "3" → "3h"
    trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ", "VEH"))
  )


for (gene in TAD_plot_genes$ENTREZID) {
  SYMBOL <- TAD_plot_genes$SYMBOL[TAD_plot_genes$ENTREZID == gene]
 

  # Filter and plot
  gene_plot <- RNA_counts %>%
    filter(ENTREZID == gene) %>%
    pivot_longer(cols = !ENTREZID, names_to = "sample", values_to = "counts") %>%
    separate(sample, into = c("trt", "ind", "time")) %>%
    mutate(
      time = factor(time, levels = c("3h", "24h")),
      trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ", "VEH"))
    ) %>%
    ggplot(aes(x = time, y = counts)) +
    geom_boxplot(aes(fill = trt)) +
    scale_fill_manual(values = drug_pal) +
    theme_bw() +
    ylab("log2 cpm RNA") +
    ggtitle(paste0("RNA Log2cpm of ", SYMBOL))
  
  plot(gene_plot)
}
```



```{r}

RNA_pval_clean <- RNA_adj.pvals %>%
  pivot_longer(cols = contains("pval"), names_to = "sample", values_to = "adj.p.val") %>% 
    separate(sample, into = c("trt", "time","pval")) %>% 
    mutate(
    time = paste0(time, "h"),  # convert "3" → "3h"
    trt = factor(trt, levels = c("DOX", "EPI", "DNR", "MTX", "TRZ", "VEH")),
    group = paste0(trt, "_", time),
    group = factor(group, levels = c(
        "DOX_3h", "EPI_3h", "DNR_3h", "MTX_3h", "TRZ_3h", "VEH_3h",
        "DOX_24h", "EPI_24h", "DNR_24h", "MTX_24h", "TRZ_24h", "VEH_24h"
      ))
    )

for (gene in TAD_plot_genes$ENTREZID) {
  SYMBOL <- TAD_plot_genes$SYMBOL[TAD_plot_genes$ENTREZID == gene]

  # Prep expression data
  gene_expr <- RNA_counts %>%
    filter(ENTREZID == gene) %>%
    pivot_longer(cols = !ENTREZID, names_to = "sample", values_to = "counts") %>%
    separate(sample, into = c("trt", "ind", "time")) %>%
    mutate(
      time = paste0(time),  # if already "3h"/"24h"
      group = paste0(trt, "_", time),
      group = factor(group, levels = c(
        "DOX_3h", "EPI_3h", "DNR_3h", "MTX_3h", "TRZ_3h", "VEH_3h",
        "DOX_24h", "EPI_24h", "DNR_24h", "MTX_24h", "TRZ_24h", "VEH_24h"
      ))
    )

  # Get gene-specific p-values
  gene_pvals <- RNA_pval_clean %>%
    filter(ENTREZID == gene)

  # Merge in p-values by group
  gene_plot_data <- left_join(gene_expr, gene_pvals, by = c("ENTREZID", "group"))

  # Create label position below box
  label_positions <- gene_plot_data %>%
    group_by(group) %>%
    summarise(y = min(counts, na.rm = TRUE) - 0.5, .groups = "drop")

  gene_plot_data <- left_join(gene_plot_data, label_positions, by = "group")
  gene_plot_data <- gene_plot_data %>%
  separate(group, into = c("trt", "time"), sep = "_", remove = FALSE)

  # Plot
  gene_plot <- ggplot(gene_plot_data, aes(x = group, y = counts)) +
    geom_boxplot(aes(fill = trt)) +
    geom_text(
      aes(y = y,
          label = ifelse(trt != "VEH" & !is.na(adj.p.val),
                         paste0("", signif(adj.p.val, 2)),
                         "")),
      size = 3,
      vjust = 1.2
    ) +
    scale_fill_manual(values = drug_pal) +
    theme_bw() +
    ggtitle(paste0("RNA Log2cpm of ", SYMBOL)) +
    ylab("log2 cpm RNA") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot(gene_plot)
}

```




